### 2018-09-24 notes/ederiv.tex
Adding notes about the energy derivatives

\documentclass{article}
\usepackage{amsmath}
\begin{document}
Consider a trial wave function

\begin{equation}
\Psi = \lim_{c\rightarrow 0} \Psi_0 + c \Psi_1
\end{equation}
 where $\Psi_0$ is the ground state and $\Psi_1$ is some excited state of a Hamiltonian H with energies $E_0, E_1$ respectively.

As $c \rightarrow 0$ the nodes of $\Psi$ match up with the nodes of $\Psi_0$. Let's consider one such nodal point $X$ where $\Psi(X) = \Psi_0(X) + c\Psi_1(X) \rightarrow 0$. We want to calculate the following quantity:

\begin{equation}
\lim_{r\rightarrow 0} \Bigg[\langle E_L \frac{\partial_c\Psi}{\Psi}\rangle - \langle E_L \rangle \langle\frac{\partial_c\Psi}{\Psi}\rangle \Bigg]_{D(X,r)},
\end{equation}
where the average $\langle \rangle$ is conducted by sampling $\Psi^2$ but with the positions sampled R restricted to the disk R $\in$ D(X,r) centered at the nodal point X with radius r.

\section{Local energy}
First we will expand the local energy in powers of c, and then in powers of r.

$$E_L = \frac{H\Psi}{\Psi} = \lim_{c\rightarrow 0} \frac{E_0\Psi_0 + cE_1\Psi_1}{\Psi_0 + c\Psi_1} \sim \lim_{c\rightarrow 0}(E_0\Psi_0 + cE_1\Psi_1)*(1-c\Psi_1/\Psi_0)/\Psi_0=$$

$$E_L(X+r) = \lim_{c\rightarrow 0}E_0 + c(E_1 - E_0)\frac{\Psi_1}{\Psi_0} + O(c^2)$$

Now expanding in terms of r we get:
$$\frac{\Psi_1(X+r)}{\Psi_0(X+r)} = \frac{\Psi_1(X) + \Psi_1^\prime(X)r + O(r^2)}{\Psi_0(X) + \Psi_0^\prime(X)r + O(r^2)}.$$
Note that $\Psi_0(X) = 0, \Psi_1^\prime(X)=\Psi_1^{\prime \prime}(X) =...=0$, namely that near the nodes $\Psi_0$ is linear in r whereas $\Psi_1$ is a \textit{constant}. Using these facts we can reduce the above expression to lowest order in r as: $\frac{\Psi_1}{\Psi_0^\prime}(X)\frac{1}{r}$. The final expression we get is then:

\begin{equation}
\boxed{\lim_{r\rightarrow 0} E_L = \lim_{c,r \rightarrow 0} E_0 + c(E_1 - E_0)\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} + O(c^2) + O(r^{-2})}.
\end{equation}

This is an expression for the local energy in a disk of radius r about the nodal point X for the wave function in equation (1).

\section{Wave function derivative}
Now we will expand the wave function derivative in powers of c, then in powers of r.

$$\frac{\partial_c \Psi}{\Psi} = \lim_{c \rightarrow 0}\frac{\Psi_1}{\Psi_0 + c\Psi_1} = \lim_{c \rightarrow 0} \frac{\Psi_1}{\Psi_0}(1-c\frac{\Psi_1}{\Psi_0})+O(c^2).$$

Using the expression above for $\Psi_1(X+r)/\Psi_0(X+r)$ and substituting we get that

\begin{equation}
\boxed{\lim_{r\rightarrow 0}\frac{\partial_c \Psi}{\Psi}(X+r) = \lim_{c,r \rightarrow 0} \frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} - c (\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r})^2+O(c^2) + O(r^{-3})}.
\end{equation}

\section{Equation (2)}
We can now combine equations (3) and (4) to get the value of (2) that we were interested in. The first term in equation (2) takes the form:

$$\lim_{c,r \rightarrow 0} \langle E_0 \frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} \rangle + \langle c(E_1-2E_0)(\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r})^2 \rangle + O(c^2) + O(r^{-3})$$

and the second term takes form:

$$\lim_{c,r \rightarrow 0} \langle E_0 \rangle \langle \frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} \rangle - \langle c(E_1 - E_0)\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} \rangle \langle \frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} \rangle - \langle E_0 \rangle \langle c (\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r})^2 \rangle + O(c^2) + O(r^{-3})$$

subtracting these two terms we come to the conclusion:

$$
(2) = c(E_1-E_0) \Big( \langle (\frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} )^2 \rangle - \langle \frac{\Psi_1(X)}{\Psi_0^\prime(X)}\frac{1}{r} \rangle ^2 \Big) + O(c^2) + O(r^{-3}) \rightarrow 
$$

\begin{equation}
\boxed{(2) \lim_{c,r \rightarrow 0} c(E_1-E_0) \text{Var}[\frac{\partial_c \Psi}{\Psi}]_{D(X,r)}+ O(c^2) + O(r^{-3})}
\end{equation}
where equation 4 was substituted in to lowest order in c,r, and the Monte Carlo estimator for the variance is evaluated on samples of position R drawn from $\Psi^2$ but restricted to the disk R $\in$ D(X,r) centered at the nodal point X with radius $r \rightarrow 0$.

\section{$\partial E/\partial c$}
In order to conduct the total parameter derivative we need to sample positions from the entire wave function, which we can write in the following way:
$$\frac{\partial E}{\partial c} = \Bigg[\langle E_L \frac{\partial_c\Psi}{\Psi}\rangle - \langle E_L \rangle \langle\frac{\partial_c\Psi}{\Psi}\rangle \Bigg]$$
where the expectation is over the entire domain $\Omega$ of $\Psi$ and points are sampled from $\Psi^2$. We can decompose this into parts which deal with the nodes, and parts which don't, as:

\begin{equation}
\boxed{\frac{\partial E}{\partial c} = \Bigg[\langle E_L \frac{\partial_c\Psi}{\Psi}\rangle - \langle E_L \rangle \langle\frac{\partial_c\Psi}{\Psi}\rangle \Bigg]_{\Omega/nodes}
+ \int dX (2)(X).}
\end{equation}
The first term here is the Monte Carlo average calculated on all points excluding the nodal surface, and the second term is the average calculated on the nodal surface: here the integral over X is over the nodal hypersurface. The first term is well behaved as seen empirically, and from the theory calculation above is also well behaved as away from the nodes $\Psi_0$ has a lowest order constant term, removing all divergences w.r.t r in expression (5).

On an infinite sample the variance term in (2) is well behaved since $\langle 1/r^2 \rangle \sim \int \Psi_0^2 (1/r^2) \sim \int r^2/r^2 $ does not diverge near the nodes. However, if we take a finite sample, it's easy to see that the \textit{variance of the estimator for the variance (sample variance)} is not well behaved.

$$\text{Var}[s^2] \sim \int (1/r^4) \Psi_0^2 dr \sim \int (1/r^2)dr. $$
This expression does diverge near the nodes, where $s^2$ is a finite sample estimator of $\text{Var}[\frac{\partial_c \Psi}{\Psi}]$ and the integration is conducted about D(X,r). Therefore we come to our final conclusion:

$$\boxed{\text{On a finite MC sample, term 1 in equation (6) has a finite variance}}$$
$$\boxed{\text{while term 2 in equation (6) has a large (possibly infinite) variance.}} $$
$$\boxed{\text{On an infinite MC sample both terms are finite with zero variance.}}$$

\section{More general derivation}
Consider a trial wave function of the form:
$$\Psi = \Psi_0 + c^p \Psi_p$$
where $\Psi_0, \Psi_p$ are not eigenstates of the Hamiltonian H. We want to calculate the functional dependence of the following quantities near nodes:

$$\frac{H\Psi}{\Psi}, \frac{\partial_p \Psi}{\Psi}$$

\subsection{Local energy}
Let's consider the denominator of the local energy first, namely let's Taylor expand $\Psi$ near the node $\textbf{N}$ as $$\Psi(\textbf{N} + \textbf{r}) = 0  + \nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)$$

The numerator can be considered in the same way. The numerator can be evaluated at the node by noting that $H\Psi$ is a wave function in our Hilbert space which generally not have the same nodes as $\Psi$ unless $\Psi$ happens to be an eigenstate. Foregoing the chance that $\Psi$ is an eigenstate, we can Taylor expand the numerator as

$$H\Psi(\textbf{N}+\textbf{r}) = C_H  + \nabla (H\Psi)(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)$$

Taking the ratio and limit as we get arbitrarily close to the nodes

$$\lim_{||\textbf{r}-\textbf{N}||\rightarrow 0} E_L(\textbf{r}) =\frac{C_H  + \nabla (H\Psi)(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)}{0  + \nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)} = \frac{C_H}{\nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N})} + \mathcal{O}((\textbf{r}-\textbf{N})^0) $$

\subsection{Wave function derivative}
The denominator of this term is the same as the local energy, the numerator is just $\Psi_p$. We note that near a node $\Psi_p$ is generally (assuming the nodes of the different determinants don't line up!) non-zero and has the Taylor expansion:

$$\Psi_p = C_P  + \nabla \Psi_p(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)$$

Again, taking the ratio and limit as we get arbitrarily close to the nodes
$$\lim_{||\textbf{r}-\textbf{N}||\rightarrow 0} \frac{\partial_p \Psi}{\Psi} = \frac{C_P  + \nabla \Psi_p(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)}{0  + \nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N}) + \mathcal{O}((\textbf{r}-\textbf{N})^2)} =\frac{C_P}{\nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N})} + \mathcal{O}((\textbf{r}-\textbf{N})^0)$$

\subsection{"Local" $\partial E/\partial p$}
We can define a quantity which I'll call the "local dE/dp" which is defined in the following way:

$$\frac{\partial E}{\partial p}(r,\textbf{r}) = \Bigg[ \langle E_L \frac{\partial_p \Psi}{\Psi} \rangle - \langle E_L \rangle \langle \frac{\partial_p \Psi}{\Psi} \rangle \Bigg]_{D(r,\textbf{r})} $$

where the brackets $\langle \rangle$ are Monte Carlo estimates using samples drawn from $\Psi^2$ drawn from the disk of radius $r$ around the point \textbf{r}.

The "local dE/dp" expression near the nodes can then be written as:\begin{equation}
\boxed{\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{N}) = C_HC_P \text{Var}\Big[\frac{1}{\nabla \Psi(\textbf{N})\cdot (\textbf{r} - \textbf{N})}\Big]_{D(r,\textbf{N})} + \mathcal{O}(r^0)}
\end{equation}

Near any non-nodal point of $\Psi$ we can note that the zeroth order term in the Taylor expansion of $\Psi$ does not vanish so that.
$$\lim_{||\textbf{r} - \textbf{x}||\rightarrow 0} E_L(\textbf{r}) = \frac{C_H}{\Psi(\textbf{x})} + \mathcal{O}(\textbf{r}-\textbf{x}), \lim_{||\textbf{r} - \textbf{x}||\rightarrow 0} \frac{\partial_p \Psi}{\Psi}(\textbf{r}) = \frac{C_P}{\Psi(\textbf{x})} + \mathcal{O}(\textbf{r}-\textbf{x}) $$
Therefore for a point nearby a non-nodal point \textbf{x} the local energy and parameter derivative are constants. The "local dE/dp" expression near non-nodal points \textbf{x} can then be written as:
\begin{equation} \boxed{\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{x}) = 0 + \mathcal{O}(r)}
\end{equation}
which makes sense because the evaluating dE/dp requires integrating over all space.

\subsection{Finite and infinite MC samples}
Let's consider equation (7) with both "infinite" (meaning we sample with infinite points and across the entire wave function domain) and finite number of MC samples.

In the first case, the expectation values can be converted to analytic integrals as:
$$\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{N}) = \lim_{r \rightarrow 0} C_HC_P \Bigg[\int_{D(\textbf{N},r)} dr \Psi^2(r) (\frac{1}{\nabla \Psi(\textbf{N})\cdot r})^2 -  \Big(\int_{D(\textbf{N},r)} dr \Psi^2(r) \frac{1}{\nabla \Psi(\textbf{N})\cdot r}\Big)^2 \Bigg]$$
substituting in $\Psi \sim \nabla \Psi(\textbf{N})\cdot r$ near the nodes, we get:
$$\lim_{r \rightarrow 0} C_HC_P \Bigg[\int_{D(\textbf{N},r)}dr\ 1  -  \Big(\nabla \Psi(\textbf{N}) \cdot \int_{D(\textbf{N},r)}  dr\ r \Big)^2 \Bigg]= 0 $$
\textit{Both} of these terms vanish in the limit since the domain of integration $D(\textbf{N},r)$ vanishes and the integrands have no poles.
Hence we see that near the nodes we get the same behavior away from the nodes if we use an analytic expression.
$$\textbf{For\ } \textbf{infinite\ } \textbf{MC } \textbf{samples }$$
\begin{equation}
\boxed{\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{N}) = 0}
\end{equation}
Further, immediately before equation (8) we showed that the local energy and derivatives are constants near a non-nodal point, meaning that:
$$\textbf{For\ } \textbf{infinite\ } \textbf{MC } \textbf{samples }$$
\begin{equation}
\boxed{\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{x}) = 0}
\end{equation}
Hence for "infinite" MC samples the "local dE/dp" behaves as expected for all points in the domain. Once integrated together we will get a non-divergent and well behaved value of dE/dp. (Duh)

In the latter case the situation is slightly more difficult. Equation (8) still holds in the finite case, so 
$$\textbf{For\ } \textbf{finite\ } \textbf{MC } \textbf{samples }$$
\begin{equation}
\boxed{\lim_{r \rightarrow 0} \frac{\partial E}{\partial p}(r,\textbf{x}) = 0, \text{Var} = 0.}
\end{equation}
Equation (7) does not behave particularly nicely when you have a finite number of samples. In particular, consider an estimator for the variance which is just the sample variance $s^2$ of the quantity $\frac{1}{\nabla \Psi(\textbf{N})(\textbf{r}-\textbf{N})}$. We can calculate properties of the sample variance, for sample $E[s^2]$ is the population variance, which is what we want in equation (10). We can also calculate the variance of this quantity analytically:
\begin{equation}
\boxed{Var[s^2] \sim \lim_{r\rightarrow 0} \int_{D(r,\textbf{N})} dr \Psi^2 (\frac{1}{\nabla\Psi(\textbf{N})\cdot r})^4 \sim \lim_{r\rightarrow 0} \int_{D(r,\textbf{N})} dr (\frac{1}{\nabla\Psi(\textbf{N})\cdot r})^2 \rightarrow \infty.}
\end{equation}
This variance of our estimator diverges!
Hence we see that 
$$\textbf{For finite MC samples, (7) has mean 0 but diverging variance.}$$
This seems to be the core problem, that the $1/r^2$ behavior of dE/dp near the nodes makes estimating the value of dE/dp using a finite MC sample difficult.

\end{document}

### 2019-03-27 paper/analysis.tex
started working on writing up my analysis for CuO, needs some cleaning up

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{subcaption}
\title{CuO Analysis Details}
\author{Shivesh Pathak}
\begin{document}
\maketitle
\section{Experiment}
APES measurements in 1996 indicate that the low-lying states of the CuO molecule are composed of 3d$^9$ and 3d$^10$ states, namely 9 and 10 electrons on the copper d orbitals [ref 48.pdf].

\begin{wrapfigure}{r}{0.4\textwidth}
  \begin{center}
    \includegraphics[width=0.3\textwidth]{APES.png}
  \end{center}
  \caption{APES measurements on CuO molecule.}
\end{wrapfigure}

They find the ground state to be of type $X^2\Pi$ and the first excited state to be of type $Y^2\Sigma^+$, which are consistent with higher resolution PES measurements and various other theoretical and experimental measurements [ref, \textbf{clean this up}]. The $X^2\Pi \rightarrow Y^2\Sigma^+$ excitation corresponds to an excitation $O p_\sigma \rightarrow O p_\pi$, and has a measured energy of 0.97 eV. The PES measurements also find a block of excitations starting at 2.20 eV which correspond to the 3d$^9$ excited states of CuO. Earlier measurements have found similar results. Both these PES measurements and Laser Induced Flourescence measurements in 1980 [ref] have found a quartet state at 1.91 eV. This state has been assigned as $^4\Sigma$ state, but the argumentation for its assignment is quite loose and based on a simple single particle model. Shown below are the most recent APES measurements for the CuO molecule, all state assignments except for the $b$ state have been verified by other experiments.

Given that the lowest energy states are 3d10 in character and higher energy excited states at 3d9, it is informative to look at the properties of the copper atom with 10 and 9 electrons respectively. The Cu$^+$ atom can have either configurations 3d$^10$4s$^0 (^1S)$ or 3d$^9$4s$^1 (^3D, ^1D)$ [ref]. The $^3D$ is lower in energy than the $^1D$ state by about 0.54 eV, indicating that a Hund's coupling between the Cu 4s and 3d orbitals of $J_H = -0.54 eV$.

\section{Sampling scheme}
In order to do DMD we need to densely sample the low energy space. In our case here, we will define the LES as the span of some base states. Since we know that our system has a low energy $3d9$ and $3d10$ sector, we will consider base states with either 9 or 10 electrons in the d-orbitals. Further, in order to consider the effects of a possible Hund's coupling arising in our effective theory from the Cu $J_H$, we will need to consider states with both $S_z=1/2, 3/2$. When moving to QMC, we will not be able to consider linear combinations of states with different $S_z$, so in order to sample the effect of $J_H$ densely, we would also like to consider "spin-flip partner" states in the $S_z=1/2$ sector. Consider for example a state 3d$^9$2p$_{pi}^3$4s$^1$ in the $S_z=1/2$ sector. The half-filled orbitals can have electrons with configuration $up\ up\ dn$ or $up\ dn\ up$, the prior which would have a Hund's energy $\frac{1}{2}J_H$ and the latter $-\frac{1}{2}J_H$. We would also like to work with single determinant base states, since we have found that single determinant Slater-Jastrow wave functions are quite accurate for transition metal oxide molecules [ref]. In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham eigenstates. We generated all unique base states in the 3d9 and 3d10 sectors using this method. In order to sample the span of the base states, namely our defined LES, we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1. Our final set of states in our span were then multiplied by a three-body Jastrow factor, which was optimized on the UKS ground state, and passed into DMC with a timestep of 0.01 and Tmoves on to calculate the 1-/2-rdms and total energy.

\section{RDM basis}
There were two choices of the RDM basis that we could have used, either an IAO basis or an MO basis. The IAO basis is more theoretically pleasing because it's a set of functions which best capture the variation between the the Cu 3d, O 2p, and Cu 4s orbitals from our different base states. However, the IAO basis has the drawback that many parameters will be correlated, for example $n_{p_\pi}$ and $t_\pi$. The MO basis choice is more arbitrary because we simply chose a set of spatially symmetric ($p_x, p_y$ look identical for example) ROKS molecular orbitals, since we don't know a way of constructing "intrinsic molecular orbitals." The MOs however yield the benefit that they are decorrelated for the most part, because to zeroth order the excitations of CuO look very similar to single-particle molecular orbital excitations. I therefore chose to do my model analysis using a mixture of both bases, namely using an MO basis for the non-interacting parts (n, t) but using an IAO basis for the interacting pieces (J, U, etc.).

\section{Model selection}
Model selection required both an understanding of the CuO molecule's low energy excitations and some statistical analysis. We know that the lowest energy excitations of CuO are between the O p and Cu 4s orbitals, as these are the only excitations which allow for a 3d10 configuration. Further, given that we will be including 3d9 states, it's clear that we will need at least consider the following non-interacting parameters:
$$\bar{\epsilon}_d, \bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$$

Here the bars indicate parameters corresponding to RDM elements evaluated on our MO basis. In addition to these parameters, we know that the Cu$^+$ atom has a Hund's coupling, so we will consider a parameter $J_{sd}$ which is Hund's coupling between the Cu 4s and Cu 3d orbitals. Finally, some of our base states have a $4s^2$ occupation, and therefore including a $U_{4s}$ is necessary. Our final proposed model then looks like:

$$ \boxed{\text{Proposed model: }\bar{\epsilon}_d, \bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}, J_{sd}, U_{4s}}$$

Since we know that $\bar{\epsilon}_d + \bar{\epsilon}_z + \bar{\epsilon}_\pi + \bar{\epsilon}_s = $ Const, we can eliminate $\bar{\epsilon}_d$ from our model since it is linearly dependent on the rest of the parameters. The left over occupation energies are certainly required in our model, given the knowledge we have of our low energy space. Since we know that $U_{4s}$ is required to describe the $4s^2$ states and that the $J_{sd}$ will probably play an important role as well, we just need to do model selection on the four hopping parameters. Below are 5-fold CV linear regressions using \textit{every} model which includes the $\bar{\epsilon}, J_{sd}, U_{4s}$ parameters above and one element in the power set of $\bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$.

\begin{figure}
\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/cv_valid.pdf}
\caption{5-fold CV regressions for model selection}
\end{figure}

The models are increasing in complexity from left-to-right, and it's clear that the fourth model listed here is as accurate as the most complex model, and significantly simpler. Therefore, we selected that model as it captures the most variation with the fewest parameters. The selected model then looks like this: 
$$ \boxed{\text{Selected model: }\bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, J_{sd}, U_{4s}}$$

\section{Model fitting}
We conducted a weighted least squares on our samples in order to fit the six parameters in our selected model. The higher density of states with $3d9$ occupation made it so that an unweighted linear regression would fit in a biased way towards the $3d9$ states, leaving the $3d10$ states fit very poorly. The weighting function we used was $e^{-\beta E_{DMC}}$, where $\beta$ is a variable "temperature" which was varied from 0.25 to 3.75 in increments of 0.25. We find that in the range of $\beta \in {1.5, 2.5}$ the model does not change very much, therefore we select a model at $\beta = 2.0$, which leads to the following set of regressed parameters:
\begin{multline}
 \boxed{\text{Final model }  (\beta=2): \bar{\epsilon}_z = 1.06(6) eV, \bar{\epsilon}_\pi = 2.12(5) eV, \bar{\epsilon}_s = 3.08(4) eV}\\
\boxed{\bar{t}_\pi = 0.52(4) eV, J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
\end{multline}

In order to look at the predictions of this model, we can rotate the MO basis elements into the IAO basis elements. Doing so yields the following more complicated model (note the lack of bars on the model parameters now!):

\begin{multline}
 \boxed{\text{Final model }  (\beta=2): \epsilon_{d_\delta} = 0.00 eV, \epsilon_{d_\pi} = -0.10 eV, \epsilon_{d_z^2} = 0.41 eV }\\
 \boxed{\epsilon_z = 1.2 eV, \epsilon_\pi = 2.21 eV, \epsilon_s = 2.44 eV}\\
\boxed{t_\pi = -0.22 eV, t_{d_z^2 s} = 0.38 eV, t_{s z} = 0.80 eV, t_{d_z^2 z} = 0.70 eV}\\
\boxed{ , J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
\end{multline}

\section{Comparison to DFT model}
We can then do an exact diagonalization on this model Hamiltonian, which was accomplished using an FCI solver for a custom Hamiltonian in PySCF [ref]. Show in the figures below are the lowest lying eigenstates of this model Hamiltonian for the full range of $\beta$, showing the energies and occupations of different orbitals. We can see that as we let $2.5 > \beta > 1.25 $ the model is fairly stable. The ground state of our model matches that of experiment, namely it has an electron configuration of $Cu 3d^{10} O 2p_z^{1.75} O 2p_\pi^3 Cu 4s^{0.4}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{2} O 2p_\pi^3 Cu 4s^{0}.$ This is also an $S_z=1/2$ state as expected in experiment. The first excited state in this range of $\beta$s is another $S_z=1/2$ state with occupations $Cu 3d^{9.7} O 2p_z^{1.2} O 2p_\pi^4 Cu 4s^{0.3}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{1} O 2p_\pi^4 Cu 4s^{0}.$ This state is at an energy of 1 eV which matches the APES measurements up to a tenth of an eV! The first $3d^9$ state is at around 2.2 eV, which again matches the predictions of the APES measurements. Aside from these states, there are also various states with $S_z=3/2$ which our model predicts to be low in energy. For example, there is an $S_z=3/2$ state with occupation at around 1.4 eV with occupations $Cu 3d^{9.7} O 2p_z^{2.0} O 2p_\pi^2 Cu 4s^{1.0}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{2} O 2p_\pi^2 Cu 4s^{1}.$ As predicted from the anion case, the lowest $S_z=3/2$ state is indeed a $O p_\pi \rightarrow Cu 4s$ excitation. There if another state at 2.0 eV which is $S_z =3/2$ and which corresponds to an $O p_z \rightarrow Cu 4s$ state. Therefore our model predicts that the measured state in APES is indeed a quartet state, however it should have $\Pi$ symmetry. The $\Sigma$ symmetry quartet state, which is indeed the lowest energy $S_z=3/2$ state, resides at an energy very close to the $^2Y$ state and may not have been able to resolve. Overall, our model matches every experimentally measured and rigorously confirmed eigenstate of CuO. We further argue that the labeling of a state at 2.0 eV as $^4\Sigma$ is faulty and it should be $^4\Pi$.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues.pdf}
  \caption{Eigenvalues of DMC fit model, hue $\beta$.}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues_sz.pdf}
  \caption{Eigenvalues of DMC fit model, hue $S_z$.}
  \label{fig:sub2}
\end{subfigure}
\label{fig:test1}
\caption{Eigenstates of models from DMC}
\end{figure}

We can compare these results to those found from, for example, an ROKS or UKS calculation of the ground state for CuO (one of our base states!). Typically one would take the ROKS/UKS eigenvalues and claim that these eigenvalues can be used as an approximate non-interacting model of the system. If we do so and exactly diagonalize in the $S_z=1/2,3/2$ sectors the ROKS/UKS eigenvalue matrix, we will find the following results for the eigenstates. The UKS eigenstates here are twice in number to the ROKS, since the UKS gives us two independent, approximate models, one for each spin channel. In table 1 below we also present the model parameters for the $\beta=2$ DMC regression compared to the ROKS model, which we will be focusing on from now on. Studying just the ROKS model for now, we see that it does predict an eigenstate at 1 eV which resembles the $^2Y$ state, however there are no low energy $S_z=3/2$ states at all. All of the $S_z=3/2$ states are $>$ 3eV above the ground state. We believe this should is due to the lack of relaxation effects present in the 1-particle model. The excited states of the CuO molecule do not look like simple 1-particle excitations on the ground state, there are relaxations of orbitals within a given symmetry sector. Further, the exclusion of the $J_{sd}$ pushes the $S_z=3/2$ states higher in energy. Clearly we see a large difference between the DMC and ROKS models, and that the DMC model more accurately reflects experiment.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/roks_eigenvalues.pdf}
  \caption{Eigenvalues of ROKS effective model.}
  \label{fig:sub3}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/uks_eigenvalues.pdf}
  \caption{Eigenvalues of UKS effective model.}
  \label{fig:sub4}
\end{subfigure}
\label{fig:test2}
\caption{Eigenstates of 1-particle models from DFT}
\end{figure}

\begin{wrapfigure}{r}{0.4\textwidth}
\begin{tabular}{lll}
 &  DMC (eV) & ROKS (eV) \\
$\epsilon_{d_\delta}$ &  0.00 & 0.00  \\
$\epsilon_{d_\pi}$ & -0.10 & -0.36 \\
$\epsilon_{d_{z^2}}$ & 0.41 & 0.52 \\
$\epsilon_z$ & 1.20 & 0.66 \\
$\epsilon_\pi$ & 2.21 & 0.85 \\
$\epsilon_s$ &  2.44 & 4.24 \\
$t_\pi$ & -0.22 & -1.14 \\
$t_{s d_{z^2}}$ & 0.38 & 0.97 \\
$t_{s z}$ & 0.80 & 1.86\\
$t_{d_{z^2} z}$ & 0.70 & 1.55\\
$J_{sd}$ & -0.51 & 0.00 \\ 
$U_s$ & 3.91 & 0.00 \\
\end{tabular}
\caption{Parameter differences between DFT/DMC models}
\end{wrapfigure}

\end{document}

### 2019-03-27 pyscf/ub3lyp_full/analyze_scf.py

@@ -14,7 +14,7 @@ el='Cu'
 r=1.725
 method='UB3LYP'
 S=1
-for run in range(10,11):
+for run in range(10,16):
   chkfile=el+'vtz'+"_r"+str(r)+"_s"+str(S)+"_"+method+"_"+str(run)+".chk"
   mol=lib.chkfile.load_mol(chkfile)
   m=ROHF(mol)

### 2019-03-27 pyscf/ub3lyp_full/collect_mos.py

@@ -16,7 +16,7 @@ el='Cu'
 
 occ=np.arange(14) 
 mo_coeff=None
-for run in [0,1,2]:
+for run in [0,1]:
   chkfile=el+basis+"_r"+str(r)+"_s"+str(S)+"_"+method+"_"+str(run)+".chk"
   mol=lib.chkfile.load_mol(chkfile)
   m=ROKS(mol)
@@ -34,4 +34,4 @@ for run in [0,1,2]:
 m.mo_coeff=mo_coeff
 print(m.mo_coeff[0].shape)
 print(m.mo_coeff[1].shape)
-print_qwalk_mol(mol,m,basename="all_min_s3")
+print_qwalk_mol(mol,m,basename="all_d10_s3")

### 2019-03-27 pyscf/ub3lyp_full/scf_s.py

@@ -38,6 +38,7 @@ symm_dict=[
 {'A1':(6,6),'E1x':(3,2),'E1y':(3,2),'E2x':(1,1),'E2y':(0,1)}, #(dd,pi -> s,s)
 ]
 '''
+'''
 #MIRROR (FOR IAOS)
 S=1
 symm_dict=[
@@ -67,8 +68,8 @@ symm_dict=[
 {'A1':(6,6),'E1x':(2,3),'E1y':(3,1),'E2x':(1,1),'E2y':(1,1)}, #(dpi,pi-> s,s)
 {'A1':(6,6),'E1x':(3,2),'E1y':(3,2),'E2x':(0,1),'E2y':(1,1)}, #(dd,pi -> s,s)
 ]
-######################################################################
 '''
+######################################################################
 S=3
 symm_dict=[
 #4s1 states-----------------------------------------------------------
@@ -83,10 +84,10 @@ symm_dict=[
 
 #4s2 states-----------------------------------------------------------
 #3d9 sector
-#{'A1':(6,6),'E1x':(3,2),'E1y':(3,2),'E2x':(1,1),'E2y':(1,0)}, 
-#{'A1':(6,6),'E1x':(3,2),'E1y':(3,1),'E2x':(1,1),'E2y':(1,1)}, 
+{'A1':(6,6),'E1x':(3,2),'E1y':(3,2),'E2x':(1,1),'E2y':(1,0)}, 
+{'A1':(6,6),'E1x':(3,2),'E1y':(3,1),'E2x':(1,1),'E2y':(1,1)}, 
 ]
-'''
+
 '''
 #MIRROR (FOR IAOS)
 S=3
@@ -100,6 +101,11 @@ symm_dict=[
 {'A1':(6,4),'E1x':(3,3),'E1y':(3,3),'E2x':(1,0),'E2y':(1,1)}, #delta, dn - px, py
 {'A1':(6,5),'E1x':(3,1),'E1y':(3,3),'E2x':(1,1),'E2y':(1,1)}, #pi, dn - pz, px
 {'A1':(6,3),'E1x':(3,3),'E1y':(3,3),'E2x':(1,1),'E2y':(1,1)}, #dz2, dn - px, py
+
+#4s2 states-----------------------------------------------------------
+#3d9 sector
[…]

### 2019-03-27 qwalk/ub3lyp_d10_s1/analyzedmc.py

@@ -18,8 +18,8 @@ from scipy import stats
 #Collect df
 def collect_df():
   df=None
-  for basestate in range(10):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
+  for basestate in range(6):
+    for gsw in np.arange(0.1,1.1,0.1):
       f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
       small_df=pd.read_pickle(f)
 
@@ -28,27 +28,17 @@ def collect_df():
       small_df['Sz']=0.5
       if(df is None): df = small_df
       else: df = pd.concat((df,small_df),axis=0,sort=True)
-
-  for basestate in range(6):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='../ub3lyp_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
+  '''
+  for basestate in range(2):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='../ub3lyp_d10_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
       small_df=pd.read_pickle(f)
     
-      small_df['basestate']=basestate
+      small_df['basestate']=basestate+6
       if(gsw==1.0): small_df['basestate']=-1
       small_df['Sz']=1.5
       df = pd.concat((df,small_df),axis=0,sort=True)
-  
-  for basestate in range(1,2):
-    for gsw in [1.0]:
-      f='../ub3lyp_do/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-    
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=-0.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  
+  '''
   return df
 
 #Formatting
@@ -66,6 +56,20 @@ def format_df(df):
   df['mo_t_sz']=2*df['mo_8_9']
   df['mo_t_ds']=2*df['mo_3_9']
[…]

### 2019-03-27 qwalk/ub3lyp_d10_s1/ed.py

@@ -34,7 +34,7 @@ def h1_moToIAO(parms,printvals=False):
   e[[2,7],[7,2]]=tdz
   e[[8,7],[7,8]]=tsz
   e[[8,2],[2,8]]=tds
-  
+
   if(printvals):
     w,vr=np.linalg.eigh(e)
     print('MO eigenvalues, Jsd=0 ------------------------------------')
@@ -44,7 +44,7 @@ def h1_moToIAO(parms,printvals=False):
   e = reduce(np.dot,(mo_to_iao.T,e,mo_to_iao))
   e[np.abs(e)<1e-10]=0
   e=(e+e.T)/2
- 
+  
   if(printvals):
     w,vr=np.linalg.eigh(e)
     print('IAO eigenvalues, Jsd=0 ------------------------------------')
@@ -52,37 +52,31 @@ def h1_moToIAO(parms,printvals=False):
 
   return e
 
-def h2_IAO(Jcu,Us):
+def h2_IAO(Jsd,Us):
   #Jsi = 0.25*(ns_u - ns_d)*(ni_u - ni_d) + 
   #0.5*(cs_u^+ cs_d ci_d^+ ci_u + cs_d^+ cs_u ci_u^+ ci_d)
+  
+  print(Jsd,Us)
 
   #PYSCF ordering: 2rdm[p,r,q,s]_x,x' = <cp_x^+ cq_x'^+ cs_x' cr_x>
   h2=np.zeros((3,9,9,9,9))
-  index=[0,1,2,3,6,8]
-  #for p in range(len(index)):
-  #  for j in range(p+1,len(index)):
-  j=5
-  for p in range(len(index)-1):
-      s=index[p]
-      i=index[j]
-      h2[0][s,s,i,i]=0.25
-      h2[2][s,s,i,i]=0.25
-      
-      h2[1][i,i,s,s]=-0.25
-      h2[1][s,s,i,i]=-0.25
-      h2[1][s,i,i,s]=-0.50
-      h2[1][i,s,s,i]=-0.50
-  h2*=Jcu
-  h2[1][8,8,8,8]=Us
+  s=8 #index for 4s orbital
+  for i in [0,1,2,3,6]:
+    h2[0][s,s,i,i]=0.25
+    h2[2][s,s,i,i]=0.25
+    
[…]

### 2019-03-27 qwalk/ub3lyp_s1_/analyzedmc.py

@@ -240,4 +240,4 @@ def analyze(df,save=False):
 if __name__=='__main__':
   df=collect_df()
   df=format_df(df)
-  analyze(df,save=True)
+  analyze(df,save=False)

### 2019-04-01 paper/analysis.tex
cleaned up RDM choice, need to work on rest before tomorrow

@@
 \usepackage{subcaption}
-\title{CuO Analysis Details}
-\author{Shivesh Pathak}
+\usepackage[margin=1.0in]{geometry}
+\usepackage{lineno}
+\linenumbers
+\linespread{2}
+\renewcommand\linenumberfont{\normalfont\bfseries\small}
+
 \begin{document}
-\maketitle
 \section{Experiment}
-APES measurements in 1996 indicate that the low-lying states of the CuO molecule are composed of 3d$^9$ and 3d$^10$ states, namely 9 and 10 electrons on the copper d orbitals [ref 48.pdf].
+Anion photoelectron spectroscopy (APES) measurements from 1996 indicate that the low-lying states of the CuO molecule are composed of 3d9 and 3d10 states [ref 48.pdf].
+Shown below are the most recent APES measurements for the CuO molecule, all state assignments except for the $b^4\Sigma$ state have been verified by other experiments.
 
@@
 
-They find the ground state to be of type $X^2\Pi$ and the first excited state to be of type $Y^2\Sigma^+$, which are consistent with higher resolution PES measurements and various other theoretical and experimental measurements [ref, \textbf{clean this up}].
+The APES measurements yield a ground state of CuO is $X^2\Pi$ and the first excited state $Y^2\Sigma^+$, which are consistent with higher resolution PES measurements and various other theoretical and experimental measurements [multiple ref].
 The $X^2\Pi \rightarrow Y^2\Sigma^+$ excitation corresponds to an excitation $O p_\sigma \rightarrow O p_\pi$, and has a measured energy of 0.97 eV.
-The PES measurements also find a block of excitations starting at 2.20 eV which correspond to the 3d$^9$ excited states of CuO.
+The APES measurements also find a block of excitations starting at 2.20 eV which correspond to the 3d9 excited states of CuO.
 Earlier measurements have found similar results.
-Both these PES measurements and Laser Induced Flourescence measurements in 1980 [ref] have found a quartet state at 1.91 eV.
-This state has been assigned as $^4\Sigma$ state, but the argumentation for its assignment is quite loose and based on a simple single particle model.
-Shown below are the most recent APES measurements for the CuO molecule, all state assignments except for the $b$ state have been verified by other experiments.
+Further, both these APES measurements and Laser Induced Flourescence measurements in 1980 [ref] have found a quartet state at 1.91 eV.
+This state has been assigned as $^4\Sigma$, but the argumentation for its assignment is based on an assumption that the quartet state measured in APES is the lowest possible energy quartet state.
 
-Given that the lowest energy states are 3d10 in character and higher energy excited states at 3d9, it is informative to look at the properties of the copper atom with 10 and 9 electrons respectively.
-The Cu$^+$ atom can have either configurations 3d$^10$4s$^0 (^1S)$ or 3d$^9$4s$^1 (^3D, ^1D)$ [ref].
-The $^3D$ is lower in energy than the $^1D$ state by about 0.54 eV, indicating that a Hund's coupling between the Cu 4s and 3d orbitals of $J_H = -0.54 eV$.
+Further, since the lowest energy states of the CuO molecule are 3d104s0, 3d94s0 and 3d94s1 in character, it is instructive to look at experimental measurements of the properties of the Cu$^+$ and Cu$^{2+}$ ions [ref].
+The Cu$^{2+}$ ion has a ground state of character 3d94s0, and a first excited state around 6.7 eV of 3d84s1, indicating that the 3d8 sector of eigenstates may be ignored in our study.
+The Cu$^+$ ion has a ground state character of 3d10, and two excited states at 2.72 and 3.26 eV of character 3d94s1.
+These two low energy excited states differ in their total spin, the lower energy state being a $^3D$ state and the higher energy state being a $^1D$ state.
+This indicates to us that there is a Hund's coupling on the copper atom of $J_H = -0.54 eV$.
 
 \section{Sampling scheme}
-In order to do DMD we need to densely sample the low energy space.
-In our case here, we will define the LES as the span of some base states.
-Since we know that our system has a low energy $3d9$ and $3d10$ sector, we will consider base states with either 9 or 10 electrons in the d-orbitals.
-Further, in order to consider the effects of a possible Hund's coupling arising in our effective theory from the Cu $J_H$, we will need to consider states with both $S_z=1/2, 3/2$.
+In order to do DMD we need to densely sample the low energy space (LES).
+In our case, we will define the LES as the span of a set of base states.
+Since we know that our system has a low energy 3d9 and 3d10 sector, we will consider base states with either 9 or 10 electrons in the d-orbitals.
+Further, in order to consider the effects of a possible Hund's coupling arising in our effective theory from the Cu atom $J_H$, we will need to consider states with both $S_z=1/2, 3/2$.
 When moving to QMC, we will not be able to consider linear combinations of states with different $S_z$, so in order to sample the effect of $J_H$ densely, we would also like to consider "spin-flip partner" states in the $S_z=1/2$ sector.
-Consider for example a state 3d$^9$2p$_{pi}^3$4s$^1$ in the $S_z=1/2$ sector.
-The half-filled orbitals can have electrons with configuration $up\ up\ dn$ or $up\ dn\ up$, the prior which would have a Hund's energy $\frac{1}{2}J_H$ and the latter $-\frac{1}{2}J_H$.
-We would also like to work with single determinant base states, since we have found that single determinant Slater-Jastrow wave functions are quite accurate for transition metal oxide molecules [ref].
-In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham eigenstates.
-We generated all unique base states in the 3d9 and 3d10 sectors using this method.
-In order to sample the span of the base states, namely our defined LES, we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1.
-Our final set of states in our span were then multiplied by a three-body Jastrow factor, which was optimized on the UKS ground state, and passed into DMC with a timestep of 0.01 and Tmoves on to calculate the 1-/2-rdms and total energy.
+Consider for example a state Cu3d9\!
+4s1 O2p$_{\pi}$3 in the $S_z=1/2$ sector.
+The half-filled orbitals can have electrons with configuration $up\ up\ dn$ or $up\ dn\ up$, the prior which would have a Hund's descriptor $\frac{1}{2}$ and the latter $-\frac{1}{2}$.
+Further, we would like to use single determinant Slater-Jastrow wave functions since they have proven to be quite accurate trial wave functions on previous QMC calculations for transition metal oxide molecules [ref].
+In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham (UKS) [ref] single determinant states using a B3LYP functional [ref] and Trail-Needs basis with the corresponding pseudopotentials [ref].
+
+First, we generated all the unique base states in the 3d9 and 3d10 sectors using this method.
+In order to sample the span of the base states we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1.
+Our final set of states in our span were then multiplied by a three-body Jastrow factor, which was optimized on the UKS ground state.
+Fixed node Diffusion Monte Carlo (FN-DMC) [ref] calculations were run with these states as trial wave functions with a timestep of 0.01 and Tmoves [ref]  in order to get 1-/2-density matrix elements and total energies.
 
@@
 The IAO basis is more theoretically pleasing because it's a set of functions which best capture the variation between the the Cu 3d, O 2p, and Cu 4s orbitals from our different base states.
-However, the IAO basis has the drawback that many parameters will be correlated, for example $n_{p_\pi}$ and $t_\pi$.
-The MO basis choice is more arbitrary because we simply chose a set of spatially symmetric ($p_x, p_y$ look identical for example) ROKS molecular orbitals, since we don't know a way of constructing "intrinsic molecular orbitals." The MOs however yield the benefit that they are decorrelated for the most part, because to zeroth order the excitations of CuO look very similar to single-particle molecular orbital excitations.
-I therefore chose to do my model analysis using a mixture of both bases, namely using an MO basis for the non-interacting parts (n, t) but using an IAO basis for the interacting pieces (J, U, etc.).
+Further, the IAO basis is beneficial for representing local interactions since they are localized orbitals.
+However, the IAO basis has the drawback that many 1-body parameters will be correlated, for example $n_{p_\pi}$ and $t_\pi$.
+The MO basis choice is more arbitrary since we don't know a way of constructing "intrinsic molecular orbitals," but the RDM elements in this basis tend to vary in a less correlated fashion.
+This is because, to lowest order, excitations of CuO look very similar to single-particle molecular orbital excitations, so variations in the MO descriptor space are nearly orthogonal.
+In order to take advantage of the benefits of both bases, I chose to do my model fitting using a mixture of both bases: an MO basis for the non-interacting parts (n, t) and an IAO basis for the interacting pieces (J, U, etc.).
+In the end we can rotate the MO parameters into the IAO basis, leading to a fully localized representation of our model.
+The IAO basis I used was constructed on the collection of active MOs (Cu 3d, O 2p and Cu 4s) from every base state.
+The MO basis selected was the the set of active MOs from the first excited ROKS state of CuO.
+This is because the single-Slater determinant ground state of CuO from ROKS breaks O$p_x, p_y$ and Cu$d_{xz}, d_{yz}$ degeneracies.
+These degeneracies are restored in the first excited state ROKS calculation.
+Later in the analysis, a weighted linear regression (WLS) is used to fit our model, and it will be shown that the WLS assigns nearly zero weight to any sampled states which have a 1-rdm trace far less than 15, the total number of electrons expected in our active space, indicating that our MO model is functioning properly even though it was seemingly arbitrarily chosen.
+Ultimately, one just needs to ensure that the MO basis can capture variation in the electron number occupancy without having electrons vanish between relevant excitations.
 

### 2019-04-24 paper/outline.tex
added outline to paper writing

\documentclass{article}
\begin{document}
\section{Introduction}
\begin{enumerate}
\item \textbf{General goal: }
Systematically develop model Hamiltonians which can accurately describe the energies as well as one- and two-particle properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.

\item \textbf{Barrier to achieving that goal: } The necessity for many-body interactions in describing the low-lying excited states of TMO molecules poses a difficult challenge when developing model Hamiltonians.

\item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.

\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe the energies, one- and two-particle properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure. 
\end{enumerate}

\section{Figures}

\end{document}

### 2019-04-24 paper/outline.tex
finished text of outline, going to add figures F1, F2, S1, S2, S3 soon
summary stats up

@@
 \documentclass{article}
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{subcaption}
+\usepackage[margin=1.0in]{geometry}
+
 \begin{document}
@@
 \item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.
+\textcolor{red}{Have to find references for this one, not sure how true this is.}
 
@@
 
+%Figure 1
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log.pdf}
+  \caption{Prediction of linear regression on full set of samples.}
+  \label{fig:Regression1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log_base.pdf}
+  \caption{Prediction of linear regression on base states only.}
+  \label{fig:Regression2}
+\end{subfigure}
+\label{fig:Regression}
+\caption{Linear regression predictions for total energy compared to DMC energies.}
+\end{figure}
+
+%Figure 2
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/}
+\label{fig:Regression}
+\caption{Results for energies and 1-/2-body properties of eigenstates from exact diagonalization of our model Hamiltonian.}
+\end{figure}
+
+\section{Supplementary Material}
+
 \end{document}

### 2019-04-24 qwalk/ub3lyp_s1_/analyzedmc.py

@@ -272,7 +272,7 @@ def ed_log(model,exp_parms_list):
     t_dz = 2*dm[:,6,7]
     t_sz = 2*dm[:,7,8]
     d = pd.DataFrame({'energy':E,'Sz':Sz,'iao_n_3d':n_3d,'iao_n_2pz':n_2pz,'iao_n_2ppi':n_2ppi,'iao_n_4s':n_4s,
-    'iao_t_pi':t_pi,'iao_t_ds':t_ds,'iao_t_dz':t_dz,'iao_t_sz':t_sz})
+    'iao_t_pi':t_pi,'iao_t_ds':t_ds,'iao_t_dz':t_dz,'iao_t_sz':t_sz,'iao_Us':res1[4],'iao_Jsd':res1[5]})
 
     E = res3[0]
     Sz = np.ones(len(E))*1.5
@@ -286,7 +286,7 @@ def ed_log(model,exp_parms_list):
     t_dz = 2*dm[:,6,7]
     t_sz = 2*dm[:,7,8]
     d = pd.concat((d,pd.DataFrame({'energy':E,'Sz':Sz,'iao_n_3d':n_3d,'iao_n_2pz':n_2pz,'iao_n_2ppi':n_2ppi,'iao_n_4s':n_4s,
-    'iao_t_pi':t_pi,'iao_t_ds':t_ds,'iao_t_dz':t_dz,'iao_t_sz':t_sz})),axis=0)
+    'iao_t_pi':t_pi,'iao_t_ds':t_ds,'iao_t_dz':t_dz,'iao_t_sz':t_sz,'iao_Us':res1[4],'iao_Jsd':res1[5]})),axis=0)
 
     d['energy']-=min(d['energy'])
     d['eig']=np.arange(d.shape[0])
@@ -398,7 +398,7 @@ def plot_ed_log(save=False):
   
   #normalize item number values to colormap
   norm = matplotlib.colors.Normalize(vmin=0, vmax=3.75)
-  
+  '''
   #FULL EIGENPROPERTIES and EIGENVALUES
   for model in np.arange(16):
     for beta in np.arange(3.75,-0.25,-0.25):
@@ -428,36 +428,35 @@ def plot_ed_log(save=False):
         plt.ylabel('energy (eV)')
     plt.savefig('analysis/ed_'+str(model)+'_log.pdf',bbox_inches='tight')
     plt.clf()
- 
-  '''
+  ''' 
[…]

### 2019-04-24 qwalk/ub3lyp_s1_/ed.py

@@ -98,60 +98,17 @@ def ED(parms, nroots, norb, nelec):
   #['del','del','yz','xz','x','y','z2','z','s']
   dm_u = []
   dm_d = []
+  sigU = []
+  sigJ = []
   for i in range(nroots):
-    dm=cis.make_rdm1s(ci[i],norb,nelec)
-    dm_u.append(dm[0])
-    dm_d.append(dm[1])
-  return e, ci, np.array(dm_u), np.array(dm_d)
-
-if __name__=='__main__':
-  '''
-  norb=9
-
-  full_df=None
-  beta=0
-  for parms in [
-  (3.0019,2.2094,0.6435,0.8995,0,0,0,-0.5798,4.2049),
-  (3.0310,2.1832,0.7768,0.8089,0,0,0,-0.5531,4.0500),
-  (3.0589,2.1512,0.9370,0.6936,0,0,0,-0.5322,3.7743),
-  (3.0883,2.1305,1.0353,0.5985,0,0,0,-0.5459,3.6741),
-  (3.0982,2.1120,1.0622,0.5232,0,0,0,-0.5692,3.8343),
-  (3.0899,2.0986,1.0575,0.4635,0,0,0,-0.5529,4.0939),
-  (3.0686,2.0945,1.0467,0.4232,0,0,0,-0.4561,4.3103),
-  (3.0413,2.0918,1.0332,0.4002,0,0,0,-0.3107,4.4374)]:
-
-    nelec=(8,7)
-    nroots=14
-    res1=ED(parms,nroots,norb,nelec)
-
-    nelec=(9,6)
-    nroots=6
-    res3=ED(parms,nroots,norb,nelec)
-
-    E = res1[0]
-    n_occ = res1[2]+res1[3]
-    Sz = np.ones(len(E))*0.5
-    n_3d = n_occ[:,0] + n_occ[:,1] + n_occ[:,2] + n_occ[:,3] + n_occ[:,6]
-    n_2ppi = n_occ[:,4] + n_occ[:,5]
-    n_2pz = n_occ[:,7]
-    n_4s = n_occ[:,8]
-    df = pd.DataFrame({'E':E,'Sz':Sz,'n_3d':n_3d,'n_2pz':n_2pz,'n_2ppi':n_2ppi,'n_4s':n_4s})
+    dm2=cis.make_rdm12s(ci[i],norb,nelec)
+    dm_u.append(dm2[0][0])
+    dm_d.append(dm2[0][1])
[…]

### 2019-05-06 pyscf/ub3lyp_new/collect_mos.py
have my full base states run ready. hopefully everything goes smoothly.

@@ -7,17 +7,13 @@ import pandas as pd
 import matplotlib.pyplot as plt
 from pyscf2qwalk import print_qwalk_mol
 
-charge=0
-S=3
-r=1.725
-method='UB3LYP'
-basis='vtz'
-el='Cu'
-
+'''
+chkfiles=['../ub3lyp_full/Cuvtz_r1.725_s1_UB3LYP_'+str(i)+'.chk' for i in range(11)]
+chkfiles+=['Cuvtz_r1.725_s1_UB3LYP_11.chk','Cuvtz_r1.725_s1_UB3LYP_12.chk']
 occ=np.arange(14) 
 mo_coeff=None
-for run in [0,1]:
-  chkfile=el+basis+"_r"+str(r)+"_s"+str(S)+"_"+method+"_"+str(run)+".chk"
+
+for chkfile in chkfiles:
   mol=lib.chkfile.load_mol(chkfile)
   m=ROKS(mol)
   m.__dict__.update(lib.chkfile.load(chkfile, 'scf'))
@@ -34,4 +30,29 @@ for run in [0,1]:
 m.mo_coeff=mo_coeff
 print(m.mo_coeff[0].shape)
 print(m.mo_coeff[1].shape)
-print_qwalk_mol(mol,m,basename="all_d10_s3")
+print_qwalk_mol(mol,m,basename="all_s1")
+'''
+
+chkfiles = ['../ub3lyp_full/Cuvtz_r1.725_s3_UB3LYP_'+str(i)+'.chk' for i in range(6)]
+chkfiles += ['Cuvtz_r1.725_s3_UB3LYP_13.chk']
+occ=np.arange(14) 
+mo_coeff=None
+
+for chkfile in chkfiles:
+  mol=lib.chkfile.load_mol(chkfile)
+  m=ROKS(mol)
+  m.__dict__.update(lib.chkfile.load(chkfile, 'scf'))
+  
+  if(mo_coeff is None): 
+    mo_coeff=[None,None]
+    mo_coeff[0]=m.mo_coeff[0][:,occ]
+    mo_coeff[1]=m.mo_coeff[1][:,occ]
+  else: 
+    mo_coeff[0]=np.concatenate((mo_coeff[0],m.mo_coeff[0][:,occ]),axis=1)
+    mo_coeff[1]=np.concatenate((mo_coeff[1],m.mo_coeff[1][:,occ]),axis=1)
+
+#Write to file 
[…]

### 2019-05-06 qwalk/mo_vmc/gather.py

@@ -1,54 +1,0 @@
-import json 
-import pandas as pd
-import numpy as np 
-import sys
-sys.path.append('../../../downfolding/')
-from shivesh_downfold_tools import get_qwalk_dm
-
-def gather_all(detgen,N,Ndet,gsw,basename):
-  ''' 
-  Gathers all your data and stores into 
-  '''
-  df=None
-  for j in range(N+1):
-<<<<<<< HEAD
-    for name in ['2X','2Y','4SigmaM']:
-=======
-    for name in ['2X']:
->>>>>>> 25bfdb4a0a27ebfa182c5df1472ce635d5a718b6
-      if(j==0): f='base/'+name+'.vmc.gosling.json'  #GS
-      else: f=basename+'/'+name+'_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(gsw)+'_'+str(j)+'.vmc.gosling.json'
-      
-      data=json.load(open(f,'r'))
-      obdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
-      energy=data['properties']['total_energy']['value'][0]*27.2114
-      energy_err=data['properties']['total_energy']['error'][0]*27.2114
-
-      n_labels=np.array(["y1","y2","x1","x2","s1","s2","s3"])
-<<<<<<< HEAD
-      sz_labels=np.array(["sy1","sy2","sx1","sx2","ss1","ss2","ss3"])
-      n=np.diag(obdm[0,:,:])+np.diag(obdm[1,:,:])
-      sz=np.diag(obdm[0,:,:])-np.diag(obdm[1,:,:])
-      
-      d=pd.DataFrame(np.array([energy,energy_err]+list(n)+list(sz))[:,np.newaxis].T,columns=['energy','energy_err']+list(n_labels)+list(sz_labels))
-=======
-      n=np.diag(obdm[0,:,:])+np.diag(obdm[1,:,:])
-
-      d=pd.DataFrame(np.array([energy,energy_err]+list(n))[:,np.newaxis].T,columns=['energy','energy_err']+list(n_labels))
->>>>>>> 25bfdb4a0a27ebfa182c5df1472ce635d5a718b6
-      d=d.astype('double')
-      d['base_state']=name
-      if(df is None): df=d
-      else: df=pd.concat((df,d),axis=0)      
-  
[…]

### 2019-05-06 qwalk/mo_vmc/geninput.py

@@ -1,151 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(detgen,N,Ndet,gsw,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample per spin (2*N states in total)
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
-  genslater(detgen,N,Ndet,gsw,basename,fout)
-  genvmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  for state in ['2X','2Y','4SigmaM']:
-    for j in range(1,N+1):
-      fname=state+fout+'_'+str(j)
-     
-      #Blue waters input  
-      string='#!/bin/bash\n'+\
-      '#PBS -q wagner\n'+\
-      '#PBS -l nodes=1,flags=allprocs\n'+\
-      '#PBS -l walltime=00:10:00\n'+\
-      '#PBS -N '+fname+'\n'\
-      '#PBS -e '+fname+'.perr\n'+\
-      '#PBS -o '+fname+'.pout\n'+\
-      'module load openmpi/3.1.1-gcc-7.2.0\n'+\
-      'module load intel/18.0\n'+\
-      'cd ${PBS_O_WORKDIR}/'+basename+'\n'+\
-      'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'
-
-      f=open(basename+'/'+fname+'.pbs','w')
-      f.write(string)
-      f.close()      
-  return 1
-
-def genvmc(N,basename,fout):
-  for state in ['2X','2Y','4SigmaM']:
-    for j in range(1,N+1):
[…]

### 2019-05-06 qwalk/mo_vmc/geninput_2rdm.py

@@ -1,160 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(detgen,N,Ndet,gsw,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample per spin (2*N states in total)
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
-  genslater(detgen,N,Ndet,gsw,basename,fout)
-  genvmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  for state in ['2X','2Y','4SigmaM']:
-    for j in range(1,N+1):
-      fname=state+fout+'_'+str(j)
-     
-      #Blue waters input  
-      string='#!/bin/bash\n'+\
-      '#PBS -q wagner\n'+\
-      '#PBS -l nodes=1,flags=allprocs\n'+\
-      '#PBS -l walltime=00:10:00\n'+\
-      '#PBS -N '+fname+'\n'\
-      '#PBS -e '+fname+'.perr\n'+\
-      '#PBS -o '+fname+'.pout\n'+\
-      'module load openmpi/3.1.1-gcc-7.2.0\n'+\
-      'module load intel/18.0\n'+\
-      'cd ${PBS_O_WORKDIR}/'+basename+'\n'+\
-      'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'
-
-      f=open(basename+'/'+fname+'.pbs','w')
-      f.write(string)
-      f.close()      
-  return 1
-
-def genvmc(N,basename,fout):
-  for state in ['2X','2Y','4SigmaM']:
-    for j in range(1,N+1):
[…]

### 2019-05-06 qwalk/mo_vmc/subpbs.py

@@ -1,26 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(detgen,N,Ndet,gsw,basename):
-  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
-<<<<<<< HEAD
-  #for state in ['2Y','4SigmaM']:
-  for state in ['2X']:
-=======
-  for state in ['2Y','4SigmaM']:
-  #for state in ['2X']:
->>>>>>> 25bfdb4a0a27ebfa182c5df1472ce635d5a718b6
-    for j in range(1,N+1):
-      fname=basename+'/'+state+fout+'_'+str(j)+'.pbs'
-      os.system('qsub '+fname)
-
-if __name__=='__main__':
-  detgen='a'
-  N=200
-  Ndet=10
-  gsw=0.9
-<<<<<<< HEAD
-  subpbs(detgen,N,Ndet,gsw,basename='run2a/')
-=======
-  subpbs(detgen,N,Ndet,gsw,basename='run1a/')
->>>>>>> 25bfdb4a0a27ebfa182c5df1472ce635d5a718b6

### 2019-05-06 qwalk/naive/analyzevmc.py

@@ -1,52 +1,0 @@
-#Analyze VMC
-import numpy as np 
-import json
-N=20 #Number of expansions 
-
-el='Cu'
-charge=0
-minao={}
-basis='vtz'
-method='B3LYP'
-
-'''
-#Energies
-E=[]
-err=[]
-nblock=[]
-for i in range(1,N+1):
-  e=[]
-  esig=[]
-  nb=0
-  basename=el+basis+str(charge)+"_"+method+".vmc"+str(i)
-  with open("/scratch/sciteam/sapatha2/"+basename+"/"+basename+".o","r") as f:
-    for line in f:
-      if("##0" in line):
-	e.append(float(line.split(" ")[10]))	
-        nb+=1
-      if("&&0" in line):
-	esig.append(float(line.split(" ")[11]))	
-  e=np.array(e)
-  esig=np.array(esig)
-   
-  if(i==5): print(esig)
-
-  e=np.sum(e)/len(e)
-  esig=np.sum(esig**2)/len(esig)**2  
-  E.append(e)
-  err.append(esig)
-  nblock.append(nb)
-  print(e,esig)
-  f.close() 
-
-
-d={'E':E,'err':err,'nblock':nblock}
-json.dump(d,open("analyzevmc.json","w"))
-'''
-
-#Plot energies
-import matplotlib.pyplot as plt
-d=json.load(open("analyzevmc.json","r"))
-print(d['err'])
-plt.errorbar(np.arange(len(d['E'])),d['E'],yerr=d['err'],c='g',marker='o')
-plt.show()

### 2019-05-06 qwalk/naive/gendmc_E.py

@@ -1,77 +1,0 @@
-#DMC files only for energy
-import numpy as np
-
-######################################################################
-#USER OPTIONS, ONLY THING TO EDIT
-cutoff="0p4" #cutoff for slater
-N=20 #number of expansions we want, minimum 1
-nblock=400 #number of vmc blocks we want, minimum 1
-timestep=0.01 #timestep, minimum 0
-nodes=20 #number of nodes (32 ppn)
-walltime="01:00:00"
-######################################################################
-
-el='Cu'
-charge=0
-minao={}
-
-#Read in template file 
-i=0
-edit_ind=[] #Indices of lines to edit
-template=[]
-with open("dmc_template_E","r") as f:
-  for line in f:
-    template.append(line)
-    if("##" in line):
-      edit_ind.append(i)
-    i+=1
-f.close()
-
-#Write out slater files
-#for method in ['ROHF','B3LYP','PBE0']:
-#  for basis in ['vdz','vtz']:
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method
-      
-      template[edit_ind[0]]="  nblock "+str(nblock)+"\n"
-      template[edit_ind[1]]="  timestep "+str(timestep)+"\n"
-      template[edit_ind[2]]="include "+basename+".sys"
-      template[edit_ind[3]]="  wf1 { include "+basename+".slater"+str(i)+cutoff+" }"+"\n"
-      
-      fname=basename+".dmc_E"+str(i)+cutoff
-      fout=open(fname,"w")
-      fout.write("".join(template))
-      fout.close()
-
-#Write dmc pbs files
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method+".dmc_E"+str(i)+cutoff
-      cpypath="/u/sciteam/$USER/cuo/qwalk/"+el+basis+str(charge)+"_"+method
-
-      contents="#!/bin/bash \n"+\
-      "#PBS -q normal\n"+\
-      "#PBS -l nodes="+str(nodes)+":ppn=32:xe \n"+\
-      "#PBS -l walltime="+walltime+"\n"+\
-      "#PBS -N "+basename+"\n"+\
[…]

### 2019-05-06 qwalk/naive/gendmc_E_not.py

@@ -1,77 +1,0 @@
-#DMC files only for energy
-import numpy as np
-
-######################################################################
-#USER OPTIONS, ONLY THING TO EDIT
-cutoff="0p2" #cutoff for slater
-N=20 #number of expansions we want, minimum 1
-nblock=100 #number of vmc blocks we want, minimum 1
-timestep=0.01 #timestep, minimum 0
-nodes=20 #number of nodes (32 ppn)
-walltime="00:30:00"
-######################################################################
-
-el='Cu'
-charge=0
-minao={}
-
-#Read in template file 
-i=0
-edit_ind=[] #Indices of lines to edit
-template=[]
-with open("dmc_template_E_not","r") as f:
-  for line in f:
-    template.append(line)
-    if("##" in line):
-      edit_ind.append(i)
-    i+=1
-f.close()
-
-#Write out slater files
-#for method in ['ROHF','B3LYP','PBE0']:
-#  for basis in ['vdz','vtz']:
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method
-      
-      template[edit_ind[0]]="  nblock "+str(nblock)+"\n"
-      template[edit_ind[1]]="  timestep "+str(timestep)+"\n"
-      template[edit_ind[2]]="include "+basename+".sys"
-      template[edit_ind[3]]="  wf1 { include "+basename+".slater"+str(i)+cutoff+" }"+"\n"
-      
-      fname=basename+".dmc_E"+str(i)+cutoff+"_not"
-      fout=open(fname,"w")
-      fout.write("".join(template))
-      fout.close()
-
-#Write dmc pbs files
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method+".dmc_E"+str(i)+cutoff+"_not"
-      cpypath="/u/sciteam/$USER/cuo/qwalk/"+el+basis+str(charge)+"_"+method
-
-      contents="#!/bin/bash \n"+\
-      "#PBS -q normal\n"+\
-      "#PBS -l nodes="+str(nodes)+":ppn=32:xe \n"+\
-      "#PBS -l walltime="+walltime+"\n"+\
[…]

### 2019-05-06 qwalk/naive/gendmc_SR_not.py

@@ -1,79 +1,0 @@
-#DMC files only for energy and small RDM (not full basis elements)
-import numpy as np
-
-######################################################################
-#USER OPTIONS, ONLY THING TO EDIT
-cutoff="0p4" #cutoff for slater
-N=20 #number of expansions we want, minimum 1
-nblock=100 #number of vmc blocks we want, minimum 1
-timestep=0.01 #timestep, minimum 0
-nodes=20 #number of nodes (32 ppn)
-walltime="01:00:00"
-######################################################################
-
-el='Cu'
-charge=0
-minao={}
-
-#Read in template file 
-i=0
-edit_ind=[] #Indices of lines to edit
-template=[]
-with open("dmc_template_SR_not","r") as f:
-  for line in f:
-    template.append(line)
-    if("##" in line):
-      edit_ind.append(i)
-    i+=1
-f.close()
-
-#Write out dmc files
-#for method in ['ROHF','B3LYP','PBE0']:
-#  for basis in ['vdz','vtz']:
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method
-      
-      template[edit_ind[0]]="  nblock "+str(nblock)+"\n"
-      template[edit_ind[1]]="  timestep "+str(timestep)+"\n"
-      template[edit_ind[2]]="include "+basename+".sys"
-      template[edit_ind[3]]="  wf1 { include "+basename+".slater"+str(i)+cutoff+" }"+"\n"
-      
-      fname=basename+".dmc_E_SR_"+str(i)+cutoff+"_not"
-      fout=open(fname,"w")
-      fout.write("".join(template))
-      fout.close()
-
-#Write dmc pbs files
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method+".dmc_E_SR_"+str(i)+cutoff+"_not"
-      cpypath="/u/sciteam/$USER/cuo/qwalk/"+el+basis+str(charge)+"_"+method
-
-      contents="#!/bin/bash \n"+\
-      "#PBS -q normal\n"+\
-      "#PBS -l nodes="+str(nodes)+":ppn=32:xe \n"+\
[…]

### 2019-05-06 qwalk/naive/genslater.py

@@ -1,48 +1,0 @@
-#Generates multi slater expansions for our calculations
-import numpy as np
-
-cutoff="0p4"
-wmax=0.4 #maximum magnitude of weights
-Ndet=23 #number of determinants in expansion
-N=20 #number of expansions we want, minimum 1
-assert(N>=1)
-
-el='Cu'
-charge=0
-minao={}
-
-#Read in template file 
-i=0
-edit_ind=[] #Indices of lines to edit
-template=[]
-with open("slat_template","r") as f:
-  for line in f:
-    template.append(line)
-    if("##" in line):
-      edit_ind.append(i)
-    i+=1
-f.close()
-
-#Write out slater files
-#for method in ['ROHF','B3LYP','PBE0']:
-#  for basis in ['vdz','vtz']:
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method
-      
-      w=2*wmax*np.random.rand(Ndet-1)-wmax
-      weights=[1.0]+w.tolist()
-      weights=[str(x) for x in weights]
-      
-      for p in np.arange(0,Ndet+5,5):
-        weights.insert(p,"\n")
-      
-      template[edit_ind[0]]="  ORBFILE "+basename+".orb"+"\n"
-      template[edit_ind[1]]="  INCLUDE "+basename+".basis"+"\n"
-      template[edit_ind[2]]="  OPTIMIZE_DET \n DETWT { "+" ".join(weights)+" }"+"\n"
-      
-      fname=basename+".slater"+str(i)+cutoff
-      fout=open(fname,"w")
-      fout.write("".join(template))
-      fout.close()

### 2019-05-06 qwalk/naive/remdmc.py

@@ -1,30 +1,0 @@
-#Remove all generated slater files
-import sys
-from os import remove 
-import os.path
-
-N=0
-if(len(sys.argv)==1):
-  N=1000
-  print("Removing all files")
-else:   
-  N=int(sys.argv[1])
-  print("Removing all files up to index "+str(N))
-
-el='Cu'
-charge=0
-#for method in ['ROHF','B3LYP','PBE0']:
-#  for basis in ['vdz','vtz']:
-for method in ['B3LYP']:
-  for basis in ['vtz']:
-    for i in range(1,N+1):
-      basename=el+basis+str(charge)+"_"+method
-      fname=basename+".dmc"+str(i)
-      
-      if(os.path.isfile(fname)):
-        remove(fname)
-
-      fname=basename+".dmc"+str(i)+".pbs"
-      
-      if(os.path.isfile(fname)):
-        remove(fname)

### 2019-05-06 qwalk/old/mo_vmc/geninput_2rdm.py

@@ -1,0 +1,160 @@
+#Generate input files for 2rdm, use same slater files as old 1rdm!
+import os 
+import shutil 
+import numpy as np 
+
+def geninput(detgen,N,Ndet,gsw,basename):
+  '''
+  input:
+  detgen - type of excitations to sample
+  N - number of states to sample per spin (2*N states in total)
+  Ndet - number of determinants per state
+  gsw - ground state weight 
+  basename - all written files to basename/__generated file names__
+  output:
+  slater files
+  vmc files 
+  pbs files for vmc
+  '''
+ 
+  #Make sure directory exists, else make it 
+  if not os.path.exists(basename):
+    #Move all important files to there 
+    shutil.copytree('req_files',basename+'/') 
+  else:
+    print('Directory '+str(basename)+' exists, not going to overwrite')
+    exit(0)  
+  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
+  genslater(detgen,N,Ndet,gsw,basename,fout)
+  genvmc(N,basename,fout)
+  genpbs(N,basename,fout)
+  return 
+
+def genpbs(N,basename,fout):
+  for state in ['2X','2Y','4SigmaM']:
+    for j in range(1,N+1):
+      fname=state+fout+'_'+str(j)
+     
+      #Blue waters input  
+      string='#!/bin/bash\n'+\
+      '#PBS -q wagner\n'+\
+      '#PBS -l nodes=1,flags=allprocs\n'+\
+      '#PBS -l walltime=00:10:00\n'+\
+      '#PBS -N '+fname+'\n'\
+      '#PBS -e '+fname+'.perr\n'+\
+      '#PBS -o '+fname+'.pout\n'+\
+      'module load openmpi/3.1.1-gcc-7.2.0\n'+\
+      'module load intel/18.0\n'+\
+      'cd ${PBS_O_WORKDIR}/'+basename+'\n'+\
+      'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'
+
+      f=open(basename+'/'+fname+'.pbs','w')
+      f.write(string)
+      f.close()      
+  return 1
+
+def genvmc(N,basename,fout):
+  for state in ['2X','2Y','4SigmaM']:
+    for j in range(1,N+1):
[…]

### 2019-05-06 qwalk/old/naive/gendmc_SR.py

@@ -1,0 +1,79 @@
+#DMC files only for energy and small RDM (not full basis elements)
+import numpy as np
+
+######################################################################
+#USER OPTIONS, ONLY THING TO EDIT
+cutoff="0p2" #cutoff for slater
+N=20 #number of expansions we want, minimum 1
+nblock=100 #number of vmc blocks we want, minimum 1
+timestep=0.01 #timestep, minimum 0
+nodes=20 #number of nodes (32 ppn)
+walltime="01:00:00"
+######################################################################
+
+el='Cu'
+charge=0
+minao={}
+
+#Read in template file 
+i=0
+edit_ind=[] #Indices of lines to edit
+template=[]
+with open("dmc_template_SR","r") as f:
+  for line in f:
+    template.append(line)
+    if("##" in line):
+      edit_ind.append(i)
+    i+=1
+f.close()
+
+#Write out dmc files
+#for method in ['ROHF','B3LYP','PBE0']:
+#  for basis in ['vdz','vtz']:
+for method in ['B3LYP']:
+  for basis in ['vtz']:
+    for i in range(1,N+1):
+      basename=el+basis+str(charge)+"_"+method
+      
+      template[edit_ind[0]]="  nblock "+str(nblock)+"\n"
+      template[edit_ind[1]]="  timestep "+str(timestep)+"\n"
+      template[edit_ind[2]]="include "+basename+".sys"
+      template[edit_ind[3]]="  wf1 { include "+basename+".slater"+str(i)+cutoff+" }"+"\n"
+      
+      fname=basename+".dmc_E_SR_"+str(i)+cutoff
+      fout=open(fname,"w")
+      fout.write("".join(template))
+      fout.close()
+
+#Write dmc pbs files
+for method in ['B3LYP']:
+  for basis in ['vtz']:
+    for i in range(1,N+1):
+      basename=el+basis+str(charge)+"_"+method+".dmc_E_SR_"+str(i)+cutoff
+      cpypath="/u/sciteam/$USER/cuo/qwalk/"+el+basis+str(charge)+"_"+method
+
+      contents="#!/bin/bash \n"+\
+      "#PBS -q normal\n"+\
+      "#PBS -l nodes="+str(nodes)+":ppn=32:xe \n"+\
[…]

### 2019-05-06 qwalk/old/naive/genslater.py

@@ -1,0 +1,48 @@
+#Generates multi slater expansions for our calculations
+import numpy as np
+
+cutoff="0p4"
+wmax=0.4 #maximum magnitude of weights
+Ndet=23 #number of determinants in expansion
+N=20 #number of expansions we want, minimum 1
+assert(N>=1)
+
+el='Cu'
+charge=0
+minao={}
+
+#Read in template file 
+i=0
+edit_ind=[] #Indices of lines to edit
+template=[]
+with open("slat_template","r") as f:
+  for line in f:
+    template.append(line)
+    if("##" in line):
+      edit_ind.append(i)
+    i+=1
+f.close()
+
+#Write out slater files
+#for method in ['ROHF','B3LYP','PBE0']:
+#  for basis in ['vdz','vtz']:
+for method in ['B3LYP']:
+  for basis in ['vtz']:
+    for i in range(1,N+1):
+      basename=el+basis+str(charge)+"_"+method
+      
+      w=2*wmax*np.random.rand(Ndet-1)-wmax
+      weights=[1.0]+w.tolist()
+      weights=[str(x) for x in weights]
+      
+      for p in np.arange(0,Ndet+5,5):
+        weights.insert(p,"\n")
+      
+      template[edit_ind[0]]="  ORBFILE "+basename+".orb"+"\n"
+      template[edit_ind[1]]="  INCLUDE "+basename+".basis"+"\n"
+      template[edit_ind[2]]="  OPTIMIZE_DET \n DETWT { "+" ".join(weights)+" }"+"\n"
+      
+      fname=basename+".slater"+str(i)+cutoff
+      fout=open(fname,"w")
+      fout.write("".join(template))
+      fout.close()

### 2019-05-06 qwalk/old/ub3lyp/gather.py

@@ -1,0 +1,94 @@
+import json 
+import pandas as pd
+import numpy as np 
+import sys
+sys.path.append('../../../downfolding/')
+from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
+
+full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
+def gather_all(N,gsw,basename):
+  ''' 
+  Gathers all your data and stores into 
+  '''
+  df=None
+  for j in range(1,N+1):
+    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
+    print(f)
+
+    data=json.load(open(f,'r'))
+    obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
+    energy=data['properties']['total_energy']['value'][0]*27.2114
+    energy_err=data['properties']['total_energy']['error'][0]*27.2114
+
+    one_labels=['n_'+x for x in full_labels]+['4s-3dz2','4s-2pz','3dz2-2pz','3dyz-2py','3dxz-2px']
+    orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
+    orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
+    one_body=sum_onebody(obdm,orb1,orb2)
+    
+    U_labels=['U_'+x for x in full_labels]
+    orb=np.arange(9)
+    U=sum_U(tbdm,orb)
+
+    orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4,0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5]
+    orb2=[1,2,3,4,5,2,3,4,5,3,4,5,4,5,5,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8]
+    J_labels=['J_'+full_labels[orb1[i]]+'_'+full_labels[orb2[i]] for i in range(len(orb1))]
+    J=sum_J(tbdm,orb1,orb2) 
+
[…]

### 2019-05-06 qwalk/old/ub3lyp/geninput_2rdm.py

@@ -1,0 +1,140 @@
+#Generate input files for 2rdm, use same slater files as old 1rdm!
+import os 
+import shutil 
+import numpy as np 
+
+def geninput(N,gsw,basestate,basename):
+  '''
+  input:
+  detgen - type of excitations to sample
+  N - number of states to sample
+  Ndet - number of determinants per state
+  gsw - ground state weight 
+  basename - all written files to basename/__generated file names__
+  output:
+  slater files
+  vmc files 
+  pbs files for vmc
+  '''
+ 
+  #Make sure directory exists, else make it 
+  if not os.path.exists(basename):
+    #Move all important files to there 
+    shutil.copytree('req_files',basename+'/') 
+  else:
+    print('Directory '+str(basename)+' exists, not going to overwrite')
+    exit(0)  
+  fout='gsw'+str(np.round(gsw,2))
+  genslater(N,gsw,basestate,basename,fout)
+  genvmc(N,basename,fout)
+  genpbs(N,basename,fout)
+  return 
+
+def genpbs(N,basename,fout):
+  for j in range(1,N+1):
+    fname=fout+'_'+str(j)
+   
+    #Blue waters input  
+    string='#!/bin/bash\n'+\
+    '#PBS -q secondary\n'+\
+    '#PBS -l nodes=1,flags=allprocs\n'+\
+    '#PBS -l walltime=00:30:00\n'+\
+    '#PBS -N '+fname+'\n'\
+    '#PBS -e '+fname+'.perr\n'+\
+    '#PBS -o '+fname+'.pout\n'+\
+    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
+    'module load intel/18.0\n'+\
+    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
+    'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'
+    
+    f=open(basename+'/'+fname+'.pbs','w')
+    f.write(string)
+    f.close()      
+  return 1
+
+def genvmc(N,basename,fout):
+  for j in range(1,N+1):
+    sysstring='s12.sys'
+    fname=fout+'_'+str(j)
+    
+    string='method {\n'+\
+    '  vmc\n'+\
+    '  nblock 100\n'+\
[…]

### 2019-05-06 qwalk/old/ub3lyp_base_s1/gatherdmc.py

@@ -1,0 +1,69 @@
+import json 
+import pandas as pd
+import numpy as np 
+import sys
+sys.path.append('../../../downfolding/')
+from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
+import os 
+
+full_labels=np.array(["3s","3pz","3py","3px","2pz","3dz2","3dxz","3dyz"])
+def gather_all(N,gsw,basename):
+  ''' 
+  Gathers all your data and stores into 
+  '''
+  df=None
+  for j in range(1,N+1):
+    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.dmc.gosling.json' 
+
+    statinfo=os.stat(f)
+    if(statinfo.st_size>0):
+      print(f)
+      data=json.load(open(f,'r'))
+      obdm,__=get_qwalk_dm(data['properties']['tbdm_basis1'])
+      obdm2,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis2'])
+      energy=data['properties']['total_energy']['value'][0]*27.2114
+      energy_err=data['properties']['total_energy']['error'][0]*27.2114
+
+      print(obdm.shape,obdm2.shape,tbdm.shape)
+
+      #MO ordering
+      #1-body
+      orb1=[0,1,2,3,4,5,6,7,8,9,1,2,3,8,3]
+      orb2=[0,1,2,3,4,5,6,7,8,9,6,7,8,9,9]      
+      mo=sum_onebody(obdm,orb1,orb2)
+      mo_labels=['mo_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
+
+      #IAO ordering (4s, dxy, dyz, dz2, dxz, dx2-y2, px, py, pz)
+      #1-body
+      orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
+      orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
+      iao=sum_onebody(obdm2,orb1,orb2)
+      iao_labels=['iao_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
+    
+      #2-body
+      orb1=[0,1,2,3,4,5,6,7,8]
+      u=sum_U(tbdm,orb1)
+      u_labels=['u'+str(orb1[i]) for i in range(len(orb1))]
+
[…]

### 2019-05-06 qwalk/old/ub3lyp_base_s3/analyze.py

@@ -1,0 +1,153 @@
+import os 
+import numpy as np 
+import pandas as pd
+import seaborn as sns 
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from sklearn import linear_model
+from sklearn.model_selection import cross_val_score
+from sklearn.metrics import mean_squared_error, r2_score
+from diagonalize import diagonalize, new_gs
+from statsmodels.sandbox.regression.predstd import wls_prediction_std
+from sklearn.model_selection import KFold
+
+def collectdf():
+  df=None
+  for basestate in range(10):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='../ub3lyp_mo3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+      print(small_df.shape)
+
+      small_df['Sz']=0.5
+      small_df['basestate']=basestate
+      small_df=small_df.drop(columns=['U4s'])
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      if(df is None): df = small_df
+      else: df = pd.concat((df,small_df),axis=0)
+
+  for basestate in range(6):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+     
+      small_df['Sz']=1.5
+      small_df['basestate']=basestate+10
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      df = pd.concat((df,small_df),axis=0)
+  return df
+
+def analyze(df):
+  #Formatting
+  df['gsw']=np.round(df['gsw'],2)
+  
+  df['n_3s']=df['t_0_0']
+  df['n_3p']=df['t_1_1']+df['t_2_2']+df['t_3_3']
+  df['n_2s']=df['t_4_4']
+  df['n_3dd']=df['t_8_8']+df['t_9_9']
+  df['n_3dpi']=df['t_5_5']+df['t_6_6']
+  df['n_3dz2']=df['t_7_7']
+  df['n_3d']=df['n_3dd']+df['n_3dpi']+df['n_3dz2']
[…]

### 2019-05-06 qwalk/old/ub3lyp_full/analyze.py

@@ -1,0 +1,51 @@
+import os 
+import numpy as np 
+import pandas as pd
+import seaborn as sns 
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from sklearn.linear_model import OrthogonalMatchingPursuit, OrthogonalMatchingPursuitCV 
+from sklearn.model_selection import cross_val_score
+
+def collectdf():
+  df=None
+  for basestate in range(16):
+  #for basestate in [0,2,3,5,6,7,8,9]:
+    for gsw in np.arange(0.1,1.01,0.1):
+      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+      
+      small_df['basestate']=basestate
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      if(df is None): df = small_df
+      else: df = pd.concat((df,small_df),axis=0)
+  return df
+
+def analyze(df):
+  df['gsw']=np.round(df['gsw'],2)
+  #PAIRPLOTS --------------------------------------------------------------------------
+  
+  sns.pairplot(df,vars=['energy','n_3d','n_2pz','n_2ppi'],hue='gsw',markers=['.']*9+['o'])
+  plt.show()
+  exit(0)
+
+  #FITS --------------------------------------------------------------------------
+  y=df['energy']
+  yerr=df['energy_err']
+  X=df[['n_3d']]#,'n_2pz','n_2ppi','3dz2-2pz','4s-2pz','3dpi-2ppi','U_4s']]
+  X=sm.add_constant(X)
+  #for beta in [0,1,2,3,4,5]:
+  for beta in [0]:
+    wls=sm.WLS(y,X,weights=np.exp(-beta*(y-min(y)))).fit()
+    print(wls.summary())
+    #df['pred']=wls.predict(X)
+    #sns.pairplot(df,vars=['energy','pred'],hue='gsw',markers=['.']*9)#,hue='basestate',markers=['o']+['.']*16)
+    plt.plot(wls.predict(X),df['energy'],'o')
+    plt.plot(df['energy'],df['energy'],'--k')
+    plt.xlabel('Predicted (eV)')
+    plt.ylabel('VMC (eV)')
+    plt.show()
+
+if __name__=='__main__':
+  df=collectdf()
+  analyze(df)

### 2019-05-06 qwalk/old/ub3lyp_full/gather.py

@@ -1,0 +1,97 @@
+import json 
+import pandas as pd
+import numpy as np 
+import sys
+sys.path.append('../../../downfolding/')
+from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
+
+full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
+def gather_all(N,gsw,basename):
+  ''' 
+  Gathers all your data and stores into 
+  '''
+  df=None
+  for j in range(1,N+1):
+    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
+    print(f)
+
+    data=json.load(open(f,'r'))
+    obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
+    energy=data['properties']['total_energy']['value'][0]*27.2114
+    energy_err=data['properties']['total_energy']['error'][0]*27.2114
+
+    one_labels=['n_'+x for x in full_labels]+['4s-3dz2','4s-2pz','3dz2-2pz','3dyz-2py','3dxz-2px']
+    orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
+    orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
+    one_body=sum_onebody(obdm,orb1,orb2)
+    
+    U_labels=['U_'+x for x in full_labels]
+    orb=np.arange(9)
+    U=sum_U(tbdm,orb)
+
+    orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4,0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5]
+    orb2=[1,2,3,4,5,2,3,4,5,3,4,5,4,5,5,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8]
+    J_labels=['J_'+full_labels[orb1[i]]+'_'+full_labels[orb2[i]] for i in range(len(orb1))]
+    J=sum_J(tbdm,orb1,orb2) 
+
[…]

### 2019-05-06 qwalk/old/ub3lyp_mo2/analyze.py

@@ -1,0 +1,110 @@
+import os 
+import numpy as np 
+import pandas as pd
+import seaborn as sns 
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from sklearn.linear_model import OrthogonalMatchingPursuit, OrthogonalMatchingPursuitCV 
+from sklearn.model_selection import cross_val_score
+from pyscf import lib,gto,scf,mcscf,fci,lo,ci,cc
+from pyscf.scf import ROHF,UHF,ROKS
+from functools import reduce 
+
+def collectdf():
+  df=None
+  for basestate in range(8):
+    for gsw in np.arange(0.1,1.01,0.1):
+      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+      
+      small_df['basestate']=basestate
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      if(df is None): df = small_df
+      else: df = pd.concat((df,small_df),axis=0)
+  return df
+
+def analyze(df):
+  df['gsw']=np.round(df['gsw'],2)
+  
+  df['n_3dd']=df['t_8_8']+df['t_9_9']
+  df['n_3dpi']=df['t_5_5']+df['t_6_6']
+  df['n_3dz2']=df['t_7_7']
+  df['n_3d']=df['n_3dd']+df['n_3dpi']+df['n_3dz2']
+  df['n_2ppi']=df['t_10_10']+df['t_11_11']
+  df['n_2pz']=df['t_12_12']
+  df['n_2p']=df['n_2ppi']+df['n_2pz']
+  df['n_4s']=df['t_13_13']
+  df['t_pi']=2*(df['t_5_10']+df['t_6_11'])
+  df['t_dz']=2*df['t_7_12']
+  df['t_ds']=2*df['t_7_13']
+  df['t_sz']=2*df['t_12_13']
+
+  #PAIRPLOTS --------------------------------------------------------------------------
+  #sns.pairplot(df,vars=['energy','n_3dd','n_3dpi','n_3dz2','n_3d'],hue='basestate',markers=['o']+['.']*8)
[…]

### 2019-05-06 qwalk/old/ub3lyp_mo2/geninputdmc.py

@@ -1,0 +1,91 @@
+#Generate input files for 2rdm, use same slater files as old 1rdm!
+import os 
+import shutil 
+import numpy as np 
+
+def geninput(N,gsw,basestate,basename):
+  '''
+  input:
+  detgen - type of excitations to sample
+  N - number of states to sample
+  Ndet - number of determinants per state
+  gsw - ground state weight 
+  basename - all written files to basename/__generated file names__
+  output:
+  slater files
+  vmc files 
+  pbs files for vmc
+  '''
+ 
+  #Make sure directory exists, else make it 
+  if not os.path.exists(basename):
+    print('Directory '+str(basename)+' doesnt exists, not going to write DMC')
+    exit(0)  
+  fout='gsw'+str(np.round(gsw,2))
+  gendmc(N,basename,fout)
+  genpbs(N,basename,fout)
+  return 
+
+def genpbs(N,basename,fout):
+  for j in range(1,N+1):
+    fname=fout+'_'+str(j)
+   
+    #Blue waters input  
+    string='#!/bin/bash\n'+\
+    '#PBS -q secondary\n'+\
+    '#PBS -l nodes=1,flags=allprocs\n'+\
+    '#PBS -l walltime=04:00:00\n'+\
+    '#PBS -N '+fname+str(j)+'\n'\
+    '#PBS -e '+fname+str(j)+'.perr\n'+\
+    '#PBS -o '+fname+str(j)+'.pout\n'+\
+    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
+    'module load intel/18.0\n'+\
+    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
+    'mpiexec ../../../../mainline/bin/qwalk '+fname+'.dmc &> '+fname+'.dmc.out\n'
+    
+    f=open(basename+'/'+fname+'.dmc.pbs','w')
+    f.write(string)
+    f.close()      
+  return 1
+
+def gendmc(N,basename,fout):
+  for j in range(1,N+1):
+    sysstring='s12.sys'
+    fname=fout+'_'+str(j)
+    
+    string='method {\n'+\
+    '  dmc\n'+\
+    '  nblock 25\n'+\
+    '  timestep 0.01 \n'+\
+    '  tmoves \n'+\
+    '  average { tbdm_basis\n'+\
+    '    mode obdm\n'+\
+    '    orbitals {\n'+\
[…]

### 2019-05-06 qwalk/old/ub3lyp_mo3/analyze.py

@@ -1,0 +1,124 @@
+import os 
+import numpy as np 
+import pandas as pd
+import seaborn as sns 
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from sklearn import linear_model
+from sklearn.model_selection import cross_val_score
+from sklearn.metrics import mean_squared_error, r2_score
+from diagonalize import diagonalize, new_gs
+from statsmodels.sandbox.regression.predstd import wls_prediction_std
+
+def collectdf():
+  df=None
+  for basestate in range(10):
+    for gsw in np.arange(0.1,1.01,0.1):
+      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+      
+      small_df['basestate']=basestate
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      if(df is None): df = small_df
+      else: df = pd.concat((df,small_df),axis=0)
+  return df
+
+def analyze(df):
+  #Formatting
+  df['gsw']=np.round(df['gsw'],2)
+  df['n_3dd']=df['t_8_8']+df['t_9_9']
+  df['n_3dpi']=df['t_5_5']+df['t_6_6']
+  df['n_3dz2']=df['t_7_7']
+  df['n_3d']=df['n_3dd']+df['n_3dpi']+df['n_3dz2']
+  df['n_2ppi']=df['t_10_10']+df['t_11_11']
+  df['n_2pz']=df['t_12_12']
+  df['n_2p']=df['n_2ppi']+df['n_2pz']
+  df['n_4s']=df['t_13_13']
+  df['t_pi']=2*(df['t_5_10']+df['t_6_11'])
+  df['t_dz']=2*df['t_7_12']
+  df['t_ds']=2*df['t_7_13']
+  df['t_sz']=2*df['t_12_13']
+
+  #PAIRPLOTS --------------------------------------------------------------------------
+  #sns.pairplot(df,vars=['energy','n_3dd','n_3dpi','n_3dz2','n_3d'],hue='basestate',markers=['o']+['.']*10)
+  #sns.pairplot(df,vars=['energy','n_2ppi','n_2pz','n_2p','n_4s'],hue='basestate',markers=['o']+['.']*10)
[…]

### 2019-05-06 qwalk/old/ub3lyp_mo_hispin/diagonalize.py

@@ -1,0 +1,45 @@
+import numpy as np 
+import matplotlib.pyplot as plt
+def diagonalize(parms):
+  print(parms)
+  e4s,e3d,epi,ez,tpi,tds,tdz,tsz=parms
+  H=np.diag([e3d,e3d,e3d,e3d,e3d,epi,epi,ez,e4s])
+  
+  #e4s,e3dpi,e3dz2,e3dd,epi,ez,tpi,tds,tdz,tsz=parms
+  #H=np.diag([e3dpi,e3dpi,e3dz2,e3dd,e3dd,epi,epi,ez,e4s])
+
+  #dx, dy, dz2, dd, dd, px, py, pz, 4s
+  H[[0,1,5,6],[5,6,0,1]]=tpi
+  H[[2,7],[7,2]]=tdz
+  H[[7,8],[8,7]]=tsz
+  H[[2,8],[8,2]]=tds
+
+  w,vr=np.linalg.eigh(H)
+  #print(w)
+  #print(vr.T)
+  #exit(0)
+  return(w-w[0])
+
+def new_gs(parms):
+  print(parms)
+  e4s,e3d,epi,ez,tpi,tds,tdz,tsz=parms
+  
+  #dx, dy, dz2, dd, px, py, pz, 4s
+  H=np.diag([e3d,e3d,e3d,e3d,e3d,epi,epi,ez,e4s])
+  H[[0,1,5,6],[5,6,0,1]]=tpi
+  H[[2,7],[7,2]]=tdz
+  H[[7,8],[8,7]]=tsz
+  H[[2,8],[8,2]]=tds
+
+  w,vr=np.linalg.eigh(H)
+
+  from pyscf import lib,gto,scf,mcscf,fci,lo,ci,cc
+  from pyscf.scf import ROHF,UHF,ROKS
+  from pyscf2qwalk import print_qwalk_mol
+  chkfile="../../pyscf/chk/Cuvtz_r1.725_s1_B3LYP_1.chk"
+  mol=lib.chkfile.load_mol(chkfile)
+  m=ROKS(mol)
+  m.__dict__.update(lib.chkfile.load(chkfile, 'scf'))
+  
+  m.mo_coeff[:,5:14]=np.dot(m.mo_coeff[:,5:14],vr)
+  print_qwalk_mol(mol,m,basename="new_gs/new_gs")

### 2019-05-06 qwalk/old/ub3lyp_s1/makejsondmc.py

@@ -1,0 +1,26 @@
+import os 
+import numpy as np 
+
+def makejson(N,gsw,basename):
+  for j in range(1,N+1):
+    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.dmc'
+    print(f)
+    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
+  
+    #Replace labels in JSON 
+    json_f=open(f+'.gosling.json','r').read().split("\n")
+    i=1 
+    for j in range(len(json_f)):
+      if('tbdm_basis' in json_f[j]): 
+        json_f[j]='"tbdm_basis'+str(i)+'":{'
+        i+=1
+    json_o=open(f+'.gosling.json','w')
+    json_o.write('\n'.join(json_f))
+  return 1
+
+if __name__=='__main__':
+  for basestate in np.arange(10):
+    for gsw in [0.2,0.4,0.6,0.8,1.0]:
+      N=5
+      if(gsw==1.0): N=1      
+      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/old/ub3lyp_s1_/testing_fit.py

@@ -1,0 +1,47 @@
+import numpy as np 
+import matplotlib.pyplot as plt
+from scipy.optimize import minimize
+import pandas as pd 
+import statsmodels.api as sm
+from statsmodels.sandbox.regression.predstd import wls_prediction_std
+
+def pred(b,x):
+  return b[0] + b[1]*x
+
+def r(u,tau):
+  return np.abs(tau - (u<0).astype(int))*u**2
+
+def cost(b,x,y,s,w=None):
+  if(w is None): w=np.ones(len(y))
+  yhat = pred(b,x)
+  res = y - yhat
+  z=(y-min(y))/s
+
+  #tau=1/2 for z<1, energy under the scale we set
+  c=np.sum(w[z<1]*r(res[z<1],0.5))
+  #tau=1 for z>1, energy above the scale we set 
+  c+=np.sum(w[z>=1]*r(res[z>=1],1.0))
+  return c
+
+x=np.arange(100)
+y=2*x + np.random.normal(size=x.shape[0])
+y[20:]+=np.random.normal(size=80)*y[20:]/10
+b0=[0,2]
+s=40
+w=np.exp(-(1./s)*(y-min(y)))
+
+res_exp = minimize(lambda b: cost(b,x,y,s,w), b0).x
+#res_ols = minimize(lambda b: cost(b,x,y,1e200,w), b0).x
+
+X=pd.DataFrame({'X':x})
+X=sm.add_constant(X)
+ols=sm.WLS(y,X,weights=w).fit()
+__, l, u = wls_prediction_std(ols,alpha=0.10)
+pred_err=(u-l)/2
+
+plt.plot(x,y,'ob',label='DATA')
+plt.errorbar(x,res_exp[0]+res_exp[1]*x,xerr=pred_err,fmt='-g',label='EXP')
+plt.errorbar(x,ols.predict(),xerr=pred_err,fmt='-k',label='OLS')
+plt.legend(loc='best')
+plt.show()
+#plt.savefig('testing_fit.pdf')

### 2019-05-06 qwalk/old/ub3lyp_s3/geninputdmc.py

@@ -1,0 +1,100 @@
+#Generate input files for 2rdm, use same slater files as old 1rdm!
+import os 
+import shutil 
+import numpy as np 
+
+def geninput(N,gsw,basestate,basename):
+  '''
+  input:
+  detgen - type of excitations to sample
+  N - number of states to sample
+  Ndet - number of determinants per state
+  gsw - ground state weight 
+  basename - all written files to basename/__generated file names__
+  output:
+  slater files
+  vmc files 
+  pbs files for vmc
+  '''
+ 
+  #Make sure directory exists, else make it 
+  if not os.path.exists(basename):
+    print('Directory '+str(basename)+' doesnt exists, not going to write DMC')
+    exit(0)  
+  fout='gsw'+str(np.round(gsw,2))
+  gendmc(N,basename,fout)
+  genpbs(N,basename,fout)
+  return 
+
+def genpbs(N,basename,fout):
+  #BW input
+  for i in range(1,N+1):
+    fname=fout+'_'+str(i)
+    string='#!/bin/bash\n'+\
+    '#PBS -q low\n'+\
+    '#PBS -l nodes=8:ppn=32:xe\n'+\
+    '#PBS -l walltime=04:00:00\n'+\
+    '#PBS -N '+fname+'\n'\
+    '#PBS -e '+fname+'.perr\n'+\
+    '#PBS -o '+fname+'.pout\n'+\
+    'mkdir -p /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
+    'cd /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
+    'cp -u /u/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/* .\n'+\
+    'aprun -n 256 /u/sciteam/$USER/fork/bin/qwalk '+fname+'.dmc &> '+fname+'.dmc.out\n'     
+    f=open(basename+'/'+fname+'.dmc.pbs','w')
+    f.write(string)
+    f.close()
+  else: pass
+  return 1
+
+def gendmc(N,basename,fout):
+  for j in range(1,N+1):
+    sysstring='s32.sys'
+    fname=fout+'_'+str(j)
+    
+    string='method {\n'+\
+    '  dmc\n'+\
+    '  nblock 25\n'+\
+    '  timestep 0.01\n'+\
[…]

### 2019-05-06 qwalk/old/ub3lyp_so_s1/analyze.py

@@ -1,0 +1,175 @@
+import os 
+import numpy as np 
+import pandas as pd
+import seaborn as sns 
+import matplotlib.pyplot as plt
+import statsmodels.api as sm
+from sklearn import linear_model
+from sklearn.model_selection import cross_val_score
+from sklearn.metrics import mean_squared_error, r2_score
+from diagonalize import diagonalize, new_gs
+from statsmodels.sandbox.regression.predstd import wls_prediction_std
+from sklearn.model_selection import KFold
+
+def collectdf():
+  df=None
+  for basestate in range(10):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+
+      small_df['Sz']='0.5_s'
+      small_df['basestate']=basestate
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      if(df is None): df = small_df
+      else: df = pd.concat((df,small_df),axis=0)
+  
+  '''
+  for basestate in range(6):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='../ub3lyp_do_s1/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+     
+      small_df['Sz']='0.5_d'
+      small_df['basestate']=basestate+10
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      df = pd.concat((df,small_df),axis=0)
+  '''
+
+  for basestate in range(6):
+    for gsw in np.arange(0.1,1.1,0.1):
+      f='../ub3lyp_so_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
+      small_df=pd.read_pickle(f)
+     
+      small_df['Sz']='1.5_s'
+      small_df['basestate']=basestate+16
+      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
+      df = pd.concat((df,small_df),axis=0)
[…]

### 2019-05-06 qwalk/old/vmc/attic/reduce.py

@@ -1,0 +1,214 @@
+import pandas as pd 
+import numpy as np 
+import matplotlib.pyplot as plt
+
+flist=['run1s/ex2_s_Ndet10_gsw0.7_gosling.pickle']#,'run2a/a_Ndet10_gsw0.8_gosling.pickle']
+#flist=['run2a/a_Ndet10_gsw0.8_gosling.pickle']
+df=None
+for f in flist:
+  if(df is None): df=pd.read_pickle(f)
+  else: df=pd.concat((df,pd.read_pickle(f)),axis=0)
+
+print(list(df))
+
+labels=["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"]
+
+#Energy units
+df['energy']*=27.2114 #eV
+df['energy_err']*=27.2114
+
+#1-body 
+nu=['obdm_up_'+i+'_'+j for i in labels for j in labels]
+nd=['obdm_down_'+i+'_'+j for i in labels for j in labels]
+ntot=['obdm_'+i+'_'+j for i in labels for j in labels]
+n=df[nu].values+df[nd].values
+nu=['obdm_up_'+i+'_'+i for i in labels]
+nd=['obdm_down_'+i+'_'+i for i in labels]
+print(df[nu].iloc[0])
+print(df[nd].iloc[0])
+exit(0)
+
+df[ntot]=pd.DataFrame(n,index=df.index)
+df=df.drop(columns=nd+nu)
+n=['obdm_'+str(i)+'_'+str(i) for i in labels]
+t=['obdm_4s_2pz','obdm_4s_3dz2','obdm_3dyz_2py','obdm_3dz2_2pz','obdm_3dxz_2px']
+
+#Us
+Ulabels=['tbdm_updown_%s_%s_%s_%s'%(s,s,s,s) for s in labels]
+
+#Vs
+Vlabels=[]
+for i in range(len(labels)):
+  for j in range(i+1,len(labels)):
+    curr_label='tbdm_V_%s_%s'%(labels[i],labels[j])
+    df[curr_label]=0
[…]

### 2019-05-06 qwalk/old/vmc/attic/run1a_1body/analyze.py

@@ -1,0 +1,69 @@
+import seaborn as sns
+import matplotlib.pyplot as plt
+import statsmodels.api as sm 
+import pandas as pd
+import numpy as np
+from sklearn.model_selection import cross_val_score
+from sklearn.linear_model import OrthogonalMatchingPursuit
+
+fname='a_Ndet10_gsw0.9_df.pickleR'
+df=pd.read_pickle(fname)
+#sns.pairplot(df.drop(columns=['energy_err']))
+#plt.savefig('s_Ndet10_gsw0.7_pairplot.pdf')
+#exit(0)
+
+y=df['energy']
+X=df.drop(columns=['energy','energy_err','obdm_2pz_2pz'])
+
+#OLS
+X=sm.add_constant(X)
+ols=sm.OLS(y,X).fit()
+print(ols.summary())
+
+plt.ylabel('E_VMC (eV)')
+plt.xlabel('E_Pred (eV)')
+plt.errorbar(ols.predict(X),y,yerr=df['energy_err'],fmt='bo')
+plt.plot(y,y,'g--')
+plt.title('Full active space 1-body fit')
+#plt.savefig('s_Ndet10_gsw0.7_df.pdf')
+plt.show()
+
+#OMP
+cscores=[]
+cscores_err=[]
+scores=[]
+conds=[]
+nparms=[]
+for i in range(1,X.shape[1]+1):
+  print("n_nonzero_coefs="+str(i))
+  omp = OrthogonalMatchingPursuit(n_nonzero_coefs=i)
+  omp.fit(X,y)
+  nparms.append(i)
+  scores.append(omp.score(X,y))
+  tmp=cross_val_score(omp,X,y,cv=5)
+  cscores.append(tmp.mean())
+  cscores_err.append(tmp.std()*2)
+  print("R2: ",omp.score(X,y))
+  print("R2CV: ",tmp.mean(),"(",tmp.std()*2,")")
+  ind=np.abs(omp.coef_)>0
+  Xr=X.values[:,ind]
+  conds.append(np.linalg.cond(Xr))
+  print("Cond: ",np.linalg.cond(Xr))
+  print(np.array(list(X))[ind])
+  print(omp.coef_[ind])
+
+  plt.title(fname)
+  plt.xlabel("Predicted energy (eV)")
+  plt.ylabel("DFT Energy (eV)")
+  plt.plot(omp.predict(X),y,'og')
+  plt.plot(y,y,'b-')
[…]

### 2019-05-06 qwalk/old/vmc/attic/run2s_1body/reducedf.py

@@ -1,0 +1,59 @@
+import pandas as pd 
+import numpy as np 
+
+fname='s_Ndet10_gsw0.7_df.pickle'
+df=pd.read_pickle(fname)
+
+#Correct labels
+labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
+iaos=  np.array([ 2,   6,     7,     8,     9,     10,      12,   13,   14])
+fix_cols=[]
+for col in list(df):
+  l=col.split("_")
+  if(len(l)>=4):
+    a=int(col.split("_")[2])
+    b=int(col.split("_")[3])
+    i=np.where(iaos==a)[0][0]
+    j=np.where(iaos==b)[0][0]
+    fix_col=col.split("_")
+    fix_col[2]=labels[i]
+    fix_col[3]=labels[j]
+    fix_col='_'.join(fix_col)
+  else: fix_col=col
+  fix_cols.append(fix_col)
+df.columns=fix_cols
+
+#Energy units
+df['energy']*=27.2114 #eV
+df['energy_err']*=27.2114
+
+#Sum over spins
+nu=['obdm_up_'+i+'_'+j for i in labels for j in labels]
+nd=['obdm_down_'+i+'_'+j for i in labels for j in labels]
+ntot=['obdm_'+i+'_'+j for i in labels for j in labels]
+n=df[nu].values+df[nd].values
+df[ntot]=pd.DataFrame(n,index=df.index)
+df=df.drop(columns=nd+nu)
+
+nu=[x+'_err' for x in nu]
+nd=[x+'_err' for x in nd]
+ntot=[x+'_err' for x in ntot]
+n=np.sqrt(df[nu].values**2 + df[nd].values**2)
+df[ntot]=pd.DataFrame(n,index=df.index)
+df=df.drop(columns=nd+nu)
+
+#Reduced DF
+n=['obdm_'+str(i)+'_'+str(i) for i in labels]
+t=['obdm_4s_2pz','obdm_4s_3dz2','obdm_3dyz_2py','obdm_3dz2_2pz','obdm_3dxz_2px']
+rdf=df[['energy']+['energy_err']+n+t]
+rdf['obdm_3dpi_3dpi']=rdf['obdm_3dxz_3dxz']+rdf['obdm_3dyz_3dyz']
[…]

### 2019-05-06 qwalk/old/vmc_eq/gather.py

@@ -1,0 +1,149 @@
+import json 
+import pandas as pd
+import numpy as np 
+import sys
+sys.path.append('../../../downfolding/')
+from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
+
+full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
+def gather_all(detgen,N,Ndet,gsw,basename):
+  ''' 
+  Gathers all your data and stores into 
+  '''
+  df=None
+  for j in range(N+1):
+    #for name in ['gs0','gs1','gs2','gs3','gs4','gs5','gs2_lo','gs3_lo','gs5_lo']:
+<<<<<<< HEAD
+    #for name in ['gs0','gs1','gs2','gs3','gs4','gs5']:
+    for name in ['gs2','gs2_lo','gs2_alt']:
+      if(j==0): f='base/'+name+'.vmc_tbdm.gosling.json'  #GS
+      else: f=basename+'/'+name+'_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(gsw)+'_'+str(j)+'.vmc.gosling.json'
+      print(f) 
+=======
+    for name in ['gs0','gs1','gs2','gs3','gs4','gs5']:
+      if(j==0): f='base/'+name+'.vmc_tbdm.gosling.json'  #GS
+      else: f=basename+'/'+name+'_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(gsw)+'_'+str(j)+'.vmc.gosling.json'
+      
+>>>>>>> 25bfdb4a0a27ebfa182c5df1472ce635d5a718b6
+      data=json.load(open(f,'r'))
+      obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
+      energy=data['properties']['total_energy']['value'][0]*27.2114
+      energy_err=data['properties']['total_energy']['error'][0]*27.2114
[…]

### 2019-05-06 qwalk/old/vmc_eq/span_sampling/geninput_2rdm.py

@@ -1,0 +1,169 @@
+#Generate input files for 2rdm, use same slater files as old 1rdm!
+import os 
+import shutil 
+import numpy as np 
+
+def geninput(spin,N,gsw,basename):
+  '''
+  input:
+  detgen - type of excitations to sample
+  N - number of states to sample per spin (2*N states in total)
+  Ndet - number of determinants per state
+  gsw - ground state weight 
+  basename - all written files to basename/__generated file names__
+  output:
+  slater files
+  vmc files 
+  pbs files for vmc
+  '''
+ 
+  #Make sure directory exists, else make it 
+  if not os.path.exists(basename):
+    #Move all important files to there 
+    shutil.copytree('req_files',basename+'/') 
+  else:
+    print('Directory '+str(basename)+' exists, not going to overwrite')
+    exit(0)  
+  fout='S'+str(spin)+'_gsw'+str(np.round(gsw,2))
+  genslater(spin,N,gsw,basename,fout)
+  genvmc(spin,N,basename,fout)
+  genpbs(N,basename,fout)
+  return 
+
+def genpbs(N,basename,fout):
+  for j in range(1,N+1):
+    fname=fout+'_'+str(j)
+   
+    #Blue waters input  
+    string='#!/bin/bash\n'+\
+    '#PBS -q secondary\n'+\
+    '#PBS -l nodes=1,flags=allprocs\n'+\
+    '#PBS -l walltime=00:30:00\n'+\
+    '#PBS -N '+fname+'\n'\
+    '#PBS -e '+fname+'.perr\n'+\
+    '#PBS -o '+fname+'.pout\n'+\
+    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
+    'module load intel/18.0\n'+\
+    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
+    'mpiexec ../../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'
+    
+    f=open(basename+'/'+fname+'.pbs','w')
+    f.write(string)
+    f.close()      
+  return 1
+
+def genvmc(spin,N,basename,fout):
+  for j in range(1,N+1):
[…]

### 2019-05-06 qwalk/sampling_test/nchoose10_sgn1/collect_data.py

@@ -1,68 +1,0 @@
-#Collect all data into one place 
-
-import json 
-
-G=[]   #Ground state weight 
-S=[]   #Sample
-E=[]   #Total energy
-Err=[] #Error bar
-Pd=[]  #Parameter derivatives
-Pderr=[] #Parameter derivative errors
-Ed=[]  #Energy derivatives
-Ederr=[] #Energy derivative errors
-Nd=[]  #Derivative number
-
-for s in range(1,10):
-  for g in range(1,10):
-    with open("Cuvtz0_B3LYP_s"+str(s)+"_g0."+str(g)+".vmc.data","r") as f:
-      for line in f:
-        if("total_energy0" in line):
-          sp1=line.split("+/-")
-          for i in range(10):
-            E.append(float(sp1[0].split(" ")[-2]))
-            Err.append(float(sp1[1].split("(")[0]))
-            Nd.append(i)
-            G.append(g)
-            S.append(s)
-        if("Wave function derivatives" in line):
-          pd=[]
-          pderr=[]
-          for i in range(10):
-            l=next(f).split("+/-")
-            Pd.append(float(l[0]))
-            Pderr.append(float(l[1]))
-        if("Derivative of the energy" in line):
-          ed=[]
-          ederr=[]
-          for i in range(10):
-            l=next(f).split("+/-")
-            Ed.append(float(l[0]))
-            Ederr.append(float(l[1]))
-    f.close()
-
-print(len(E),len(Err),len(G),len(S),len(Pd),len(Pderr),len(Ed),len(Ederr))
-d={'Nd':Nd,'E':E,'Err':Err,'G':G,'S':S,'Pd':Pd,'Pderr':Pderr,'Ed':Ed,'Ederr':Ederr}
-json.dump(d,open("collect_data.json","w"))
-
-'''
-import pandas as pd
-import matplotlib.pyplot as plt
-
-d=json.load(open("energy.json","r"))
-df=pd.DataFrame(d)
-
-#Ground state
-E0=-213.361501
-err0=0.001006581014
-df['E']-=E0
-df['E']*=27.2
-df['Err']*=27.2
-
-for S in range(max(d['S'])):
-  ind=(df['S']==S)
-  plt.errorbar(df['G'][ind]*0.1,df['E'][ind],yerr=df['Err'][ind],marker='o')
-
-plt.ylabel("E(VMC) - E0(VMC), eV")
-plt.xlabel("Ground state weight")
-plt.show()
-'''

### 2019-05-06 qwalk/targeted_casscf/base/analyze_base.py

@@ -1,8 +1,0 @@
-import pandas as pd
-import seaborn as sns
-import matplotlib.pyplot as plt
-
-df=pd.read_pickle('base_gosling.pickle')
-df['energy']-=min(df['energy'])
-df=df.sort_values(by=['energy'])
-print(df[['base_state','energy','n_3d','n_4s','n_2ppi','n_2pz','J_4s_3d']])

### 2019-05-06 qwalk/ub3lyp/gather.py

@@ -1,94 +1,0 @@
-import json 
-import pandas as pd
-import numpy as np 
-import sys
-sys.path.append('../../../downfolding/')
-from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
-
-full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
-def gather_all(N,gsw,basename):
-  ''' 
-  Gathers all your data and stores into 
-  '''
-  df=None
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
-    print(f)
-
-    data=json.load(open(f,'r'))
-    obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
-    energy=data['properties']['total_energy']['value'][0]*27.2114
-    energy_err=data['properties']['total_energy']['error'][0]*27.2114
-
-    one_labels=['n_'+x for x in full_labels]+['4s-3dz2','4s-2pz','3dz2-2pz','3dyz-2py','3dxz-2px']
-    orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
-    orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
-    one_body=sum_onebody(obdm,orb1,orb2)
-    
-    U_labels=['U_'+x for x in full_labels]
-    orb=np.arange(9)
-    U=sum_U(tbdm,orb)
-
-    orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4,0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5]
-    orb2=[1,2,3,4,5,2,3,4,5,3,4,5,4,5,5,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8]
-    J_labels=['J_'+full_labels[orb1[i]]+'_'+full_labels[orb2[i]] for i in range(len(orb1))]
-    J=sum_J(tbdm,orb1,orb2) 
-
[…]

### 2019-05-06 qwalk/ub3lyp_3/subpbsdmc.py

@@ -1,0 +1,15 @@
+import os 
+import numpy as np 
+
+def subpbs(N,gsw,basestate,basename):
+  fout='gsw'+str(np.round(gsw,2))
+  for j in range(1,N+1):
+    fname=basename+'/'+fout+'_'+str(j)+'.dmc.pbs'
+    os.system('qsub '+fname)
+
+if __name__=='__main__':
+  for basestate in np.arange(7):
+    for gsw in np.arange(0.1,1.1,0.1):
+      if(gsw==1.0): N=1
+      else: N=10
+      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_base_s1/analyzedmc.py

@@ -1,240 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-#from diagonalize import diagonalize, new_gs
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-
-def collectdf():
-  df=None
-  for basestate in range(10):
-    for gsw in [1.0]:
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-
-      small_df['Sz']=0.5
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0,sort=True)
-
-  for basestate in range(6):
-    for gsw in [1.0]:
-      f='../ub3lyp_base_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-     
-      small_df['Sz']=1.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  return df
-
-def analyze(df):
-  #Formatting
-  df['mo_n_3dd']=df['mo_4_4']+df['mo_5_5']
-  df['mo_n_3dpi']=df['mo_1_1']+df['mo_2_2']
-  df['mo_n_3dz2']=df['mo_3_3']
-  df['mo_n_3d']=df['mo_n_3dd']+df['mo_n_3dpi']+df['mo_n_3dz2']
-  df['mo_n_2ppi']=df['mo_6_6']+df['mo_7_7']
-  df['mo_n_2pz']=df['mo_8_8']
-  df['mo_n_2p']=df['mo_n_2ppi']+df['mo_n_2pz']
-  df['mo_n_4s']=df['mo_9_9']
-  df['mo_t_pi']=2*(df['mo_1_6']+df['mo_2_7'])
-  df['mo_t_dz']=2*df['mo_3_8']
-  df['mo_t_sz']=2*df['mo_8_9']
[…]

### 2019-05-06 qwalk/ub3lyp_base_s1/makejson.py

@@ -1,25 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.vmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  
-    #Replace labels in JSON 
-    json_f=open(f+'.gosling.json','r').read().split("\n")
-    i=1 
-    for j in range(len(json_f)):
-      if('tbdm_basis' in json_f[j]): 
-        json_f[j]='"tbdm_basis'+str(i)+'":{'
-        i+=1
-    json_o=open(f+'.gosling.json','w')
-    json_o.write('\n'.join(json_f))
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(10):
-    for gsw in [1.0]:
-      N=1  
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_base_s3/diagonalize.py

@@ -1,41 +1,0 @@
-import numpy as np 
-import matplotlib.pyplot as plt
-def diagonalize(parms):
-  e4s,e3d,epi,ez,tpi,tds,tdz,tsz=parms
-  H=np.diag([e3d,e3d,e3d,e3d,e3d,epi,epi,ez,e4s])
-  
-  #e4s,e3dpi,e3dz2,e3dd,epi,ez,tpi,tds,tdz,tsz=parms
-  #H=np.diag([e3dpi,e3dpi,e3dz2,e3dd,e3dd,epi,epi,ez,e4s])
-
-  #dx, dy, dz2, dd, px, py, pz, 4s
-  H[[0,1,5,6],[5,6,0,1]]=tpi
-  H[[2,7],[7,2]]=tdz
-  H[[7,8],[8,7]]=tsz
-  H[[2,8],[8,2]]=-tds
-
-  w,vr=np.linalg.eigh(H)
-  return(w-w[0])
-
-def new_gs(parms):
-  print(parms)
-  e4s,e3d,epi,ez,tpi,tds,tdz,tsz=parms
-  
-  #dx, dy, dz2, dd, px, py, pz, 4s
-  H=np.diag([e3d,e3d,e3d,e3d,e3d,epi,epi,ez,e4s])
-  H[[0,1,5,6],[5,6,0,1]]=tpi
-  H[[2,7],[7,2]]=tdz
-  H[[7,8],[8,7]]=tsz
-  H[[2,8],[8,2]]=tds
-
-  w,vr=np.linalg.eigh(H)
-
-  from pyscf import lib,gto,scf,mcscf,fci,lo,ci,cc
-  from pyscf.scf import ROHF,UHF,ROKS
-  from pyscf2qwalk import print_qwalk_mol
-  chkfile="../../pyscf/chk/Cuvtz_r1.725_s1_B3LYP_1.chk"
-  mol=lib.chkfile.load_mol(chkfile)
-  m=ROKS(mol)
-  m.__dict__.update(lib.chkfile.load(chkfile, 'scf'))
-  
-  m.mo_coeff[:,5:14]=np.dot(m.mo_coeff[:,5:14],vr)
-  print_qwalk_mol(mol,m,basename="new_gs/new_gs")

### 2019-05-06 qwalk/ub3lyp_base_s3/makejson.py

@@ -1,25 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.vmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  
-    #Replace labels in JSON 
-    json_f=open(f+'.gosling.json','r').read().split("\n")
-    i=1 
-    for j in range(len(json_f)):
-      if('tbdm_basis' in json_f[j]): 
-        json_f[j]='"tbdm_basis'+str(i)+'":{'
-        i+=1
-    json_o=open(f+'.gosling.json','w')
-    json_o.write('\n'.join(json_f))
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(6):
-    for gsw in [1.0]:
-      N=1  
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_d10_s1/analyzedmc.py

@@ -1,284 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-#from diagonalize import diagonalize, new_gs
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-from scipy import stats
-
-######################################################################################
-#FROZEN METHODS
-
-#Collect df
-def collect_df():
-  df=None
-  for basestate in range(6):
-    for gsw in np.arange(0.1,1.1,0.1):
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=0.5
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0,sort=True)
-  '''
-  for basestate in range(2):
-    for gsw in np.arange(0.1,1.1,0.1):
-      f='../ub3lyp_d10_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-    
-      small_df['basestate']=basestate+6
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=1.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  '''
-  return df
-
-#Formatting
-def format_df(df):
-  df['mo_n_3dd']=df['mo_4_4']+df['mo_5_5']
-  df['mo_n_3dpi']=df['mo_1_1']+df['mo_2_2']
-  df['mo_n_3dz2']=df['mo_3_3']
[…]

### 2019-05-06 qwalk/ub3lyp_d10_s1/copy_output.py

@@ -1,9 +1,0 @@
-import os
-import numpy as np 
-
-for gsw in np.arange(0.1,1.1,0.1):
-  for basestate in np.arange(6):
-    dir='gsw'+str(np.round(gsw,2))+'b'+str(basestate)
-    print(dir)
-    os.system('cp -u ~/scratch/cuo/qwalk/ub3lyp_d10_s1/'+dir+'/*.log ./'+dir)
-    os.system('cp -u ~/scratch/cuo/qwalk/ub3lyp_d10_s1/'+dir+'/*.o ./'+dir)

### 2019-05-06 qwalk/ub3lyp_d10_s3/geninput.py

@@ -1,159 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  genslater(N,gsw,basestate,basename,fout)
-  #genvmc(N,basename,fout)
-  #genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  #BW input
-  for i in range(1,N+1):
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q low\n'+\
-    '#PBS -l nodes=1:ppn=32:xe\n'+\
-    '#PBS -l walltime=01:00:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'mkdir -p /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_d10_s3/'+basename+'/\n'+\
-    'cd /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_d10_s3/'+basename+'/\n'+\
-    'cp -u /u/sciteam/$USER/cuo/qwalk/ub3lyp_d10_s3/'+basename+'/* .\n'+\
-    'aprun -n 32 /u/sciteam/$USER/fork/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'   
-
-    f=open(basename+'/'+fname+'.pbs','w')
-    f.write(string)
-    f.close()
-  return 1
-
-def genvmc(N,basename,fout):
-  for j in range(1,N+1):
-    sysstring='s32.sys'
[…]

### 2019-05-06 qwalk/ub3lyp_do/geninput.py

@@ -1,160 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  genslater(N,gsw,basestate,basename,fout)
-  #genvmc(N,basename,fout)
-  #genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  #BW input
-  for i in range(1,N+1):
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q low\n'+\
-    '#PBS -l nodes=1:ppn=32:xe\n'+\
-    '#PBS -l walltime=01:00:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'mkdir -p /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_do/'+basename+'/\n'+\
-    'cd /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_do/'+basename+'/\n'+\
-    'cp -u /u/sciteam/$USER/cuo/qwalk/ub3lyp_do/'+basename+'/* .\n'+\
-    'aprun -n 32 /u/sciteam/$USER/fork/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'   
-
-    f=open(basename+'/'+fname+'.pbs','w')
-    f.write(string)
-    f.close()
-  return 1
-
-def genvmc(N,basename,fout):
-  for j in range(1,N+1):
-    sysstring='s12.sys'
-    fname=fout+'_'+str(j)
[…]

### 2019-05-06 qwalk/ub3lyp_full/gather.py

@@ -1,97 +1,0 @@
-import json 
-import pandas as pd
-import numpy as np 
-import sys
-sys.path.append('../../../downfolding/')
-from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
-
-full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
-def gather_all(N,gsw,basename):
-  ''' 
-  Gathers all your data and stores into 
-  '''
-  df=None
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
-    print(f)
-
-    data=json.load(open(f,'r'))
-    obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
-    energy=data['properties']['total_energy']['value'][0]*27.2114
-    energy_err=data['properties']['total_energy']['error'][0]*27.2114
-
-    one_labels=['n_'+x for x in full_labels]+['4s-3dz2','4s-2pz','3dz2-2pz','3dyz-2py','3dxz-2px']
-    orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
-    orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
-    one_body=sum_onebody(obdm,orb1,orb2)
-    
-    U_labels=['U_'+x for x in full_labels]
-    orb=np.arange(9)
-    U=sum_U(tbdm,orb)
-
-    orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4,0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5]
-    orb2=[1,2,3,4,5,2,3,4,5,3,4,5,4,5,5,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8,6,7,8]
-    J_labels=['J_'+full_labels[orb1[i]]+'_'+full_labels[orb2[i]] for i in range(len(orb1))]
-    J=sum_J(tbdm,orb1,orb2) 
-
[…]

### 2019-05-06 qwalk/ub3lyp_full/subpbs.py

@@ -1,16 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(N,gsw,basestate,basename):
-  fout='gsw'+str(np.round(gsw,2))
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  #for gsw in np.arange(1.0,0.0,-0.1):
-  for gsw in [0.1,0.2]:
-    if(gsw==1.0): N=1
-    else: N=10
-    for basestate in np.arange(16):
-      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_min_s1/analyze.py

@@ -1,163 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-
-def collectdf():
-  df=None
-  for basestate in range(3):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
-      small_df=pd.read_pickle(f)
-  
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-
-      small_df['Sz']=0.5
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0,sort=True)
-
-  for basestate in range(3):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='../ub3lyp_min_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
-      small_df=pd.read_pickle(f)
-      
-      small_df['basestate']=basestate+3
-      if(gsw==1.0): small_df['basestate']=-1
-
-      small_df['Sz']=1.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  return df
-
-def analyze(df):
-  #Formatting
-  df['mo_n_3s']=df['mo_0_0']
-  df['mo_n_3p']=df['mo_1_1']+df['mo_2_2']+df['mo_3_3']
-  df['mo_n_2s']=df['mo_4_4']
-  df['mo_n_3dd']=df['mo_8_8']+df['mo_9_9']
-  df['mo_n_3dpi']=df['mo_5_5']+df['mo_6_6']
-  df['mo_n_3dz2']=df['mo_7_7']
-  df['mo_n_3d']=df['mo_n_3dd']+df['mo_n_3dpi']+df['mo_n_3dz2']
-  df['mo_n_2ppi']=df['mo_10_10']+df['mo_11_11']
[…]

### 2019-05-06 qwalk/ub3lyp_min_s1/analyzedmc.py

@@ -1,206 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-#from diagonalize import diagonalize, new_gs
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-
-def collectdf():
-  df=None
-  for basestate in range(3):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=0.5
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0,sort=True)
-
-  for basestate in range(3):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='../ub3lyp_min_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-    
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=1.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  return df
-
-def analyze(df):
-  #Formatting
-  df['mo_n_3dd']=df['mo_4_4']+df['mo_5_5']
-  df['mo_n_3dpi']=df['mo_1_1']+df['mo_2_2']
-  df['mo_n_3dz2']=df['mo_3_3']
-  df['mo_n_3d']=df['mo_n_3dd']+df['mo_n_3dpi']+df['mo_n_3dz2']
-  df['mo_n_2ppi']=df['mo_6_6']+df['mo_7_7']
-  df['mo_n_2pz']=df['mo_8_8']
-  df['mo_n_2p']=df['mo_n_2ppi']+df['mo_n_2pz']
[…]

### 2019-05-06 qwalk/ub3lyp_min_s1/gather.py

@@ -1,64 +1,0 @@
-import json 
-import pandas as pd
-import numpy as np 
-import sys
-sys.path.append('../../../downfolding/')
-from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
-import os 
-
-full_labels=np.array(["3s","3pz","3py","3px","2pz","3dz2","3dxz","3dyz"])
-def gather_all(N,gsw,basename):
-  ''' 
-  Gathers all your data and stores into 
-  '''
-  df=None
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
-
-    statinfo=os.stat(f)
-    if(statinfo.st_size>0):
-      print(f)
-      data=json.load(open(f,'r'))
-      obdm,__=get_qwalk_dm(data['properties']['tbdm_basis1'])
-      obdm2,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis2'])
-      energy=data['properties']['total_energy']['value'][0]*27.2114
-      energy_err=data['properties']['total_energy']['error'][0]*27.2114
-
-      print(obdm.shape,obdm2.shape,tbdm.shape)
-
-      #MO ordering
-      #1-body
-      orb1=[0,1,2,3,4,5,6,7,8,9,10,11,12,13,5, 6 ,7 ,7 ,12]
-      orb2=[0,1,2,3,4,5,6,7,8,9,10,11,12,13,10,11,12,13,13]
-      mo=sum_onebody(obdm,orb1,orb2)
-      mo_labels=['mo_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
-
-      #2-body
-      orb1=[0,1,2,3,4,5]
-      u=sum_U(tbdm,orb1)
-      u_labels=['u'+str(orb1[i]) for i in range(len(orb1))]
-
-      orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4]
-      orb2=[1,2,3,4,5,2,3,4,5,3,4,5,4,5,5]
-      j=sum_J(tbdm,orb1,orb2)
-      j_labels=['j_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
-
-      dat=np.array([energy,energy_err]+list(mo)+list(u)+list(j))
[…]

### 2019-05-06 qwalk/ub3lyp_min_s1/subpbsdmc.py

@@ -1,15 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(N,gsw,basestate,basename):
-  fout='gsw'+str(np.round(gsw,2))
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.dmc.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  for basestate in np.arange(1,3):
-    for gsw in np.arange(0.2,1.2,0.2):
-      if(gsw==1.0): N=1
-      else: N=5
-      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_min_s3/subpbs.py

@@ -1,15 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(N,gsw,basestate,basename):
-  fout='gsw'+str(np.round(gsw,2))
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  for basestate in np.arange(3):
-    for gsw in np.arange(0.2,1.2,0.2):
-      if(gsw==1.0): N=1
-      else: N=5
-      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo2/analyze.py

@@ -1,110 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn.linear_model import OrthogonalMatchingPursuit, OrthogonalMatchingPursuitCV 
-from sklearn.model_selection import cross_val_score
-from pyscf import lib,gto,scf,mcscf,fci,lo,ci,cc
-from pyscf.scf import ROHF,UHF,ROKS
-from functools import reduce 
-
-def collectdf():
-  df=None
-  for basestate in range(8):
-    for gsw in np.arange(0.1,1.01,0.1):
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
-      small_df=pd.read_pickle(f)
-      
-      small_df['basestate']=basestate
-      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0)
-  return df
-
-def analyze(df):
-  df['gsw']=np.round(df['gsw'],2)
-  
-  df['n_3dd']=df['t_8_8']+df['t_9_9']
-  df['n_3dpi']=df['t_5_5']+df['t_6_6']
-  df['n_3dz2']=df['t_7_7']
-  df['n_3d']=df['n_3dd']+df['n_3dpi']+df['n_3dz2']
-  df['n_2ppi']=df['t_10_10']+df['t_11_11']
-  df['n_2pz']=df['t_12_12']
-  df['n_2p']=df['n_2ppi']+df['n_2pz']
-  df['n_4s']=df['t_13_13']
-  df['t_pi']=2*(df['t_5_10']+df['t_6_11'])
-  df['t_dz']=2*df['t_7_12']
-  df['t_ds']=2*df['t_7_13']
-  df['t_sz']=2*df['t_12_13']
-
-  #PAIRPLOTS --------------------------------------------------------------------------
-  #sns.pairplot(df,vars=['energy','n_3dd','n_3dpi','n_3dz2','n_3d'],hue='basestate',markers=['o']+['.']*8)
[…]

### 2019-05-06 qwalk/ub3lyp_mo2/diagonalize.py

@@ -1,35 +1,0 @@
-import numpy as np 
-import matplotlib.pyplot as plt
-
-parms_list=[
-(0,-3.2999,-0.9092,-1.8537,0.8163,0,0,0),          #Tpi only,R2=0.979,C=700
-(0,-3.2836,-0.9591,-1.8779,0.8014,0,0.1260,0),     #Tpi,Tsz, R2=0.979,C=800
-(0,-3.3011,-0.9135,-1.8600,0.8125,-0.0096,0,0),    #Tpi,Tdz,R2=0.979,C=800
-(0,-3.2487,-1.6910,-2.575,0.3782,-0.7785,1.1160,0), #Tpi,Tdz,Ts,R2=0.981,C=1540
-
-(0,-2.4505,-1.4719,-1.6933,0,0,0,2.0757),          #Tpi only,R2=0.980,C=700
-(0,-2.7723,-1.2603,-1.7578,0.3189,0,0,1.3095),     #Tpi only,R2=0.981,C=1610
-(0,-2.5176,-1.4976,-1.7923,0,-0.1347,0,1.9594),    #Tpi only,R2=0.981,C=947
-(0,-2.4457,-1.4105,-1.6489,0,-0.2115,0,2.1666),    #Tpi only,R2=0.981,C=730
-]
-
-i=0
-for parms in parms_list:
-  e4s,e3d,epi,ez,tpi,tdz,tsz,tds=parms
-  #dz2, dd, dpi
-  H=np.diag([e3d,e3d,e3d,e3d,e3d,ez,epi,epi,e4s])
-  H[[3,4,6,7],[6,7,3,4]]=tpi
-  H[[0,5],[5,0]]=tdz
-  H[[5,8],[8,5]]=tsz
-  H[[0,8],[8,0]]=tds
-
-  w,__=np.linalg.eigh(H)
-  print(w-w[0])
-
-  plt.plot(np.ones(len(w))*i,w-w[0],'o')
-  i+=1
-plt.show()
-
-#Anything else added would increase the correlation too much and not affect anything else
-#Next step: is there any difference between these different model parameterizations in terms of 1-body properties or energies?
-

### 2019-05-06 qwalk/ub3lyp_mo2/geninputdmc.py

@@ -1,91 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    print('Directory '+str(basename)+' doesnt exists, not going to write DMC')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  gendmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  for j in range(1,N+1):
-    fname=fout+'_'+str(j)
-   
-    #Blue waters input  
-    string='#!/bin/bash\n'+\
-    '#PBS -q secondary\n'+\
-    '#PBS -l nodes=1,flags=allprocs\n'+\
-    '#PBS -l walltime=04:00:00\n'+\
-    '#PBS -N '+fname+str(j)+'\n'\
-    '#PBS -e '+fname+str(j)+'.perr\n'+\
-    '#PBS -o '+fname+str(j)+'.pout\n'+\
-    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
-    'module load intel/18.0\n'+\
-    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
-    'mpiexec ../../../../mainline/bin/qwalk '+fname+'.dmc &> '+fname+'.dmc.out\n'
-    
-    f=open(basename+'/'+fname+'.dmc.pbs','w')
-    f.write(string)
-    f.close()      
-  return 1
-
-def gendmc(N,basename,fout):
-  for j in range(1,N+1):
-    sysstring='s12.sys'
-    fname=fout+'_'+str(j)
-    
-    string='method {\n'+\
-    '  dmc\n'+\
-    '  nblock 25\n'+\
-    '  timestep 0.01 \n'+\
-    '  tmoves \n'+\
-    '  average { tbdm_basis\n'+\
-    '    mode obdm\n'+\
-    '    orbitals {\n'+\
[…]

### 2019-05-06 qwalk/ub3lyp_mo2/makejson.py

@@ -1,16 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.vmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(8):
-    for gsw in np.arange(0.1,1.1,0.1):
-      if(gsw==1.0): N=1
-      else: N=10
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo2/makejsondmc.py

@@ -1,17 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.dmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(7,8):
-    for gsw in np.arange(0.1,1.1,0.1):
-    #for gsw in [1.0]:
-      if(gsw==1.0): N=1
-      else: N=10
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo3/makejson.py

@@ -1,16 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.vmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(8,10):
-    for gsw in np.arange(0.1,1.1,0.1):
-      if(gsw==1.0): N=1
-      else: N=10
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo3/makejsondmc.py

@@ -1,17 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.dmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(10):
-    for gsw in np.arange(0.1,1.1,0.1):
-    #for gsw in [1.0]:
-      if(gsw==1.0): N=1
-      else: N=10
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo3/subpbsdmc.py

@@ -1,15 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(N,gsw,basestate,basename):
-  fout='gsw'+str(np.round(gsw,2))
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.dmc.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  for basestate in np.arange(10):
-    for gsw in np.arange(1.0,0.0,-0.1):
-      if(gsw==1.0): N=1
-      else: N=10
-      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_mo_hispin/analyze.py

@@ -1,163 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-from diagonalize import diagonalize, new_gs
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-
-def collectdf():
-  df=None
-  for basestate in range(10):
-    for gsw in np.arange(0.1,1.1,0.1):
-      f='../ub3lyp_mo3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
-      small_df=pd.read_pickle(f)
-
-      small_df['Sz']=0.5
-      small_df['basestate']=basestate
-      small_df=small_df.drop(columns=['U4s'])
-      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0)
-
-  for basestate in range(6):
-    for gsw in np.arange(0.1,1.1,0.1):
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/gosling.pickle' 
-      small_df=pd.read_pickle(f)
-     
-      small_df['Sz']=1.5
-      small_df['basestate']=basestate+10
-      if(np.around(gsw,2)==1.0): small_df['basestate']=-1
-      df = pd.concat((df,small_df),axis=0)
-  return df
-
-def analyze(df):
-  #Formatting
-  df['gsw']=np.round(df['gsw'],2)
-  
-  df['n_3s']=df['t_0_0']
-  df['n_3p']=df['t_1_1']+df['t_2_2']+df['t_3_3']
-  df['n_2s']=df['t_4_4']
-  df['n_3dd']=df['t_8_8']+df['t_9_9']
-  df['n_3dpi']=df['t_5_5']+df['t_6_6']
-  df['n_3dz2']=df['t_7_7']
-  df['n_3d']=df['n_3dd']+df['n_3dpi']+df['n_3dz2']
[…]

### 2019-05-06 qwalk/ub3lyp_s1/analyzedmc.py

@@ -1,258 +1,0 @@
-import os 
-import numpy as np 
-import pandas as pd
-import seaborn as sns 
-import matplotlib.pyplot as plt
-import statsmodels.api as sm
-from sklearn import linear_model
-from sklearn.model_selection import cross_val_score
-from sklearn.metrics import mean_squared_error, r2_score
-#from diagonalize import diagonalize, new_gs
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.model_selection import KFold
-from scipy import stats
-
-######################################################################################
-#FROZEN METHODS
-
-#Collect df
-def collect_df():
-  df=None
-  for basestate in range(10):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=0.5
-      if(df is None): df = small_df
-      else: df = pd.concat((df,small_df),axis=0,sort=True)
-
-  for basestate in range(6):
-    for gsw in [0.2,0.4,0.6,0.8,1.0]:
-      f='../ub3lyp_s3/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-    
-      small_df['basestate']=basestate
-      if(gsw==1.0): small_df['basestate']=-1
-      small_df['Sz']=1.5
-      df = pd.concat((df,small_df),axis=0,sort=True)
-  
-  for basestate in range(1,2):
-    for gsw in [1.0]:
-      f='../ub3lyp_do/gsw'+str(np.round(gsw,2))+'b'+str(basestate)+'/dmc_gosling.pickle' 
-      small_df=pd.read_pickle(f)
-    
-      small_df['basestate']=basestate
[…]

### 2019-05-06 qwalk/ub3lyp_s1_/simple_analyze.py

@@ -1,169 +1,0 @@
-import pandas as pd
-import numpy as np 
-import matplotlib.pyplot as plt 
-from sklearn.feature_selection import RFE, RFECV
-import statsmodels.api as sm 
-from sklearn.linear_model import LinearRegression, base
-from sklearn.model_selection import cross_val_score
-from ed import h1_moToIAO
-import seaborn as sns 
-from sklearn.model_selection import KFold
-from sklearn.decomposition import PCA
-from ed import ED
-
-def calc_density(df,dE):
-  density=np.zeros(df.shape[0])
-  dE = 0.1 #eV
-  for p in range(df.shape[0]):
-    density[p] = np.sum((df['energy']<(df['energy'].iloc[p] + dE))&(df['energy']>(df['energy'].iloc[p] - dE)))
-  df['density']=density
-
-  return df
-
-def diagonalize(params):
-  norb=9
-  nelec=(8,7)
-  nroots=25
-  res1=ED(params,nroots,norb,nelec)
-
-  nelec=(9,6)
-  nroots=15
-  res3=ED(params,nroots,norb,nelec)
-
-  E = res1[0]
-  Sz = np.ones(len(E))*0.5
-  dm = res1[2] + res1[3]
-  n_3d = dm[:,0,0]+dm[:,1,1]+dm[:,2,2]+dm[:,3,3]+dm[:,6,6]
-  n_2ppi = dm[:,4,4]+dm[:,5,5]
-  n_2pz = dm[:,7,7]
-  n_4s = dm[:,8,8]
-  t_pi = 2*(dm[:,3,4]+dm[:,2,5])
-  t_ds = 2*dm[:,6,8]
-  t_dz = 2*dm[:,6,7]
-  t_sz = 2*dm[:,7,8]
-  d = pd.DataFrame({'energy':E,'Sz':Sz,'iao_n_3d':n_3d,'iao_n_2pz':n_2pz,'iao_n_2ppi':n_2ppi,'iao_n_4s':n_4s,
-  'iao_t_pi':t_pi,'iao_t_ds':t_ds,'iao_t_dz':t_dz,'iao_t_sz':t_sz,'iao_Us':res1[4],'iao_Jsd':res1[5]})
-
-  E = res3[0]
-  Sz = np.ones(len(E))*1.5
-  dm = res3[2] + res3[3]
-  n_3d = dm[:,0,0]+dm[:,1,1]+dm[:,2,2]+dm[:,3,3]+dm[:,6,6]
[…]

### 2019-05-06 qwalk/ub3lyp_s1_/testing_fit.py

@@ -1,47 +1,0 @@
-import numpy as np 
-import matplotlib.pyplot as plt
-from scipy.optimize import minimize
-import pandas as pd 
-import statsmodels.api as sm
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-
-def pred(b,x):
-  return b[0] + b[1]*x
-
-def r(u,tau):
-  return np.abs(tau - (u<0).astype(int))*u**2
-
-def cost(b,x,y,s,w=None):
-  if(w is None): w=np.ones(len(y))
-  yhat = pred(b,x)
-  res = y - yhat
-  z=(y-min(y))/s
-
-  #tau=1/2 for z<1, energy under the scale we set
-  c=np.sum(w[z<1]*r(res[z<1],0.5))
-  #tau=1 for z>1, energy above the scale we set 
-  c+=np.sum(w[z>=1]*r(res[z>=1],1.0))
-  return c
-
-x=np.arange(100)
-y=2*x + np.random.normal(size=x.shape[0])
-y[20:]+=np.random.normal(size=80)*y[20:]/10
-b0=[0,2]
-s=40
-w=np.exp(-(1./s)*(y-min(y)))
-
-res_exp = minimize(lambda b: cost(b,x,y,s,w), b0).x
-#res_ols = minimize(lambda b: cost(b,x,y,1e200,w), b0).x
-
-X=pd.DataFrame({'X':x})
-X=sm.add_constant(X)
-ols=sm.WLS(y,X,weights=w).fit()
-__, l, u = wls_prediction_std(ols,alpha=0.10)
-pred_err=(u-l)/2
-
-plt.plot(x,y,'ob',label='DATA')
-plt.errorbar(x,res_exp[0]+res_exp[1]*x,xerr=pred_err,fmt='-g',label='EXP')
-plt.errorbar(x,ols.predict(),xerr=pred_err,fmt='-k',label='OLS')
-plt.legend(loc='best')
-plt.show()
-#plt.savefig('testing_fit.pdf')

### 2019-05-06 qwalk/ub3lyp_s1_/uks_dn_model.py

@@ -1,125 +1,0 @@
-#Exact diagonalization routine in pyscf
-import numpy as np
-import scipy.linalg
-from pyscf import gto, scf, ao2mo, cc, fci, mcscf, lib
-from pyscf.scf import ROKS, UKS
-from functools import reduce
-import matplotlib.pyplot as plt 
-import pandas as pd
-import seaborn as sns 
-
-#Get 1-body parameters in IAO representation
-def h1_moToIAO(printvals=False):
-  #LOAD IN IAOS
-  act_iao=[5,9,6,8,11,12,7,13,1]
-  iao=np.load('../../pyscf/ub3lyp_full/b3lyp_iao_b.pickle')
-  iao=iao[:,act_iao]
-  
-  #LOAD IN MOS
-  act_mo=[5,6,7,8,9,10,11,12,13]
-  chkfile='../../pyscf/ub3lyp_full/Cuvtz_r1.725_s1_UB3LYP_0.chk'
-  mol=lib.chkfile.load_mol(chkfile)
-  m=UKS(mol)
-  m.__dict__.update(lib.chkfile.load(chkfile, 'scf'))
- 
-  print(m.mo_energy[0][act_mo]*27.2114)
-  print(m.mo_energy[1][act_mo]*27.2114)
-
-  for spin in [1]:
-    mo=m.mo_coeff[spin][:,act_mo]
-    s=m.get_ovlp()
-
-    #IAO ordering: ['del','del','yz','xz','x','y','z2','z','s'] 
-    #MO ordering:  dxz, dyz, dz2, delta, delta, px, py, pz, 4s
-    e=np.diag(m.mo_energy[spin][act_mo])*27.2114
-
-    mo_to_iao = reduce(np.dot,(mo.T,s,iao))
-    e = reduce(np.dot,(mo_to_iao.T,e,mo_to_iao))
-    e[np.abs(e)<1e-10]=0
-    e=(e+e.T)/2
-
-  return e
-
-def h2_IAO(Jcu,Us):
-  #Jsi = 0.25*(ns_u - ns_d)*(ni_u - ni_d) + 
-  #0.5*(cs_u^+ cs_d ci_d^+ ci_u + cs_d^+ cs_u ci_u^+ ci_d)
-
-  #PYSCF ordering: 2rdm[p,r,q,s]_x,x' = <cp_x^+ cq_x'^+ cs_x' cr_x>
[…]

### 2019-05-06 qwalk/ub3lyp_s3/geninput.py

@@ -1,160 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  genslater(N,gsw,basestate,basename,fout)
-  #genvmc(N,basename,fout)
-  #genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  #BW input
-  for i in range(1,N+1):
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q low\n'+\
-    '#PBS -l nodes=1:ppn=32:xe\n'+\
-    '#PBS -l walltime=01:00:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'mkdir -p /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
-    'cd /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
-    'cp -u /u/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/* .\n'+\
-    'aprun -n 32 /u/sciteam/$USER/fork/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'   
-
-    f=open(basename+'/'+fname+'.pbs','w')
-    f.write(string)
-    f.close()
-  return 1
-
-def genvmc(N,basename,fout):
-  for j in range(1,N+1):
-    sysstring='s32.sys'
[…]

### 2019-05-06 qwalk/ub3lyp_s3/geninputdmc.py

@@ -1,100 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    print('Directory '+str(basename)+' doesnt exists, not going to write DMC')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  gendmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  #BW input
-  for i in range(1,N+1):
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q low\n'+\
-    '#PBS -l nodes=8:ppn=32:xe\n'+\
-    '#PBS -l walltime=04:00:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'mkdir -p /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
-    'cd /scratch/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/\n'+\
-    'cp -u /u/sciteam/$USER/cuo/qwalk/ub3lyp_s3/'+basename+'/* .\n'+\
-    'aprun -n 256 /u/sciteam/$USER/fork/bin/qwalk '+fname+'.dmc &> '+fname+'.dmc.out\n'     
-    f=open(basename+'/'+fname+'.dmc.pbs','w')
-    f.write(string)
-    f.close()
-  else: pass
-  return 1
-
-def gendmc(N,basename,fout):
-  for j in range(1,N+1):
-    sysstring='s32.sys'
-    fname=fout+'_'+str(j)
-    
-    string='method {\n'+\
-    '  dmc\n'+\
-    '  nblock 25\n'+\
-    '  timestep 0.01\n'+\
[…]

### 2019-05-06 qwalk/ub3lyp_so_1do/diagonalize.py

@@ -1,161 +1,0 @@
-import numpy as np 
-import matplotlib.pyplot as plt
-from pyscf import lib
-from pyscf.scf import ROKS
-from functools import reduce 
-
-'''
-const      -5776.3165      0.297  -1.94e+04      0.000   -5776.900   -5775.733
-n_3d          -2.5089      0.025   -102.135      0.000      -2.557      -2.461
-n_2ppi        -0.4060      0.024    -17.199      0.000      -0.452      -0.360
-n_2pz         -1.9120      0.027    -71.364      0.000      -1.965      -1.859
-t_pi           1.0849      0.026     41.361      0.000       1.033       1.136
-sigU           4.2194      0.054     78.338      0.000       4.114       4.325
-
-
-n_3d          -2.5356      0.025    -99.798      0.000      -2.585      -2.486
-n_2ppi        -0.8657      0.049    -17.561      0.000      -0.962      -0.769
-n_2pz         -2.0601      0.031    -67.187      0.000      -2.120      -2.000
-t_pi           0.8990      0.038     23.659      0.000       0.824       0.973
-t_sz           0.8957      0.079     11.337      0.000       0.741       1.051
-t_dz          -0.3208      0.047     -6.883      0.000      -0.412      -0.229
-sigU           3.4658      0.085     41.013      0.000       3.300       3.632
-'''
-
-def diagonalize_3d10(parms,printvals=False):
-  #LOAD IN IAOS
-  act_iao=[5,9,6,8,11,12,7,13,1]
-  iao=np.load('../../pyscf/ub3lyp_full/b3lyp_iao_b.pickle')
-  iao=iao[:,act_iao]
-  #iao[:,7]*=-1 #CORRECT SIGN ON PZ
-
-  #LOAD IN MOS
-  act_mo=[5,6,7,8,9,10,11,12,13]
-  chkfile='../../pyscf/chk/Cuvtz_r1.725_s1_B3LYP_1.chk'
-  mol=lib.chkfile.load_mol(chkfile)
-  m=ROKS(mol)
[…]

### 2019-05-06 qwalk/ub3lyp_so_s1/geninput.py

@@ -1,180 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  genslater(N,gsw,basestate,basename,fout)
-  genvmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  if(N==1):
-    #CC input
-    i=1
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q secondary\n'+\
-    '#PBS -l nodes=1,flags=allprocs\n'+\
-    '#PBS -l walltime=00:30:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
-    'module load intel/18.0\n'+\
-    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
-    'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'   
-    f=open(basename+'/'+fname+'.pbs','w')
-    f.write(string)
-    f.close()
-  elif(N!=10): print("Cannot run"); exit(0)
-  for i in range(2):
-    #CC input
-    fname=fout+'_'+str(i+1)
-    string='#!/bin/bash\n'+\
-    '#PBS -q secondary\n'+\
-    '#PBS -l nodes=1,flags=allprocs\n'+\
[…]

### 2019-05-06 qwalk/ub3lyp_so_s1/subpbs.py

@@ -1,16 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(N,gsw,basestate,basename):
-  fout='gsw'+str(np.round(gsw,2))
-  if(N==10): N=2
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  for basestate in np.arange(10):
-    for gsw in np.arange(1.0,0.0,-0.1):
-      if(gsw==1.0): N=1
-      else: N=10
-      subpbs(N,gsw,basestate,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/ub3lyp_so_s3/geninput.py

@@ -1,180 +1,0 @@
-#Generate input files for 2rdm, use same slater files as old 1rdm!
-import os 
-import shutil 
-import numpy as np 
-
-def geninput(N,gsw,basestate,basename):
-  '''
-  input:
-  detgen - type of excitations to sample
-  N - number of states to sample
-  Ndet - number of determinants per state
-  gsw - ground state weight 
-  basename - all written files to basename/__generated file names__
-  output:
-  slater files
-  vmc files 
-  pbs files for vmc
-  '''
- 
-  #Make sure directory exists, else make it 
-  if not os.path.exists(basename):
-    #Move all important files to there 
-    shutil.copytree('req_files',basename+'/') 
-  else:
-    print('Directory '+str(basename)+' exists, not going to overwrite')
-    exit(0)  
-  fout='gsw'+str(np.round(gsw,2))
-  genslater(N,gsw,basestate,basename,fout)
-  genvmc(N,basename,fout)
-  genpbs(N,basename,fout)
-  return 
-
-def genpbs(N,basename,fout):
-  if(N==1):
-    #CC input
-    i=1
-    fname=fout+'_'+str(i)
-    string='#!/bin/bash\n'+\
-    '#PBS -q secondary\n'+\
-    '#PBS -l nodes=1,flags=allprocs\n'+\
-    '#PBS -l walltime=00:30:00\n'+\
-    '#PBS -N '+fname+'\n'\
-    '#PBS -e '+fname+'.perr\n'+\
-    '#PBS -o '+fname+'.pout\n'+\
-    'module load openmpi/3.1.1-gcc-7.2.0\n'+\
-    'module load intel/18.0\n'+\
-    'cd ${PBS_O_WORKDIR}/'+basename+'/ \n'+\
-    'mpiexec ../../../../mainline/bin/qwalk '+fname+'.vmc &> '+fname+'.vmc.out\n'   
-    f=open(basename+'/'+fname+'.pbs','w')
-    f.write(string)
-    f.close()
-  elif(N!=10): print("Cannot run"); exit(0)
-  for i in range(2):
-    #CC input
-    fname=fout+'_'+str(i+1)
-    string='#!/bin/bash\n'+\
-    '#PBS -q secondary\n'+\
-    '#PBS -l nodes=1,flags=allprocs\n'+\
[…]

### 2019-05-06 qwalk/ub3lyp_so_s3/makejson.py

@@ -1,26 +1,0 @@
-import os 
-import numpy as np 
-
-def makejson(N,gsw,basename):
-  for j in range(1,N+1):
-    f=basename+'/gsw'+str(np.around(gsw,2))+'_'+str(j)+'.vmc'
-    print(f)
-    os.system('../../../mainline/bin/gosling '+f+'.log -json &> '+f+'.gosling.json')
-  
-    #Replace labels in JSON 
-    json_f=open(f+'.gosling.json','r').read().split("\n")
-    i=1 
-    for j in range(len(json_f)):
-      if('tbdm_basis' in json_f[j]): 
-        json_f[j]='"tbdm_basis'+str(i)+'":{'
-        i+=1
-    json_o=open(f+'.gosling.json','w')
-    json_o.write('\n'.join(json_f))
-  return 1
-
-if __name__=='__main__':
-  for basestate in np.arange(6):
-    for gsw in np.arange(0.1,1.1,0.1):
-      if(gsw==1.0): N=1
-      else: N=10
-      makejson(N,gsw,basename='gsw'+str(np.around(gsw,2))+'b'+str(basestate))

### 2019-05-06 qwalk/vmc/attic/analyze.py

@@ -1,64 +1,0 @@
-import seaborn as sns
-import matplotlib.pyplot as plt
-import statsmodels.api as sm 
-import pandas as pd
-import numpy as np 
-sns.set(style="ticks")
-
-'''
-labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
-fname='run1s/s_Ndet10_gsw0.7_gosling.pickle'
-df=pd.read_pickle(fname)
-olabels=np.where('obdm' in list(df))[0]
-print(olabels)
-exit(0)
-Ulabels=['tbdm_updown_%s_%s_%s_%s'%(s,s,s,s) for s in labels]
-X=df[['energy']+Ulabels]
-X['tbdm_updown_3dd_3dd_3dd_3dd']=X['tbdm_updown_3dxy_3dxy_3dxy_3dxy']+X['tbdm_updown_3dx2y2_3dx2y2_3dx2y2_3dx2y2']
-X['tbdm_updown_3dpi_3dpi_3dpi_3dpi']=X['tbdm_updown_3dxz_3dxz_3dxz_3dxz']+X['tbdm_updown_3dyz_3dyz_3dyz_3dyz']
-X['tbdm_updown_2ppi_2ppi_2ppi_2ppi']=X['tbdm_updown_2px_2px_2px_2px']+X['tbdm_updown_2py_2py_2py_2py']
-X['tbdm_updown_d_d_d_d']=-1*(X['tbdm_updown_3dd_3dd_3dd_3dd']+X['tbdm_updown_3dpi_3dpi_3dpi_3dpi']+X['tbdm_updown_3dz2_3dz2_3dz2_3dz2'])
-X=X.drop(columns=['tbdm_updown_3dxy_3dxy_3dxy_3dxy','tbdm_updown_3dx2y2_3dx2y2_3dx2y2_3dx2y2',
-'tbdm_updown_3dxz_3dxz_3dxz_3dxz','tbdm_updown_3dyz_3dyz_3dyz_3dyz',
-'tbdm_updown_2px_2px_2px_2px','tbdm_updown_2py_2py_2py_2py'])
-#sns.pairplot(X)
-#plt.show()
-
-X['obdm_4s_4s']=df['obdm_up_4s_4s']+df['obdm_down_4s_4s']
-X['obdm_2pz_2pz']=df['obdm_up_2pz_2pz']+df['obdm_down_2pz_2pz']
[…]

### 2019-05-06 qwalk/vmc/attic/run1s_1body/reducedf.py

@@ -1,59 +1,0 @@
-import pandas as pd 
-import numpy as np 
-
-fname='s_Ndet10_gsw0.7_df.pickle'
-df=pd.read_pickle(fname)
-
-#Correct labels
-labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
-iaos=  np.array([ 2,   6,     7,     8,     9,     10,      12,   13,   14])
-fix_cols=[]
-for col in list(df):
-  l=col.split("_")
-  if(len(l)>=4):
-    a=int(col.split("_")[2])
-    b=int(col.split("_")[3])
-    i=np.where(iaos==a)[0][0]
-    j=np.where(iaos==b)[0][0]
-    fix_col=col.split("_")
-    fix_col[2]=labels[i]
-    fix_col[3]=labels[j]
-    fix_col='_'.join(fix_col)
-  else: fix_col=col
-  fix_cols.append(fix_col)
-df.columns=fix_cols
-
-#Energy units
-df['energy']*=27.2114 #eV
-df['energy_err']*=27.2114
-
-#Sum over spins
-nu=['obdm_up_'+i+'_'+j for i in labels for j in labels]
-nd=['obdm_down_'+i+'_'+j for i in labels for j in labels]
-ntot=['obdm_'+i+'_'+j for i in labels for j in labels]
-n=df[nu].values+df[nd].values
-df[ntot]=pd.DataFrame(n,index=df.index)
-df=df.drop(columns=nd+nu)
-
-nu=[x+'_err' for x in nu]
-nd=[x+'_err' for x in nd]
-ntot=[x+'_err' for x in ntot]
-n=np.sqrt(df[nu].values**2 + df[nd].values**2)
-df[ntot]=pd.DataFrame(n,index=df.index)
-df=df.drop(columns=nd+nu)
-
-#Reduced DF
-n=['obdm_'+str(i)+'_'+str(i) for i in labels]
-t=['obdm_4s_2pz','obdm_4s_3dz2','obdm_3dyz_2py','obdm_3dz2_2pz','obdm_3dxz_2px']
-rdf=df[['energy']+['energy_err']+n+t]
-rdf['obdm_3dpi_3dpi']=rdf['obdm_3dxz_3dxz']+rdf['obdm_3dyz_3dyz']
[…]

### 2019-05-06 qwalk/vmc/subpbs.py

@@ -1,16 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(detgen,N,Ndet,gsw,basename):
-  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
-  for state in ['2X','2Y','4SigmaM','4Phi','4Delta','2Delta','4SigmaP']:
-    for j in range(1,N+1):
-      fname=basename+'/'+state+fout+'_'+str(j)+'.pbs'
-      os.system('qsub '+fname)
-
-if __name__=='__main__':
-  detgen='a'
-  N=25
-  Ndet=10
-  gsw=0.8
-  subpbs(detgen,N,Ndet,gsw,basename='run1a/')

### 2019-05-06 qwalk/vmc_eq/span_sampling/gather.py

@@ -1,97 +1,0 @@
-import json 
-import pandas as pd
-import numpy as np 
-import sys
-sys.path.append('../../../../downfolding/')
-from shivesh_downfold_tools import get_qwalk_dm, sum_onebody, sum_J, sum_U, sum_V
-
-full_labels=np.array(["4s","3dxy","3dyz","3dz2","3dxz","3dx2y2","2px","2py","2pz"])
-def gather_all(spin,N,gsw,basename):
-  ''' 
-  Gathers all your data and stores into 
-  '''
-  df=None
-  for j in range(1,N+1):
-    #if(j==0): f='base/'+name+'.vmc_tbdm.gosling.json'  #GS
-    #else: f=basename+'/'+name+'_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(gsw)+'_'+str(j)+'.vmc.gosling.json'
-    f=basename+'/S'+str(spin)+'_gsw'+str(np.round(gsw,2))+'_'+str(j)+'.vmc.gosling.json' 
-    print(f)
-
-    data=json.load(open(f,'r'))
-    obdm,__,tbdm,__=get_qwalk_dm(data['properties']['tbdm_basis'])
-    energy=data['properties']['total_energy']['value'][0]*27.2114
-    energy_err=data['properties']['total_energy']['error'][0]*27.2114
-
-    one_labels=['n_'+x for x in full_labels]+['4s-3dz2','4s-2pz','3dz2-2pz','3dyz-2py','3dxz-2px']
-    orb1=[0,1,2,3,4,5,6,7,8,0,0,3,2,4]
-    orb2=[0,1,2,3,4,5,6,7,8,3,8,8,7,6]
-    one_body=sum_onebody(obdm,orb1,orb2)
-    
-    U_labels=['U_'+x for x in full_labels]
-    orb=np.arange(9)
-    U=sum_U(tbdm,orb)
-
-    orb1=[0,0,0,0,0,1,1,1,1,2,2,2,3,3,4,0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5]
[…]

### 2019-05-06 qwalk/vmc_eq/span_sampling/subpbs.py

@@ -1,14 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(spin,N,gsw,basename):
-  fout='S'+str(spin)+'_gsw'+str(np.round(gsw,2))
-  for j in range(1,N+1):
-    fname=basename+'/'+fout+'_'+str(j)+'.pbs'
-    os.system('qsub '+fname)
-
-if __name__=='__main__':
-  N=20
-  spin=3 #2*Sz
-  for gsw in np.arange(0.1,1.0,0.1):
-    subpbs(spin,N,gsw,basename='spin'+str(spin)+'gsw'+str(np.around(gsw,2)))

### 2019-05-06 qwalk/vmc_eq/subpbs.py

@@ -1,17 +1,0 @@
-import os 
-import numpy as np 
-
-def subpbs(detgen,N,Ndet,gsw,basename):
-  fout='_'+detgen+'_Ndet'+str(Ndet)+'_gsw'+str(np.round(gsw,2))
-  #for state in ['gs0','gs1','gs2','gs3','gs4','gs5','gs2_lo','gs3_lo','gs5_lo']:
-  for state in ['gs2_lo','gs3_lo','gs5_lo']:
-    for j in range(1,N+1):
-      fname=basename+'/'+state+fout+'_'+str(j)+'.pbs'
-      os.system('qsub '+fname)
-
-if __name__=='__main__':
-  detgen='a'
-  N=100
-  Ndet=10
-  gsw=0.7
-  subpbs(detgen,N,Ndet,gsw,basename='run2a/')

### 2019-05-06 paper/analysis.tex

@@
 \section{Model selection}
-Model selection required both an understanding of the CuO molecule's low energy excitations and some statistical analysis.
+Model selection requires both an understanding of the CuO molecule's low energy excitations and some statistical analysis.
 We know that the lowest energy excitations of CuO are between the O p and Cu 4s orbitals, as these are the only excitations which allow for a 3d10 configuration.
-Further, given that we will be including 3d9 states, it's clear that we will need at least consider the following non-interacting parameters:
+Further, given that we will be including 3d9 states, it's clear that we will need to at least consider the following non-interacting parameters:
 $$\bar{\epsilon}_d, \bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$$
@@
 
-Since we know that $\bar{\epsilon}_d + \bar{\epsilon}_z + \bar{\epsilon}_\pi + \bar{\epsilon}_s = $ Const, we can eliminate $\bar{\epsilon}_d$ from our model since it is linearly dependent on the rest of the parameters.
+Since we know that $\bar{n}_d + \bar{n}_z + \bar{n}_\pi + \bar{n}_s = $ Const, we can eliminate $\bar{\epsilon}_d$ from our model since it is linearly dependent on the rest of the parameters.
 The left over occupation energies are certainly required in our model, given the knowledge we have of our low energy space.
 Since we know that $U_{4s}$ is required to describe the $4s^2$ states and that the $J_{sd}$ will probably play an important role as well, we just need to do model selection on the four hopping parameters.
-Below are 5-fold CV linear regressions using \textit{every} model which includes the $\bar{\epsilon}, J_{sd}, U_{4s}$ parameters above and one element in the power set of $\bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$.
-
-\begin{figure}
-\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/cv_valid.pdf}
-\caption{5-fold CV regressions for model selection}
-\end{figure}
+Figure 2 shows 5-fold cross-validated (CV) linear regressions using \textit{every} model which includes the $\bar{\epsilon}, J_{sd}, U_{4s}$ parameters above and one element in the power set of $\{\bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}\}$.
 
 The models are increasing in complexity from left-to-right, and it's clear that the fourth model listed here is as accurate as the most complex model, and significantly simpler.
-Therefore, we selected that model as it captures the most variation with the fewest parameters.
+Therefore, we select that model as it captures the most variation with the fewest parameters.
 The selected model then looks like this:
@@
 \section{Model fitting}
-We conducted a weighted least squares on our samples in order to fit the six parameters in our selected model.
-The higher density of states with $3d9$ occupation made it so that an unweighted linear regression would fit in a biased way towards the $3d9$ states, leaving the $3d10$ states fit very poorly.
+We conducted a weighted least squares regression on our samples in order to fit the six parameters in our selected model.
+The higher density of states with 3d9 occupation made it so that an unweighted linear regression would bias towards a more accurate description of the 3d9 states, leaving the 3d10 states fit very poorly.
+Since we are particularly interested in describing the lowest energy eigenstates accurately, which are 3d10 in character, we need to weight our linear regression so that the 3d10 sector is fit more accurately than in the unweighted case.
 The weighting function we used was $e^{-\beta E_{DMC}}$, where $\beta$ is a variable "temperature" which was varied from 0.25 to 3.75 in increments of 0.25.
-We find that in the range of $\beta \in {1.5, 2.5}$ the model does not change very much, therefore we select a model at $\beta = 2.0$, which leads to the following set of regressed parameters:
+We find that in the range of $\beta \in \{1.5, 2.5\}$ the model does not change very much, therefore we select a model at $\beta = 2.0$, which leads to the following set of regressed parameters:
 \begin{multline}
@@
 \boxed{t_\pi = -0.22 eV, t_{d_z^2 s} = 0.38 eV, t_{s z} = 0.80 eV, t_{d_z^2 z} = 0.70 eV}\\
-\boxed{ , J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
+\boxed{  J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
 \end{multline}
 
+Shown in Figure 3 are predictions using $\beta = 2.0$ with 95\% confidence intervals on the full set of samples and only on the base states.
+In both cases the model was fit using the full set of samples.
+Figure 4 shows for $\beta=2.0$ the sample weights versus the trace ($\bar{n}_{3d} + \bar{n}_{p_z} + \bar{n}_{p_\pi} + \bar{n}_{4s}$) of the 1-rdm in our chosen MO basis for the different samples.
+As mentioned in section 3, the weights of samples which have a trace that vary significantly from the ground state trace of 14.80 are small, indicating that our regression is fitting primarily to states for which the MO basis is functioning properly.
+
 \section{Comparison to DFT model}
-We can then do an exact diagonalization on this model Hamiltonian, which was accomplished using an FCI solver for a custom Hamiltonian in PySCF [ref].
-Show in the figures below are the lowest lying eigenstates of this model Hamiltonian for the full range of $\beta$, showing the energies and occupations of different orbitals.
-We can see that as we let $2.5 > \beta > 1.25 $ the model is fairly stable.
-The ground state of our model matches that of experiment, namely it has an electron configuration of $Cu 3d^{10} O 2p_z^{1.75} O 2p_\pi^3 Cu 4s^{0.4}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{2} O 2p_\pi^3 Cu 4s^{0}.$ This is also an $S_z=1/2$ state as expected in experiment.
-The first excited state in this range of $\beta$s is another $S_z=1/2$ state with occupations $Cu 3d^{9.7} O 2p_z^{1.2} O 2p_\pi^4 Cu 4s^{0.3}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{1} O 2p_\pi^4 Cu 4s^{0}.$ This state is at an energy of 1 eV which matches the APES measurements up to a tenth of an eV!
-The first $3d^9$ state is at around 2.2 eV, which again matches the predictions of the APES measurements.
-Aside from these states, there are also various states with $S_z=3/2$ which our model predicts to be low in energy.
-For example, there is an $S_z=3/2$ state with occupation at around 1.4 eV with occupations $Cu 3d^{9.7} O 2p_z^{2.0} O 2p_\pi^2 Cu 4s^{1.0}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{2} O 2p_\pi^2 Cu 4s^{1}.$ As predicted from the anion case, the lowest $S_z=3/2$ state is indeed a $O p_\pi \rightarrow Cu 4s$ excitation.
-There if another state at 2.0 eV which is $S_z =3/2$ and which corresponds to an $O p_z \rightarrow Cu 4s$ state.
-Therefore our model predicts that the measured state in APES is indeed a quartet state, however it should have $\Pi$ symmetry.
-The $\Sigma$ symmetry quartet state, which is indeed the lowest energy $S_z=3/2$ state, resides at an energy very close to the $^2Y$ state and may not have been able to resolve.
-Overall, our model matches every experimentally measured and rigorously confirmed eigenstate of CuO.
-We further argue that the labeling of a state at 2.0 eV as $^4\Sigma$ is faulty and it should be $^4\Pi$.
+We did an exact diagonalization on our Hamiltonian (2) using an FCI solver for a custom Hamiltonian in PySCF [ref].
+Show in Figure 5 below are the lowest lying eigenstates of this model Hamiltonian and their single particle occupations.
+At $\beta=2$ (what we will be focusing on from here onwards) the ground state of our model matches that of experiment, namely it has an electron configuration of $Cu 3d^{10} O 2p_z^{1.75} O 2p_\pi^3 Cu 4s^{0.4}$, which would map to the approximate nominal filling of $Cu 3d^{10} O 2p_z^{2} O 2p_\pi^3 Cu 4s^{0}$, and is an $S_z=1/2$ state.
+The first excited state is an $S_z=1/2$ state at 1eV and which looks like an $O p_z \rightarrow O p_\pi$ excitation on the ground state, matching the results from APES.
+The first $3d^9$ state is also an $S_z=1/2$ state and sits at around 2.2 eV, which again matches the predictions of the APES measurements.
+Our model eigenstates therefore match very closely in the $S_z=1/2$ sector to the experimentally measured eigenstates in both energy and single particle properties.
 
+There are also model eigenstates with $S_z=3/2$ which are low in energy.
+There is a quartet eigenstate at 2.0 eV which looks like an $O p_z \rightarrow Cu 4s$ excitation on the ground state, disagreeing with the experimental claims of a $^4\Sigma$ state at this energy.
+Our model predicts that the $^4\Sigma$ state is actually lower in energy at around 1.2 eV above the ground state, and looks like an $O p_\pi \rightarrow Cu 4s$ excitation on the ground state.
+These results indicate that a potential mislabelling may have occurred in experiment regarding the 2.0 eV quartet eigenstate, based on the faulty assumption that the lowest energy quartet state seen in the APES experiment was in fact the lowest energy quartet state.
+This may be due to the difficulty in measuring excitations to and out-of the $^4\Sigma$ state since it is so close in energy to the $S_z=1/2$ first excited state.
+
+We can compare these results to those found from, for example, an ROKS or UKS calculation of the ground state for CuO.
+Typically one would take the ROKS/UKS eigenvalues to build an approximate non-interacting model of the system.
+Shown in Figure 6 are the ROKS/UKS eigenstates if we do so and exactly diagonalize in the $S_z=1/2,3/2$ sectors.
+The UKS eigenstates here are twice in number to the ROKS, since the UKS gives us two independent models, one for each spin channel.
+Studying just the ROKS model for now, we see that it does predict an eigenstate at 1 eV which resembles the $^2Y$ state, however there are no low energy $S_z=3/2$ states at all.
+All of the $S_z=3/2$ states are $>$ 3eV above the ground state.
+I believe this is due, in part, to the lack of relaxation effects present in the 1-particle model, as the orbitals of excited states of the CuO molecule are augmented relative to the orbitals of the ground state.
+Further, the exclusion of the $J_{sd}$ pushes the $S_z=3/2$ states higher in energy than expected in reality.
+The UKS model also fails to describe the $S_z=3/2$ states accurately for similar reasons.
+
+\pagebreak
+%Figure 2
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/cv_valid.pdf}
+\caption{5-fold CV regressions for model selection}
+\end{figure}
+
+%Figure 3
+\begin{figure}
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit.pdf}
+  \caption{DMC predictions for all samples.}
+  \label{fig:sub6}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_baseonly.pdf}
+  \caption{DMC predictions for basestates. }
+  \label{fig:sub7}
+\end{subfigure}
+\label{fig:test2}
+\caption{DMC regression using all states and $\beta=2.0$.}
+\end{figure}
+
+%Figure 4
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/w_vs_t.pdf}
+\caption{Weights versus trace for linear regression with $\beta=2.0$.}
+\end{figure}
+
+%Figure 5
 \begin{figure}
@@
 
-We can compare these results to those found from, for example, an ROKS or UKS calculation of the ground state for CuO (one of our base states!).
-Typically one would take the ROKS/UKS eigenvalues and claim that these eigenvalues can be used as an approximate non-interacting model of the system.
-If we do so and exactly diagonalize in the $S_z=1/2,3/2$ sectors the ROKS/UKS eigenvalue matrix, we will find the following results for the eigenstates.
-The UKS eigenstates here are twice in number to the ROKS, since the UKS gives us two independent, approximate models, one for each spin channel.
-In table 1 below we also present the model parameters for the $\beta=2$ DMC regression compared to the ROKS model, which we will be focusing on from now on.
-Studying just the ROKS model for now, we see that it does predict an eigenstate at 1 eV which resembles the $^2Y$ state, however there are no low energy $S_z=3/2$ states at all.
-All of the $S_z=3/2$ states are $>$ 3eV above the ground state.
-We believe this should is due to the lack of relaxation effects present in the 1-particle model.
-The excited states of the CuO molecule do not look like simple 1-particle excitations on the ground state, there are relaxations of orbitals within a given symmetry sector.
-Further, the exclusion of the $J_{sd}$ pushes the $S_z=3/2$ states higher in energy.
-Clearly we see a large difference between the DMC and ROKS models, and that the DMC model more accurately reflects experiment.
-
+%Figure 6
 \begin{figure}
@@
 
-\begin{wrapfigure}{r}{0.4\textwidth}
-\begin{tabular}{lll}
- &  DMC (eV) & ROKS (eV) \\
-$\epsilon_{d_\delta}$ &  0.00 & 0.00  \\
-$\epsilon_{d_\pi}$ & -0.10 & -0.36 \\
-$\epsilon_{d_{z^2}}$ & 0.41 & 0.52 \\
-$\epsilon_z$ & 1.20 & 0.66 \\
-$\epsilon_\pi$ & 2.21 & 0.85 \\
-$\epsilon_s$ &  2.44 & 4.24 \\
-$t_\pi$ & -0.22 & -1.14 \\
-$t_{s d_{z^2}}$ & 0.38 & 0.97 \\
-$t_{s z}$ & 0.80 & 1.86\\
-$t_{d_{z^2} z}$ & 0.70 & 1.55\\
-$J_{sd}$ & -0.51 & 0.00 \\ 
-$U_s$ & 3.91 & 0.00 \\
-\end{tabular}
-\caption{Parameter differences between DFT/DMC models}
-\end{wrapfigure}
-
+%Table
+%\begin{wrapfigure}{r}{0.4\textwidth}
+%\begin{tabular}{lll}
+% &  DMC (eV) & ROKS (eV) \\
+%$\epsilon_{d_\delta}$ &  0.00 & 0.00  \\
+%$\epsilon_{d_\pi}$ & -0.10 & -0.36 \\
+%$\epsilon_{d_{z^2}}$ & 0.41 & 0.52 \\
+%$\epsilon_z$ & 1.20 & 0.66 \\
+%$\epsilon_\pi$ & 2.21 & 0.85 \\
+%$\epsilon_s$ &  2.44 & 4.24 \\
+%$t_\pi$ & -0.22 & -1.14 \\
+%$t_{s d_{z^2}}$ & 0.38 & 0.97 \\
+%$t_{s z}$ & 0.80 & 1.86\\
+%$t_{d_{z^2} z}$ & 0.70 & 1.55\\
+%$J_{sd}$ & -0.51 & 0.00 \\ 
+%$U_s$ & 3.91 & 0.00 \\
+%\end{tabular}
+%\caption{Parameter differences between DFT/DMC models}
+%\end{wrapfigure}
 \end{document}

### 2019-05-20 paper/analysis.tex
finished analysis tex, need to figure out Figures for the outline!

@@
 \usepackage{lineno}
-\linenumbers
-\linespread{2}
-\renewcommand\linenumberfont{\normalfont\bfseries\small}
+\usepackage{float}
 
@@
 In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham (UKS) [ref] single determinant states using a B3LYP functional [ref] and Trail-Needs basis with the corresponding pseudopotentials [ref].
+Spin and spatial-symmetry targeted UKS cannot generate the following singly excited states: $(3d_\pi \rightarrow 2p_\pi)|GS\rangle, (3d_{z^2} \rightarrow 2p_\pi)|GS\rangle$.
+We tried and failed to converge these excited states using constrained DFT.
+Therefore the span of the basestates we are sampling is not the complete 3d9 and 3d10 sectors of the Hilbert space.
 
-First, we generated all the unique base states in the 3d9 and 3d10 sectors using this method.
 In order to sample the span of the base states we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1.
@@
 
-\section{Model selection}
+\section{Model selection and fitting}
 Model selection requires both an understanding of the CuO molecule's low energy excitations and some statistical analysis.
@@
 Since we know that $U_{4s}$ is required to describe the $4s^2$ states and that the $J_{sd}$ will probably play an important role as well, we just need to do model selection on the four hopping parameters.
-Figure 2 shows 5-fold cross-validated (CV) linear regressions using \textit{every} model which includes the $\bar{\epsilon}, J_{sd}, U_{4s}$ parameters above and one element in the power set of $\{\bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}\}$.
 
-The models are increasing in complexity from left-to-right, and it's clear that the fourth model listed here is as accurate as the most complex model, and significantly simpler.
-Therefore, we select that model as it captures the most variation with the fewest parameters.
-The selected model then looks like this:
-$$ \boxed{\text{Selected model: }\bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, J_{sd}, U_{4s}}$$
+\subsection{Ordinary Linear Regression (OLS)}
+To choose a model we first conduct OLS on all sixteen models which have subsets of these hopping parameters and conducting, We then removed from consideration any model which had OLS coefficients which were zero within two standard deviations of the mean, derived from boostrap resampling.
+We find that the $R^2$ scores between the resultant models are comparable and high, above 0.95.
+Since we were not able to sample the full low-energy (LE) space, the $R^2$ score itself is not a complete description of the validity of a model our LE space since an increased $R^2$ score can be due to overfitting of the model within our sample space (SS), leading to large extrapolation errors of our model predictions in the unsampled parts of the LE space.
+In order to investigate the extent of the extrapolation errors between models, we ran exact diagonalization (ED) calculations on our models in the IAO basis.
+After constructing the means and errors of the eigenvalues by bootstrapping, we removed any models with had an average error in the eigenvalues greater than 0.25 eV.
+This leaves just five models under consideration which have comparable $R^2$ score and small errors in the ED eigenvalues.
+Within these five models are two states which have a large extrapolation error as shown in the red boxes of Figure 2.
+The two states under consideration are a $(3dz^2 \rightarrow 2p_\pi)|GS\rangle, (2p_\pi \rightarrow 4s, d\bar{t}_\pi = 0)|GS\rangle$.
+As described earlier, the first state was not accessible by our sampling method and therefore no samples within SS can constrain the energy of this state.
+The latter state is also outside our sample set for a less obvious reason.
+Our sample space does contain a $(2p_\pi \rightarrow 4s)|GS\rangle$ state, however it has $d\bar{t}_\pi > 0$ because of the bonding nature of the $3d_\pi, 2p_\pi$ orbitals.
+In order to get the $d\bar{t}_\pi = 0$ state would require there to be no bonding between these orbitals or a linear combination with a state $d\bar{t}_\pi < 0$.
+Neither of these conditions are possible within our SS, hence the $(2p_\pi \rightarrow 4s, d\bar{t}_\pi = 0)|GS\rangle$ state is not contained in SS.
+Therefore, in order to pick one model out of our five potential models, we need to apply constraints on states which the ED may describe as low-energy, but which we did not sample.
 
-\section{Model fitting}
-We conducted a weighted least squares regression on our samples in order to fit the six parameters in our selected model.
-The higher density of states with 3d9 occupation made it so that an unweighted linear regression would bias towards a more accurate description of the 3d9 states, leaving the 3d10 states fit very poorly.
-Since we are particularly interested in describing the lowest energy eigenstates accurately, which are 3d10 in character, we need to weight our linear regression so that the 3d10 sector is fit more accurately than in the unweighted case.
-The weighting function we used was $e^{-\beta E_{DMC}}$, where $\beta$ is a variable "temperature" which was varied from 0.25 to 3.75 in increments of 0.25.
-We find that in the range of $\beta \in \{1.5, 2.5\}$ the model does not change very much, therefore we select a model at $\beta = 2.0$, which leads to the following set of regressed parameters:
+%Figure 2
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\linewidth]{extrap.pdf}
+\label{fig:extrap}
+\caption{Two out of the five potential models with red boxes indicating the low-energy states which suffer a large extrapolation error.}
+\end{figure}
+
+\subsection{OLS with a prior}
+In order to constrain samples outside of our set we can use information about eigenstates in LE - SS to construct a Bayesian prior.
+We know that LE - SS should be spanned by states of type $(3d_\pi \rightarrow 2p_\pi), (3d_{z^2} \rightarrow 2p_\pi), (3d_{z^2} \rightarrow 2s)$ and any composite excitations built on these states.
+While we cannot generate wave functions which represent these states using UKS, we can generate wave functions with higher energy which lack relevant orbital relaxations via molecular orbital excitations on the UKS ground state.
+Doing so and using these as trial functions in DMC, we find that all of these states have DMC energies $\geq$ 3.5 eV.
+This energy provides upper bounds for the lowest energy states with these certain occupation properties, and allows us to construct a pretty reasonable prior.
+
+$$\text{\textbf{Prior: }Any eigenstates outside of our SS should have an energy expectation } \langle H \rangle \sim \langle H_m \rangle \ge E_{cut} = 2 eV$$
+
+The choice of 2eV as our lower bound for these eigenvalues was chosen because it falls significantly below 3.5 eV, allowing for the possibility of these states being heavily relaxed, but also constraining the energy to be higher than the lowest energy singly excited 3d10 states.
+In order to enforce this prior we use the following cost function to fit our linear models:
+
+$$ \text{Cost} = \sum_i (y_i - \hat{y}_i)^2 + \lambda\sum_p Sig(E_{cut} - E_p), Sig(x) = \frac{1}{1+e^{-x}}.$$
+
+The first term of this cost function is just the standard OLS cost with index $i$ running over our DMC samples within SS.
+The second term penalizes eigenstates which have energy below the chosen $E_{cut} = 2eV$.
+The index $p$ here runs over the eigenstates from section 4.1 which had a large extrapolation error.
+Therefore the second term is a simple implementation of our prior.
+The value of $\lambda$ can be varied in order to tradeoff the importance of each term.
+
+Starting with our five initial models, we allow $\lambda$ to vary between 0 to 40 with steps of 5 and conduct our linear regression with the above cost fuction.
+We then pass these models into ED and remove any models which have energy errors greater than 0.25 eV as before.
+Figure 3 shows the difference between $E_p$ and $E_{cut} = 2eV$ for the two different states composing the index $p$.
+It is pretty clear that the only model which is best at satisfying the prior for \textit{both} states is model 5.
+The regression with model 5 and $\lambda = 15$ match our prior the best and still have a good $R^2 = 0.96$ value and small noise.
+The final chosen model then accurately describes our SS and satisfies our prior for states within LE - SS and has form:
 \begin{multline}
- \boxed{\text{Final model }  (\beta=2): \bar{\epsilon}_z = 1.06(6) eV, \bar{\epsilon}_\pi = 2.12(5) eV, \bar{\epsilon}_s = 3.08(4) eV}\\
-\boxed{\bar{t}_\pi = 0.52(4) eV, J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
+ \boxed{\text{Final model }: \bar{\epsilon}_z = 0.65(7) eV, \bar{\epsilon}_\pi = 1.8(1) eV, \bar{\epsilon}_s = 3.0(1) eV, J_{sd} = -0.8(3) eV, U_{4s} = 3.8(5) eV}
 \end{multline}
 
-In order to look at the predictions of this model, we can rotate the MO basis elements into the IAO basis elements.
-Doing so yields the following more complicated model (note the lack of bars on the model parameters now!):
-
-\begin{multline}
- \boxed{\text{Final model }  (\beta=2): \epsilon_{d_\delta} = 0.00 eV, \epsilon_{d_\pi} = -0.10 eV, \epsilon_{d_z^2} = 0.41 eV }\\
- \boxed{\epsilon_z = 1.2 eV, \epsilon_\pi = 2.21 eV, \epsilon_s = 2.44 eV}\\
-\boxed{t_\pi = -0.22 eV, t_{d_z^2 s} = 0.38 eV, t_{s z} = 0.80 eV, t_{d_z^2 z} = 0.70 eV}\\
-\boxed{  J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
-\end{multline}
-
-Shown in Figure 3 are predictions using $\beta = 2.0$ with 95\% confidence intervals on the full set of samples and only on the base states.
-In both cases the model was fit using the full set of samples.
-Figure 4 shows for $\beta=2.0$ the sample weights versus the trace ($\bar{n}_{3d} + \bar{n}_{p_z} + \bar{n}_{p_\pi} + \bar{n}_{4s}$) of the 1-rdm in our chosen MO basis for the different samples.
-As mentioned in section 3, the weights of samples which have a trace that vary significantly from the ground state trace of 14.80 are small, indicating that our regression is fitting primarily to states for which the MO basis is functioning properly.
+%Figure 3
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\linewidth]{prior.pdf}
+\label{fig:extrap}
+\caption{Difference from cutoff for different models for different $\lambda$.}
+\end{figure}
 
@@
 
-\pagebreak
-%Figure 2
-\begin{figure}
-\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/cv_valid.pdf}
-\caption{5-fold CV regressions for model selection}
-\end{figure}
-
-%Figure 3
-\begin{figure}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit.pdf}
-  \caption{DMC predictions for all samples.}
-  \label{fig:sub6}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_baseonly.pdf}
-  \caption{DMC predictions for basestates. }
-  \label{fig:sub7}
-\end{subfigure}
-\label{fig:test2}
-\caption{DMC regression using all states and $\beta=2.0$.}
-\end{figure}
-
-%Figure 4
-\begin{figure}
-\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/w_vs_t.pdf}
-\caption{Weights versus trace for linear regression with $\beta=2.0$.}
-\end{figure}
-
-%Figure 5
-\begin{figure}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues.pdf}
-  \caption{Eigenvalues of DMC fit model, hue $\beta$.}
-  \label{fig:sub1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues_sz.pdf}
-  \caption{Eigenvalues of DMC fit model, hue $S_z$.}
-  \label{fig:sub2}
-\end{subfigure}
-\label{fig:test1}
-\caption{Eigenstates of models from DMC}
-\end{figure}
-
-%Figure 6
-\begin{figure}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/roks_eigenvalues.pdf}
-  \caption{Eigenvalues of ROKS effective model.}
-  \label{fig:sub3}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/uks_eigenvalues.pdf}
-  \caption{Eigenvalues of UKS effective model.}
-  \label{fig:sub4}
-\end{subfigure}
-\label{fig:test2}
-\caption{Eigenstates of 1-particle models from DFT}
-\end{figure}
-
-%Table
-%\begin{wrapfigure}{r}{0.4\textwidth}
-%\begin{tabular}{lll}
-% &  DMC (eV) & ROKS (eV) \\
-%$\epsilon_{d_\delta}$ &  0.00 & 0.00  \\
-%$\epsilon_{d_\pi}$ & -0.10 & -0.36 \\
-%$\epsilon_{d_{z^2}}$ & 0.41 & 0.52 \\
-%$\epsilon_z$ & 1.20 & 0.66 \\
-%$\epsilon_\pi$ & 2.21 & 0.85 \\
-%$\epsilon_s$ &  2.44 & 4.24 \\
-%$t_\pi$ & -0.22 & -1.14 \\
-%$t_{s d_{z^2}}$ & 0.38 & 0.97 \\
-%$t_{s z}$ & 0.80 & 1.86\\
-%$t_{d_{z^2} z}$ & 0.70 & 1.55\\
-%$J_{sd}$ & -0.51 & 0.00 \\ 
-%$U_s$ & 3.91 & 0.00 \\
-%\end{tabular}
-%\caption{Parameter differences between DFT/DMC models}
-%\end{wrapfigure}
 \end{document}

### 2019-05-20 paper/old_outline.tex
finished analysis tex, need to figure out Figures for the outline!

--- 2019-04-24 paper/outline.tex
@@
 \usepackage[margin=1.0in]{geometry}
+\usepackage{float}
 
@@
 \section{Figures}
-
 %Figure 1
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
   \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log.pdf}
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/regr_log.pdf}
   \caption{Prediction of linear regression on full set of samples.}
@@
   \centering
-  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log_base.pdf}
+  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/regr_log_base.pdf}
   \caption{Prediction of linear regression on base states only.}
@@
 %Figure 2
-\begin{figure}
+\begin{figure}[H]
 \centering
-\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/}
-\label{fig:Regression}
+\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/ed_0_log.pdf}
+\label{fig:ED}
 \caption{Results for energies and 1-/2-body properties of eigenstates from exact diagonalization of our model Hamiltonian.}
@@
 \section{Supplementary Material} 
+%Supplementary Figure 1
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/r2_test.pdf}
+\label{fig:OneParm}
+\caption{Cross validated R2 scores for all sixteen models under consideration, hued by $\beta$.}
+\end{figure}
 
+%Supplementary Figure 2
+\begin{figure}[H]
+\centering
+\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/Xerr.pdf}
+\label{fig:Xerr}
+\caption{Ranges of parameters from ED using the first 80 eigenstates compared against the ranges of the DMC training data.}
+\end{figure}
+
+%Supplementary Figure 3
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\linewidth]{../qwalk/ub3lyp_s1_/analysis/ed_combined_log.pdf}
+\label{fig:ED_comp}
+\caption{ED results for the four selected models, different models have different markers.
+Models with more parameter have larger error bars, but all three models have similar results within errorbars.}
+\end{figure}
+
+%Table 1
+%\begin{figure}[H]
+\begin{table}[H]
+\centering
+\begin{tabular}{l|lllll}
+    & Model 0 & Model 2 & Model 3 & Model 8 & Model 14 \\ \hline
+$\bar{\epsilon}_s$  & 3.0(1)  & 3.1(1)  & 3.0(1)  & 3.1(1)  & 2.9(1)   \\
+$\bar{\epsilon}_\pi$ & 1.9(1)  & 1.7(1)  & 1.9(2)  & 1.4(2)  & 1.4(2)   \\
+$\bar{\epsilon}_z$ & 0.8(1)  & 0.6(1)  & 0.8(2)  & 0.4(2)  & 0.6(2)   \\
+$\bar{t}_{sz}$& 0       & -0.5(1) & 0       & -0.7(2) & -0.4(2)  \\
+$\bar{t}_{sz}$& 0       & 0       & \textcolor{red}{-0.2(5)} & 0.8(4)  & \textcolor{red}{0.4(5)}   \\
+$\bar{t}_{ds}$& 0       & 0       & 0       & 0       & 0.7(4)   \\
+$\bar{t}_{\pi}$& 0       & 0       & 0       & 0       & 0        \\
+$J_{sd}$ & -0.8(3) & -0.5(3) & -0.7(3) & -0.7(3) & -0.6(3)  \\
+$U_s$  & 4.7(5)  & 4.2(6)  & 4.7(5)  & 4.0(5)  & 3.7(6)  
+\end{tabular}
+\label{fig:Table1}
+\caption{Model parameters for models with appropriate descriptor ranges.}
+\end{table}
+%\end{figure} 
 \end{document}

### 2019-05-20 paper/outline.tex
finished analysis tex, need to figure out Figures for the outline!

--- 2019-04-24 paper/outline.tex
@@
 \documentclass{article}
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage{subcaption}
+\usepackage[margin=1.0in]{geometry}
+\usepackage{float}
+
 \begin{document}
@@
 \item \textbf{General goal: }
-Systematically develop model Hamiltonians which can accurately describe the energies as well as one- and two-particle properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.
+Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.
 
@@
 \item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.
+\textcolor{red}{Have to find references for this one, not sure how true this is.}
 
-\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe the energies, one- and two-particle properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
+\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
 \end{enumerate}
 
-\section{Figures}
-
+%Figure 1 - Show extrapolation error somehow
+%Figure 2 - Show prior regression results
+%Figure 3 - Show final regression + ED
 \end{document}

### 2019-05-20 qwalk/old/ub3lyp_s1_/analyzedmc.py

@@ -624,7 +624,7 @@ def analyze(df=None,save=False):
 
   #Plot ed
   avg_eig_df = pd.read_pickle('analysis/avg_eig.pickle')
-  for model in [5,9,12,21,20,24]:
+  for model in [9,12]:
     plot_ed(df,avg_eig_df,model=model)
 
 if __name__=='__main__':

### 2019-05-20 qwalk/old/ub3lyp_s1_/analyzeprior.py

@@ -76,7 +76,6 @@ def analyze(df=None,save=False):
   #Analysis
   df = add_priors(df,cutoff = 2)
 
-  '''
   #Generate models + get all the proeperties we need
   oneparm_df = pd.read_pickle('analysis/oneparm.pickle').drop(columns=['r2_mu','r2_err'])
   prior_df = None
@@ -89,11 +88,12 @@ def analyze(df=None,save=False):
     fit_df = df[['energy','prior']+model]
     fit_df['const'] = 1
 
-    lams = np.arange(0,80,20)
+    lams = [15]#np.arange(0,40,5)
     E_errs = []
     s1 = []
     s2 = []
     r2 = []
+    z = []
     for lam in lams:
       print("lambda = "+str(lam)) 
       E = []
@@ -102,10 +102,13 @@ def analyze(df=None,save=False):
         params = prior_fit(d,lam)
         e = ed(model,params[:-1])
         E.append(np.array(e[0]+e[1])-min(e[0]+e[1]))
-     
+        z.append(params)
+        
       params = prior_fit(fit_df,lam)
       score = prior_score(params,fit_df)
-      print(score)
+      print(np.array(z).mean(axis=0))
+      print(np.array(z).std(axis=0))
+      exit(0)
 
       E_errs.append(np.std(E,axis=0).mean())
       s1.append(score[1].values[0])
@@ -115,13 +118,18 @@ def analyze(df=None,save=False):
     data = pd.DataFrame({'r2':r2,'E_errs':E_errs,'s1':s1,'s2':s2,'lam':lams,'model':i*np.ones(len(r2))})
     if(prior_df is None): prior_df = data
     else: prior_df = pd.concat((prior_df,data),axis=0)
+    exit(0)
   prior_df.to_pickle('analysis/prior.pickle')
-  '''
 
+  exit(0)
+  
+  '''
   prior_df = pd.read_pickle('analysis/prior.pickle')
   prior_df = prior_df[prior_df['E_errs']<=0.25]
+  print(prior_df)
   sns.scatterplot(data =prior_df, x='s1',y='s2',hue='model')
   plt.show()
+  '''
 
 if __name__=='__main__':
   #DATA COLLECTION

### 2019-05-26 paper/outline.tex
first draft of outline ready

@@
 
+\section{Methods}
+\begin{enumerate}
+\item \textbf{Density matrix downfolding} The DMD procedure allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian $H_{ab}$.
+
+\item \textbf{Defining the low-energy space} We define the low-energy space for the CuO molecule as the full space of states with 9 to 10 electrons in the Cu 3d orbitals.
+
+\item \textbf{Sample states} States within our low energy space (LE) were generated by sampling the span of base states - states which approximately describe true eigenstates within LE.
+
+\item \textbf{Model basis} We constructed two bases for our model Hamiltonian, a localized atomic basis for evaluating two-body reduced density matrix (2-rdm) elements, and a molecular orbital basis for one-body reduce density matrix (1-rdm) elements.
+
+\item \textbf{Model selection and fitting}
+\begin{enumerate}
+\item We initially narrow down the space of potential models by discarding any models which do not contain the descriptors $n_{4s}, n_{2p_\pi}, n_{2p_z}, J_{sd}, U_s$.
+
+\item Our inability to sample certain states within the LE space manifests itself through intruder eigenstates within our selected models.
+
+\item In order to ensure that intruder states are not present within our final model, we enforce a prior that pushes intruder states above a chosen $E_{cut}$ by altering the cost function for our regression.
+
+\item \textcolor{red}{Might want to put this in discussion, not sure.}
+\end{enumerate}
+\end{enumerate}
+
+\section{Discussion}
+\begin{enumerate}
+\item \textbf{Regression with prior} Using our new cost function we find a set of models which accurately describe our sample set without the presence of intruder states.
+
+\item \textbf{Comparison to experiment} The selected low-energy model accurately describes the energies and single particle properties of the low-energy eigenstates of CuO as measured in experiment.
+
+\item \textbf{Comparison to DFT} Our model is more accurate than a single-particle model constructed using density functional theory orbitals and eigenvalues.
+\end{enumerate}
+
+\section{Conclusion}
+\begin{enumerate}
+\item \textbf{Our findings} We have systematically developed a low-energy model for the CuO molecule which can quantitatively accurately describe the energies and properties of the lowest lying eigenstates as seen in experiment starting from the many-body \textit{ab-initio} Hamiltonian.
+
+\item \textbf{Avenues of interest} The procedure outlined here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
+\end{enumerate}
+
 %Figure 1 - Show extrapolation error somehow

### 2019-05-26 qwalk/old/ub3lyp_s1_/testing_scripts/check_ed.py

@@ -5,7 +5,6 @@ from functools import reduce
 import matplotlib.pyplot as plt 
 
 #1-body 
-'''
 #MO to IAO Matrix in the correct ordering 
 #dxy, dy, dz, z, py, s
 act_iao=[5,6,7,13,12,1]
@@ -41,12 +40,12 @@ mo_to_iao = reduce(np.dot,(mo.T,s,iao))
 #IAO = [0,0.1,0.39,0.74,1.72,2.16,-0.43,0.56,0.83,0.67]
 
 #model 20
-#MO = [0,0,0,0.45,2.08,2.87,0.22,0,-0.9,0]
-#IAO = [0,0.08,0.48,1.46,2.00,1.3,-0.46,0.84,1.25,0.71]
+MO = [0,0,0,0.45,2.08,2.87,0.22,0,-0.9,0]
+IAO = [0,0.08,0.48,1.46,2.00,1.3,-0.46,0.84,1.25,0.71]
 
 #model 24 
-MO = [0,0,0,0.32,1.74,2.78,0,-0.21,0,0.11]
-IAO = [0,0.18,0.44,0.56,1.57,2.02,-0.52,0.53,0.98,0.49]
+#MO = [0,0,0,0.32,1.74,2.78,0,-0.21,0,0.11]
+#IAO = [0,0.18,0.44,0.56,1.57,2.02,-0.52,0.53,0.98,0.49]
 
 H1_MO = np.diag(MO[:6])
 H1_IAO = np.diag(IAO[:6])
@@ -70,8 +69,8 @@ print(np.around(w2,2))
 ovlp = reduce(np.dot,(vr.T,mo_to_iao,vr2))
 plt.matshow(ovlp,vmin=-1,vmax=1,cmap = plt.cm.bwr)
 plt.show()
-'''
 
+'''
 #2-body
 #Jsi = 0.25*(ns_u - ns_d)*(ni_u - ni_d) + 
 #0.5*(cs_u^+ cs_d ci_d^+ ci_u + cs_d^+ cs_u ci_u^+ ci_d)
@@ -103,3 +102,4 @@ eri = (eri_aa, eri_ab, eri_bb)
 
 e, ci = fci.direct_uhf.kernel(h1, eri, norb, nelec, nroots=10)
 print(e)
+'''

### 2019-05-27 paper/outline.tex
cleaned up outline, gonna shoot it to lucas

--- 2019-05-20 paper/outline.tex
@@
 \begin{enumerate}
-\item \textbf{General goal: }
+\item \textbf{General goal}
 Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.
 
-\item \textbf{Barrier to achieving that goal: } The necessity for many-body interactions in describing the low-lying excited states of TMO molecules poses a difficult challenge when developing model Hamiltonians.
+\item \textbf{Barrier to achieving that goal} The necessity for many-body interactions in describing the low-lying excited states of TMO molecules poses a difficult challenge when developing model Hamiltonians.
 
-\item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.
+\item \textbf{State of the art} Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.
 \textcolor{red}{Have to find references for this one, not sure how true this is.}
 
-\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
+\item\textbf{How are we advancing state of the art} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
 \end{enumerate}
 
-%Figure 1 - Show extrapolation error somehow
-%Figure 2 - Show prior regression results
-%Figure 3 - Show final regression + ED
+\section{Methods}
+\begin{enumerate}
+\item \textbf{Density matrix downfolding} The DMD procedure allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian $H_{ab}$.
+
+\item \textbf{Defining the low-energy space} We define the low-energy space for the CuO molecule as the full space of states with 9 to 10 electrons in the Cu 3d orbitals.
+
+\item \textbf{Sample states} Our sample space (SS) was generated by sampling the span of base states - states which approximately describe true eigenstates within the LES - using multi-Slater-Jastrow trial wave functions in Diffusion Monte Carlo (DMC).
+
+\item \textbf{Model basis} We constructed two bases for our model Hamiltonian, a localized intrinsic atomic orbital (IAO) basis for evaluating two-body reduced density matrix (2-rdm) elements, and a molecular orbital (MO) basis for one-body reduced density matrix (1-rdm) elements.
+
+\item \textbf{Model selection and fitting}
+\begin{enumerate}
+\item We initially narrowed down the space of potential models by discarding any which did not at minimum contain descriptors essential in describing the low-energy space: $n_{4s}, n_{2p_\pi}, n_{2p_z}, \Sigma_{J_{sd}}, \Sigma_{U_s}$.
+\textcolor{red}{"Essential" should be determined through experimental knowledge + variation of descriptors within our SS}.
+
+\item After fitting each potential model using ordinary linear regression (OLS) and solving the resultant models using exact diagonalization, we find a set of models which describe the energy functional on our SS accurately but whose eigenstates and spectra differ.
+\textcolor{red}{Need a figure to show this.}
+
+\item Our inability to sample certain states within our target LE space manifests itself through intruder eigenstates within our fit models.
+
+\item In order to ensure that intruder states are not present within our final model, we enforce a prior that pushes intruder states above a chosen $E_{cut}$ = 2eV by altering the cost function for our regression.
+\end{enumerate}
+\end{enumerate}
+
+\section{Discussion}
+\begin{enumerate}
+\item \textbf{Regression with prior} Using our new cost function we find a set of models which accurately describe the energy functional on our SS, have similar spectra and eigenvectors, and do not contain  intruder states below a cutoff energy $E_{cut} $= 2eV.
+
+\item \textbf{Comparison to experiment} The selected low-energy model accurately describes the energies and single particle properties of the low-energy eigenstates of CuO as measured in experiment.
+
+\item \textbf{Comparison to DFT} Our model is more accurate than a single-particle model constructed using density functional theory orbitals and eigenvalues.
+\end{enumerate}
+
+\section{Conclusion}
+\begin{enumerate}
+\item \textbf{Our findings} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
+
+\item \textbf{Avenues of interest} The procedure outlined here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
+\end{enumerate}
+
+\pagebreak
+\section{Figures}
+\begin{figure}[H]
+\centering
+\begin{subfigure}{.4\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/MD.pdf}
+  \caption{Mahalanobis distances of excited eigenstates below 2eV.}
+  \label{fig:Intruder1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/intruders.pdf}
+  \caption{Properties and energies of intruder states.}
+  \label{fig:Intruder2}
+\end{subfigure}
+\label{fig:Intruder}
+\caption{a) The selection process for intruder states.
+Any excited eigenstates below 2eV with a Mahalanobis distance greater than 80 away from our SS are considered intruder states.
+b) The properties and energies of the selected intruder states.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/prior.pdf}
+\label{fig:Prior}
+\caption{The $R^2$ scores and quadratic hinge loss versus $\lambda$ for the prior regression on the different models under consideration.
+The quadratic hinge loss converges to a single value for all six selected models as $\lambda$ is increased to 20 while the $R^2$ score stays above 0.95.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/params.pdf}
+  \label{fig:Params1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/params_iao.pdf}
+  \label{fig:Params2}
+\end{subfigure}
+\label{fig:Params}
+\caption{The parameters fit for six different models using the prior cost function with $\lambda = 20$.
+On the left have the 1-body parameters in the MO basis and the right have the 1-body parameters in the IAO basis.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/regr_m5_l20.pdf}
+  \caption{Predicted versus sampled energies.}
+  \label{fig:Fit1}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/ed_m5_l20.pdf}
+  \caption{Results of exact diagonalization.}
+  \label{fig:Fit2}
+\end{subfigure}
+\label{fig:Fit}
+\caption{The results of using the altered cost function with a prior to fit model 5 with $\lambda = 20$.}
+\end{figure}
 \end{document}

### 2019-05-31 paper/outline.tex
small changes to outline, got to get figures good

@@
 \usepackage{float}
+\usepackage{ulem}
 
@@
 \item \textbf{General goal}
-Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.
+Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electrons systems.
 
-\item \textbf{Barrier to achieving that goal} The necessity for many-body interactions in describing the low-lying excited states of TMO molecules poses a difficult challenge when developing model Hamiltonians.
+\item \textbf{Barrier to achieving that goal} The necessity for many-body interactions in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing model Hamiltonians.
 
-\item \textbf{State of the art} Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.
+\item \textbf{State of the art} Common approaches to building these model Hamiltonians use effective single particle theories like density functional theory (DFT) to generate an effective 1-body model or build phenomenological models based on experimental measurements of the properties and energies of low-lying excitations.
 \textcolor{red}{Have to find references for this one, not sure how true this is.}
 
-\item\textbf{How are we advancing state of the art} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
+\item\textbf{How are we advancing state of the art} In this paper we systematically fit a many-body model which can accurately describe energies and properties of low-lying eigenstates for the neutral CuO molecule using a generalizable \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method, and discuss the details of and developments in the model fitting procedure.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \textbf{Our findings} We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure.
+\item \textbf{Our findings} In this paper we systematically fit a many-body model for the neutral CuO molecule which can accurately reproduce the spectrum and properties of low-lying eigenstates seen in experiment using a \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method, and discuss the details of and developments in our model fitting procedure.
 
-\item \textbf{Avenues of interest} The procedure outlined here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
+\item \textbf{Avenues of interest} The fitting procedure illustrated here can be extended to other neutral transition metal oxide molecules, allowing for the construction of a sequence of low-energy models across the transition metals.
 \end{enumerate}

### 2019-06-02 paper/bw_book.tex
bw book figure and caption done

\documentclass{article}
\usepackage{graphicx}
\begin{document}
\begin{figure}
	\begin{center}
    \includegraphics[width=\textwidth]{bw_book_fig.pdf}
  \end{center}
  \caption{Shown is the data-driven selection and fitting process used in developing a low-energy effective model of the CuO molecule using a density matrix downfolding procedure. The figures on the left indicate the performance of candidate models on sampled data via an R$^2$ score and the degree to which a prior condition is satisfied through a quadratic hinge loss (QHL) as a control parameter $\lambda$ in the cost function is varied. The figure on the right shows the predicted energy E\textsubscript{eff} for the best model, the minimal model at $\lambda$ = 20, against the target energy E\textsubscript{DMC} for training samples used in the regression. All errorbars are 95\% confidence intervals estimated through bootstrappping.}
\end{figure}
\end{document}

### 2019-06-02 qwalk/old/ub3lyp_s1_/analyzeprior.py

@@ -362,8 +362,8 @@ def analyze(df=None,save=False):
   #Generate models and plot cost 
   #prior_df = prior_analysis(df,cutoff=cutoff)
   #prior_df.to_pickle('analysis/prior.pickle')
-  plot_prior()
-  exit(0)
+  #plot_prior()
+  #exit(0)
 
   #ED for models
   '''

### 2019-06-02 qwalk/old/ub3lyp_s1_/analyzedmc.py
reorganizing figures. have post prior done, need pre-prior figures!

@@ -560,17 +560,22 @@ def plot_ed(full_df,av_df,model,save=True):
   plt.show()
   return -1
 
-def plot_ed_small(full_df,av_df,model,save=True):
+def plot_ed_small(full_df,av_df,model,fname=None,title=None):
   norm = mpl.colors.Normalize(vmin=0, vmax=3.75)
-  limits = [(0.5,2.5),(2.5,4.5),(1.5,4.5),(0.5,2.5),(1.5,4.5),(0,1.5)]
+  limits = [(0.5,2.5),(2.5,4.5),(2.5,4.5),(0.5,2.5),(1.5,4.5),(-0.75,1.5)]
     
   rgba_color = plt.cm.Blues(norm(1.75))
   rgba_color2 = plt.cm.Oranges(norm(1.75))
   z=-1 
   fig, axes = plt.subplots(nrows=2,ncols=3,sharey=True,figsize=(6,6))
+  xlabels = [r'n$_{d_{z^2}}$',r'n$_{d_{\pi}}$',r'n$_{d_{\delta}}$',
+  r'n$_{z}$',r'n$_{\pi}$',r'n$_{s}$']
   for parm in ['iao_n_3dz2','iao_n_3dpi','iao_n_3dd','iao_n_2pz','iao_n_2ppi','iao_n_4s']:
     z+=1 
     ax = axes[z//3,z%3]
+
+    l1 = None
+    l2 = None
 
     #DMC Data
     full_df['energy'] -= min(full_df['energy'])
@@ -579,8 +584,7 @@ def plot_ed_small(full_df,av_df,model,save=True):
     x = f_df[parm].values
     y = f_df['energy'].values
     yerr = f_df['energy_err'].values
-    if(parm=='iao_n_3dd'): ax.errorbar(x,y,yerr,fmt='s',c=rgba_color,alpha=0.5,label='DMC')
-    else: ax.errorbar(x,y,yerr,fmt='s',c=rgba_color,alpha=0.5)
+    ax.errorbar(x,y,yerr,fmt='s',c=rgba_color,alpha=0.5)
 
     f_df = full_df[full_df['Sz']==1.5]
     x = f_df[parm].values
@@ -599,7 +603,6 @@ def plot_ed_small(full_df,av_df,model,save=True):
     y=sub_df['energy'].values
     yerr_u=sub_df['energy_u'].values
     yerr_d=sub_df['energy_l'].values
[…]

### 2019-06-02 qwalk/old/ub3lyp_s1_/analyzeprior.py

@@ -183,7 +183,7 @@ def plot_prior():
     z+=1
   plt.legend(loc='best')
   plt.xticks(np.arange(0,24,4))
-  plt.ylabel('QHL')
+  plt.ylabel(r'QHL (eV$^2$)')
   plt.xlabel(r'$\lambda$')
   plt.savefig('analysis/figs/prior.pdf',bbox_inches='tight')
   return -1
@@ -375,7 +375,7 @@ def analyze(df=None,save=False):
       avg_df = avg_ed(ed_df)
       avg_df.to_pickle('analysis/avg_eig_prior_m'+str(model)+'_l'+str(lam)+'.pickle')
   '''
- 
+
   #Lowest noise model
   '''
   for model in [9,20,21,12,24,5]:
@@ -389,13 +389,16 @@ def analyze(df=None,save=False):
   '''
  
   #ED plot
-  model = 5
+  model = 12
   lam = 20
-  #avg_df = pd.read_pickle('analysis/avg_eig_prior_m'+str(model)+'_l'+str(lam)+'.pickle')
-  #plot_ed_small(df,avg_df,model)
+  titles={5:r'Min',9:r'Min$ + \bar{t}_\pi$',
+  12:r'Min$ + \bar{t}_{dz}$',20:r'Min$ + \bar{t}_\pi, \bar{t}_{sz}$',
+  21:r'Min$ + \bar{t}_\pi, \bar{t}_{ds}$',24:r'Min$ + \bar{t}_{ds}, \bar{t}_{dz}$'}
+  avg_df = pd.read_pickle('analysis/avg_eig_prior_m'+str(model)+'_l'+str(lam)+'.pickle')
+  plot_ed_small(df,avg_df,model,fname='analysis/figs/ed_m'+str(model)+'_l'+str(lam)+'.pdf',title=titles[model]+r' model, $\lambda$='+str(lam))
   
   #Linear regression plot of selected model 
-  regr_prior(df,model,lam)
+  #regr_prior(df,model,lam)
 
   #Model parameters
   #params_df = iao_analysis(df)

### 2019-06-04 paper/draft.tex
working on cuo paper draft

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}
\usepackage{ulem}
\usepackage{amsmath}
\usepackage{mathtools}

\begin{document}
\section{Introduction}

\section{Methods}
The DMD procedure \textbf{[ref]} allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian under a Born-Oppenheimer approximation:

\begin{equation}
H_\text{ab} = -\frac{1}{2} \sum_{i} \nabla_i^2 - \sum_{i,I}\frac{Z}{|r_i - R_I|} + \sum_{i<j}\frac{1}{|r_i - r_j|}
\end{equation}
where $i$ indicates electrons and $I$ nuclei. 
The unit of energy using this Hamiltonian is Hartree (Ha). 
The goal of DMD is to downfold the \textit{ab-initio} Hamiltonian and Hilbert space onto an effective Hamiltonian acting on a low-energy subspace of the Hilbert space

\begin{equation}
(H_\text{ab}, \mathcal{H}) \xrightarrow{\text{DMD}} (H_\text{eff}, \mathcal{LE} \subset \mathcal{H}) \text{ so that }
\forall |\Psi\rangle \in \mathcal{LE}, \ \langle \Psi | H_\text{ab} | \Psi\rangle = \langle \Psi | H_\text{eff} | \Psi\rangle
\end{equation} 
Broadly the DMD method consists of four steps which will be discussed in detail later: 1) Selecting a low-energy subspace $\mathcal{LE}$ which includes all excitations one wants to describe accurately. 
In theory $\mathcal{LE}$ would be chosen to be the subspace spanned by the N lowest-energy eigenstates of $H_\text{ab}$, but is constructed more approximately in practice.  
2) Generate a set of samples within our low-energy space $\mathcal{SS} \in \mathcal{LE}$. 
The choice of sampling scheme may be system dependent. 
We will discuss a shell-sampling scheme in this paper. 
It is important to note that one does not need to have access to the eigenstates of $H_\text{ab}$ in order to sample a chosen $\mathcal{LE}$, nor are the eigenstates required to be in the sample set.
3) Parameterizing $H_\text{eff}$ as a linear combination of descriptors, 
\begin{equation}
H_\text{eff} = \sum_k a_k \hat{d}_k
\end{equation}
where $\hat{d}_k$ are typically 1- or 2-body reduced density matrix (RDM) elements which can represent single- or two-particle terms in an effective theory.
4) Using the samples to fit the coefficients $\{c_k\}$ such that $H_\text{eff}$ satisfies the conditions in equation (2) as well as possible. 
The fitting procedure is typically an ordinary linear regression, however one may use a custom cost function in the regression as well. 
Therefore the DMD procedure allows us to map the problem of downfolding strongly correlated electrons systems onto a linear regression problem which can then be systematically studied using tools developed in data science and statistics.

Based on anion photoelectron spectroscopy (APES) experiments\textbf{[ref]} on the CuO molecule we define our low-energy space $\mathcal{LE}$ as the space of states with 9 to 10 electrons in the Cu 3d orbitals. 
The APES measurements indicate that the lowest energy excitations in the CuO molecule are between the O p-orbitals and Cu 4s orbitals, leaving around 10 electrons in the Cu 3d orbitals. 
Bonding between the O p and Cu 3d orbitals lead to significant variations in the Cu 3d occupation, indicating the importance of including excitations out of the Cu 3d orbitals. 
This is corroborated by APES measurements indicating that the lowest energy eigenstates with 9 electrons in the Cu 3d orbitals are only $\sim$ 0.2 eV higher in energy than the second excited state of the system with 10 electrons in the Cu 3d orbitals. 
Our particular focus will be on describing most accurately the properties and energies of eigenstates up to 2eV, as higher energy states form a nearly continuous block of states which include vibrational modes.

Our sample space $\mathcal{SS}$ was generated by sampling the span of base states - states which approximately describe true eigenstates within the $\mathcal{LE}$ - using multi-Slater-Jastrow trial wave functions in fixed-node Diffusion Monte Carlo (FN-DMC).

\section{Discussion}

\section{Conclusion}

\end{document}

### 2019-06-05 paper/draft.tex
draft methods done. really rough

@@
 \end{equation}
-where $i$ indicates electrons and $I$ nuclei. 
+where $i$ indicates electrons and $I$ nuclei. We also treat core electrons using pseudo-potentials. 
 The unit of energy using this Hamiltonian is Hartree (Ha). 
@@
 Based on anion photoelectron spectroscopy (APES) experiments\textbf{[ref]} on the CuO molecule we define our low-energy space $\mathcal{LE}$ as the space of states with 9 to 10 electrons in the Cu 3d orbitals.
+Mathematically we can express this space as the span of some eigenstates within our Hilbert space
+\begin{equation}
+\mathcal{LE} = \text{Span(}\{ |\Psi \rangle | \langle \Psi | n_{3d} | \Psi \rangle \ge 9,\ H|\Psi\rangle = E |\Psi\rangle \}\text{)}.
+\end{equation}
 The APES measurements indicate that the lowest energy excitations in the CuO molecule are between the O p-orbitals and Cu 4s orbitals, leaving around 10 electrons in the Cu 3d orbitals. 
@@
 Our sample space $\mathcal{SS}$ was generated by sampling the span of base states - states which approximately describe true eigenstates within the $\mathcal{LE}$ - using multi-Slater-Jastrow trial wave functions in fixed-node Diffusion Monte Carlo (FN-DMC).
+In principle we could sample $\mathcal{LE}$ by taking linear combinations of the eigenvectors which span it.
+In practice we do not have access to these eigenvectors and approximate methods are required to sample the low-energy space.
+We consider wave functions of the following form:
+\begin{equation}
+\lim_{\tau \rightarrow \infty} e^{-\tau H_\text{ab}} (e^{J}\sum_{i} c_i|\text{D}_i\rangle) = \sum_i c_i \lim_{\tau \rightarrow \infty} e^{-\tau H_\text{ab}} (e^J |D_i\rangle) \equiv \sum_i c_i |\Phi_i\rangle .
+\end{equation}
+where $|D_i\rangle$ is a determinant of single particle orbitals, $e^J$ is a three-body Jastrow function in \textbf{ref}, and $e^{-\tau H_\text{ab}}$ is a projection operator which exponentially suppresses high-energy contributions to the wave function and is realized through an FN-DMC calculation.
+This state is an accurate approximation to a state $|\Psi\rangle \in \mathcal{LE}$ of the form $|\Psi \rangle = \sum_i c_i |\Psi_i\rangle$, where $|\Psi_i\rangle$ is an eigenstate within $\mathcal{LE}$, if $\forall i\ |\Phi_i\rangle \sim |\Psi_i\rangle$.
+While $|\Psi_i\rangle$ are eigenstates of $H_\text{ab}$, $|\Phi_i\rangle$ generally are not, but do form the basis for our sample space and will be called \textit{base states}.
+The fixed-node projection can achieve this similarity if the nodes of $|D_i\rangle$ accurately approximate those of $|\Psi_i\rangle $.
+We use symmetry-targeted unrestricted Kohn-Sham (UKS) to generate our determinants $|D_i\rangle$ using a Trail-Needs pseudopotential, VTZ Trail-Needs basis \textbf{ref}, and a B3LYP functional \textbf{ref}, which has been shown to accurately reproduce nodal properties of transition-metal oxide molecules \textbf{ref}.
+These calculations were carried out in the package PySCF \textbf{ref}.
+The symmetry-targeted UKS method allows us to fix the total spin projection S$_z$ and the total number of electrons in a particular irreducible representation (irrep) of the symmetry group under use, $\text{A},\ \text{E}_\text{1x},\ \text{E}_\text{2y}$ etc.
+There are some cases of two or more base states which have identical S$_z$ and number of electrons per irrep.
+within  $\mathcal{LE}$, for example the ground state and the excited state with excitation $c^\dagger_{p_\pi} c_{d_\pi} |GS\rangle$.
+In this scenario the higher energy excitations are inaccessible and excluded from our sample set.
+We will discuss the consequences of this exclusion later on.
+The three-body Jastrow factor was optimized on the lowest energy UKS state using a linear energy optimization methods \textbf{ref}.
+The FN-DMC was conducted with T-moves \textbf{ref} to make the calculation variational while using pseudopotentials with a timestep of $\tau = 0.01$.
+Necessary 1- and 2-RDM elements were also calculated in FN-DMC using a mixed estimator \textbf{ref}.
+The coefficients $\{c_j\}$ were chosen via a shell-sampling method.
+For each base state $|\Phi_i\rangle$ we fix the coefficient $c_i = \sqrt{w},\ w \in \{0.2, 0.4, ..., 1.0\}$ and for each $w$ sample N = 5 states uniformly such that $\sum_j c_j^2 = 1$.
+Looping over $i$ yields shells of samples centered on each base state.
+This sampling scheme tends to be sparse where the density of states of $H_\text{ab}$ is low and therefore extra samples are generated in regions of sparse sample density \textit{post-hoc}.
+This sampling scheme therefore generates a sample set which can be defined as
+\begin{equation}
+\mathcal{SS} \in \text{Span(}\{ |\Phi \rangle | \langle \Phi | n_{3d} | \Psi \rangle \ge 9,\ H|\Phi\rangle = E |\Phi\rangle \}\text{)} \sim \mathcal{LE}.
+\end{equation}
+where $|\Phi\rangle$ is defined in (5), and which maps exactly onto the true $\mathcal{LE}$ if our base states exactly match the true eigenstates of $H_\text{ab}$.
 
+Parameterizing our effective model requires constructing a basis on which to calculate our \textit{ab-initio} 1-/2-RDM elements and selecting a set of descriptors from which we would like to build our model.
+We constructed two bases for our model Hamiltonian, a localized intrinsic atomic orbital (IAO) basis for evaluating two-body reduced density matrix (2-rdm) elements, and a molecular orbital (MO) basis for one-body reduced density matrix (1-rdm) elements.
+The two-body interactions we are interested in are typically local interactions, for example a Hubbard-U, Hund's-J or superexchange-J, therefore motivating a local basis for the two-body terms.
+In the CuO molecule there is heavy hybridization between the Cu d and O p orbitals, and an MO basis can compactly represent this hybridization, leading us to use MO basis elements for our one-body basis elements.
+Based on experimental measurements and the structure of the data within our $\mathcal{SS}$, the lowest energy excitations of the CuO molecule have excitations between Cu d, O p and Cu 4s orbitals.
+APES measurements do not see any 4s$^2$ states in the low-energy spectra which is corroborated by our FN-DMC energy for the lowest energy base state with a Cu 4s$^2$ occupation is $\sim$ 7 eV above the lowest energy base state.
+Including the $\sim$ 0.5eV Hund's coupling on the copper atom, we believe that a minimal model for our downfolding must contain: $\bar{n}_{4s}, \bar{n}_{p_\pi}, \bar{n}_{p_z}, \sum_{i \in \{xy, xz, ...\}}\vec{S}_{4s}\cdot \vec{S}_{d_i}, n_{4s, \uparrow} n_{4s,\downarrow}$.
+The barred terms are built on the MO basis, and the non-barred ones on the IAO basis.
+The exclusion of $n_{3d}$ from our minimal model is because of the total number of electrons being constrainted by $\bar{n}_{3d} + \bar{n}_{p_\pi} + \bar{n}_{p_z} + \bar{n}_{4s} = 15$, leaving one of these four occupation numbers linearly dependent on the rest.
+Excited states in CuO have heavy orbital relaxation, so including extra hoppings may be useful.
+Therefore we define the following model space $\mathcal{MS}$, from which will we try and select the \textit{best} low-energy model for CuO:
+
+\begin{equation}
+\mathcal{MS} = \{\bar{n}_{4s}, \bar{n}_{p_\pi}, \bar{n}_{p_z}, \sum_{i \in \{xy, xz, ...\}}\vec{S}_{4s}\cdot \vec{S}_{d_i}, n_{4s, \uparrow} n_{4s,\downarrow}\} + \text{P}(\bar{t}_\pi, \bar{t}_{dz}, \bar{t}_{sz}, \bar{t}_{ds})
+\end{equation}
+where P denotes the power set.
+
+After fitting each potential model using ordinary linear regression (OLS) and solving the resultant models using exact diagonalization, we find a set of models which describe the energy functional on our $\mathcal{SS}$ accurately but whose eigenstates and spectra differ as a consequence of intruder states below an energy of 2eV.
+The sixteen different models in $\mathcal{MS}$ all regress with R$^2 >$  0.95.
+We ignore all models which have parameters which are zero within 95\% confidence intervals which we computed through a bootstrap estimate \textbf{ref}.
+Further, any models which have an average errorbar in eigenvalues $>$ 0.25 eV are ignored.
+This leaves us with just six models to further consider: the minimal model (Min), Min + $\bar{t}_\pi$, Min + $\bar{t}_{dz}$, Min + $\bar{t}_\pi, \bar{t}_{ds}$, Min + $\bar{t}_\pi, \bar{t}_{sz}$, Min + $\bar{t}_{ds}, \bar{t}_{dz}$.
+Within the latter five models there are intruder eigenstates, states which lie very far away from our sample set and suffer from large extrapolation errors.
+Intruder states were defined as any eigenstates with energy $< $ 2 eV with a Mahalanobis distance greater than the 90th percentile of all distances.
+The Mahalanobis distance is used in data science for outlier detection \textbf{ref} and tells us how far away an eigenstate is from $\mathcal{SS}$.
+Show in \textbf{Figure ?} are the identified intruder states among the six models above which in aggregate we will call the prior space $\mathcal{PS}$.
+These energies of these eigenstates are not constrained by $\mathcal{SS}$ because of our inability to target certain base states like $c^\dagger_{p_\pi} c_{d_\pi} |GS\rangle$ as discussed before.
+This excitation specifically is within our set of intruder states alongside others like $c^\dagger_{p_\pi} c_{d_{z^2}} |GS\rangle$.
+Other methods like constrained DFT and CASSCF were used to converge these states but we were unsuccessful.
+
+In order to ensure that intruder states are not present within our final model, we enforce a prior that pushes intruder states above a chosen $E_{cut}$ = 2eV by altering the cost function for our regression.
+The choice of prior is built on both experimental knowledge and FN-DMC results.
+From experiment we know that any excitation which de-occupies a d-orbital should be $\sim$ 2 eV in energy.
+In fact all of our intruder states are excitations out of a d-orbital except for the higher energy intruder which is already nearly at 2eV and would not be affected too strongly by this choice of $E_{cut}$.
+While we cannot converge these missing base states using UKS, we can consider singles excitations on the UKS ground state which correspond to these excitations in order to get an upper bound for the FN-DMC energies of our missing base states.
+In FN-DMC the corresponding MO excited states are $> $4eV, and we believe even with orbital relaxation that the converged excited state should be $>$ 2eV in energy.
+The altered cost function takes the form:
+
+\begin{equation}
+\text{Cost} = \sum_{i \in \mathcal{SS}} (E_{eff,i} - E_{ab, i})^2 + \lambda \sum_{p \in \mathcal{PS}} \text{QHL}(2 - E_{eff,p})\ \text{QHL}(x) = \Theta(x)x^2
+\end{equation}
+where $E_{eff}$ is the energy of a state on our effective model, $\lambda>0$ is a parameter which can be varied, and QHL is a quadratic hinge loss with $\Theta$ the Heaviside step function. 
 \section{Discussion}

### 2019-06-07 paper/draft.tex
intro paragraph 1 looks nice!~

@@
 \section{Methods}
-The DMD procedure \textbf{[ref]} allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian under a Born-Oppenheimer approximation:
-
+The DMD procedure allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian:
 \begin{equation}
 H_\text{ab} = -\frac{1}{2} \sum_{i} \nabla_i^2 - \sum_{i,I}\frac{Z}{|r_i - R_I|} + \sum_{i<j}\frac{1}{|r_i - r_j|}
+\label{eq:Hab}
 \end{equation}
-where $i$ indicates electrons and $I$ nuclei. We also treat core electrons using pseudo-potentials. 
-The unit of energy using this Hamiltonian is Hartree (Ha). 
-The goal of DMD is to downfold the \textit{ab-initio} Hamiltonian and Hilbert space onto an effective Hamiltonian acting on a low-energy subspace of the Hilbert space
+where $i$ indicates electrons and $I$ nuclei, and the unit of energy is Hartree (Ha).
+In this paper we will be working under the Born-Oppenheimer approximation and core electrons will be treated using pseudo-potentials.
+The procedure defines a method for downfolding the \textit{ab-initio} energy functional and Hilbert space onto an effective energy functional defined on a low-energy subspace of the Hilbert space 
+\begin{equation}
+(E_\text{ab}, \mathcal{H}) \xrightarrow{\text{DMD}} (E_\text{eff}, \mathcal{LE} \subset \mathcal{H}), \text{ s.t. }
+\forall |\Psi\rangle \in \mathcal{LE}, \ E_\text{eff}[\Psi] - E_\text{ab}[\Psi] = \epsilon[\Psi] + E_0.
+\label{eq:DMD}
+\end{equation} 
+The energy functionals can be written as expectations over Hamiltonian operators $E_\text{ab} = \langle \Psi | H_\text{ab} |\Psi \rangle$, $E_\text{eff} = \langle \Psi | H_\text{eff} |\Psi \rangle$, $\epsilon$ represents the error in our effective theory, and $E_0$ is a constant energy shift.
+Broadly the DMD method consists of four steps which will be discussed in detail later: 
+A) Defining the space of low-energy excitations which $E_\text{eff}$ should be able to describe accurately.
+B) Sampling, at minimum, a set of states in $\mathcal{H}$ which probe the chosen low-energy excitations in a statistically independent manner. The selected states need not be eigenstates. 
+C) Constructing a set of candidate models which are linear in reduced density matrix (RDM) descriptors with variable coefficients $\{c\}$
+\begin{equation}
+E_\text{eff} = \sum_k c_k d_k[\Psi]\ + E_0,\ d_k[\Psi] = \langle \Psi | \hat{d}_k |\Psi \rangle.
+\label{eq:Eeff}
+\end{equation}
+Here $\hat{d}_k$ are Hermitian operators typically composed of 1- or 2-RDM elements. 
+Examples of possible $\hat{d}_k$ are number operators $\hat{n}$ and exchange operators $\vec{S}_i \cdot \vec{S}_j$.
+Additionally, a single particle basis must be built to express RDM elements on and should be chosen such that variations among states in $\mathcal{LE}$ are mostly described by variations in the projection of these states onto the basis.
+D) Using the samples to fit the coefficients $\{c\}$ by linear regression such that $E_\text{eff}$ satisfies the conditions in \eqref{eq:DMD} with the smallest error $\epsilon$ possible. 
+The fitting procedure is typically an ordinary linear regression, however, one may use a custom cost function in the regression as well. 
+In order to conduct the linear regression for a functional like \eqref{eq:Eeff}, one needs to calculate for each state sampled from $\mathcal{LE}$ the expectation values of $H_\text{ab}$ and every descriptor $\{\hat{d}_k\}$ used in the regression.
+In principle, if conducted with no approximations, the DMD method is rigorously guaranteed to obtain exact results, namely $\epsilon[\Psi] = 0$.
 
-\begin{equation}
-(H_\text{ab}, \mathcal{H}) \xrightarrow{\text{DMD}} (H_\text{eff}, \mathcal{LE} \subset \mathcal{H}) \text{ so that }
-\forall |\Psi\rangle \in \mathcal{LE}, \ \langle \Psi | H_\text{ab} | \Psi\rangle = \langle \Psi | H_\text{eff} | \Psi\rangle
-\end{equation} 
-Broadly the DMD method consists of four steps which will be discussed in detail later: 1) Selecting a low-energy subspace $\mathcal{LE}$ which includes all excitations one wants to describe accurately.
-In theory $\mathcal{LE}$ would be chosen to be the subspace spanned by the N lowest-energy eigenstates of $H_\text{ab}$, but is constructed more approximately in practice.  
-2) Generate a set of samples within our low-energy space $\mathcal{SS} \in \mathcal{LE}$. 
-The choice of sampling scheme may be system dependent. 
-We will discuss a shell-sampling scheme in this paper. 
-It is important to note that one does not need to have access to the eigenstates of $H_\text{ab}$ in order to sample a chosen $\mathcal{LE}$, nor are the eigenstates required to be in the sample set.
-3) Parameterizing $H_\text{eff}$ as a linear combination of descriptors, 
-\begin{equation}
-H_\text{eff} = \sum_k a_k \hat{d}_k
-\end{equation}
-where $\hat{d}_k$ are typically 1- or 2-body reduced density matrix (RDM) elements which can represent single- or two-particle terms in an effective theory.
-4) Using the samples to fit the coefficients $\{c_k\}$ such that $H_\text{eff}$ satisfies the conditions in equation (2) as well as possible. 
-The fitting procedure is typically an ordinary linear regression, however one may use a custom cost function in the regression as well. 
-Therefore the DMD procedure allows us to map the problem of downfolding strongly correlated electrons systems onto a linear regression problem which can then be systematically studied using tools developed in data science and statistics.
+\pagebreak
+peepoo
+
+\pagebreak
 

### 2019-06-07 paper/draft.tex
methods DMD and FNDMC done

@@
 \section{Methods}
+\subsection{Density Matrix Downfolding (DMD)}
 The DMD procedure allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian:
@@
 
-\pagebreak
-peepoo
+\subsection{Fixed-node diffusion Monte Carlo (FN-DMC)}
+When downfolding $H_\text{ab}$ we will use FN-DMC to access states in $\mathcal{LE}$ and accurately calculate their \textit{ab-initio} energies and RDM elements.
+Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a Hamiltonian given some initial trial wave function.
+Consider a trial wave function $|\psi_T\rangle$ and the Hamiltonian $H_\text{ab}$ with ground state $|\phi_0\rangle$.
+We apply the projector $e^{-\tau H_\text{ab}}$ as $\tau \rightarrow \infty$ to $|\psi_T \rangle$
+\begin{equation}
+\lim_{\tau \rightarrow \infty} e^{-\tau H_\text{ab}} |\psi_T\rangle 
+\equiv \lim_{\tau \rightarrow \infty} |\psi_\text{DMC}(\tau)\rangle \propto \langle \phi_0|\psi_T\rangle |\phi_0\rangle,
+\end{equation}
+projecting out the ground state as long as the trial wave function we choose is not orthogonal to the ground state. 
+The stochastic implementation involves moving samples from the trial function $\psi_T(R)$ using the Green function $G(R, R^\prime, \tau) = \langle R | e^{-\tau(H_\text{ab} - E_T)} | R^\prime \rangle$.
+Since $H_\text{ab} = T + V$, kinetic and potential energy terms, the Green function is approximated by a Trotter expansion $G(R, R^\prime, \tau) = \langle R | e^{-\tau(H - E_T)} | R^\prime \rangle \sim \Big[e^{-d\tau(V(R) + V(R^\prime))/2} \langle R| e^{-d\tau(T - E_T)}|R^\prime \rangle + O(d\tau^2) \Big]^N $ where $d\tau = \tau/N$.
+This expansion can be interpreted as an interative procedure where samples are moved N times with a small timestep $d\tau$ until convergence.
+The constant $E_T$ is a trial energy used to control the normalization of $\psi_\text{DMC}(\tau, R)$ and is updated at each move.
+This implementation, however, suffers from a fermion sign problem. 
+We deal with this sign problem through a fixed-node approximation, where the nodal surface of $\psi_\text{DMC}(\tau, R)$ is forced to match that of the initial trial wave function for all $\tau$.
+This approximation makes FN-DMC variational, and will only return the exact ground state of $H_\text{ab}$ if the nodal surfaces of $|\psi_T\rangle$ and $|\phi_0\rangle$ are identical.
+We make use of this variational principle to access low-energy states within $\mathcal{H}$ by choosing trial wave functions with nodes that differ from the nodes of $|\phi_0 \rangle$.
+To calculate the expectation value of an operator $\hat{O}$ in FN-DMC we will use a mixed estimator $\langle \psi_{DMC}(\tau) |\hat{O} | \psi_T \rangle/\langle \psi_\text{DMC}(\tau) | \psi_T \rangle$ which allows us to use the importance sampled distribution $f = \psi_\text{DMC}(\tau)\psi_T$ for our Monte Carlo estimates.
+Details for calculating reduced density matrix elements in FN-DMC can be found in Wagner.
 
 \pagebreak
-
+\subsection{Defining $\mathcal{LE}$ for CuO molecule}
 Based on anion photoelectron spectroscopy (APES) experiments\textbf{[ref]} on the CuO molecule we define our low-energy space $\mathcal{LE}$ as the space of states with 9 to 10 electrons in the Cu 3d orbitals.
@@
 Our particular focus will be on describing most accurately the properties and energies of eigenstates up to 2eV, as higher energy states form a nearly continuous block of states which include vibrational modes.
+
+\pagebreak
 

### 2019-06-07 paper/draft.tex
writing methods almost done, just need to introduce the prior stuff. figures update

--- 2019-06-07 paper/draft.tex
@@
 \usepackage{mathtools}
+\usepackage{wrapfig}
 
@@
 \section{Methods}
+\subsection{Density Matrix Downfolding (DMD)}
 The DMD procedure allows us to develop low-energy effective theories for physical systems in a systematic manner beginning with the \textit{ab-initio} Hamiltonian:
 \begin{equation}
-H_\text{ab} = -\frac{1}{2} \sum_{i} \nabla_i^2 - \sum_{i,I}\frac{Z}{|r_i - R_I|} + \sum_{i<j}\frac{1}{|r_i - r_j|}
+\hat{H}_\text{ab} = -\frac{1}{2} \sum_{i} \nabla_i^2 - \sum_{i,I}\frac{Z}{|r_i - R_I|} + \sum_{i<j}\frac{1}{|r_i - r_j|}
 \label{eq:Hab}
@@
 \end{equation} 
-The energy functionals can be written as expectations over Hamiltonian operators $E_\text{ab} = \langle \Psi | H_\text{ab} |\Psi \rangle$, $E_\text{eff} = \langle \Psi | H_\text{eff} |\Psi \rangle$, $\epsilon$ represents the error in our effective theory, and $E_0$ is a constant energy shift.
+The energy functionals can be written as expectations over Hamiltonian operators $E_\text{ab} = \langle \Psi | \hat{H}_\text{ab} |\Psi \rangle$, $E_\text{eff} = \langle \Psi | \hat{H}_\text{eff} |\Psi \rangle$, $\epsilon$ represents the error in our effective theory, and $E_0$ is a constant energy shift.
 Broadly the DMD method consists of four steps which will be discussed in detail later: 
@@
 \begin{equation}
-E_\text{eff} = \sum_k c_k d_k[\Psi]\ + E_0,\ d_k[\Psi] = \langle \Psi | \hat{d}_k |\Psi \rangle.
+E_\text{eff} = \sum_k c_k \langle \Psi | \hat{d}_k |\Psi \rangle + E_0.
 \label{eq:Eeff}
@@
 Here $\hat{d}_k$ are Hermitian operators typically composed of 1- or 2-RDM elements. 
-Examples of possible $\hat{d}_k$ are number operators $\hat{n}$ and exchange operators $\vec{S}_i \cdot \vec{S}_j$.
+Examples of possible $\hat{d}_k$ are number operators $\hat{n}_i$ and exchange operators $\vec{S}_i \cdot \vec{S}_j$.
 Additionally, a single particle basis must be built to express RDM elements on and should be chosen such that variations among states in $\mathcal{LE}$ are mostly described by variations in the projection of these states onto the basis.
@@
 The fitting procedure is typically an ordinary linear regression, however, one may use a custom cost function in the regression as well. 
-In order to conduct the linear regression for a functional like \eqref{eq:Eeff}, one needs to calculate for each state sampled from $\mathcal{LE}$ the expectation values of $H_\text{ab}$ and every descriptor $\{\hat{d}_k\}$ used in the regression.
+In order to conduct the linear regression for a functional like \eqref{eq:Eeff}, one needs to calculate for each state sampled from $\mathcal{LE}$ the expectation values of $\hat{H}_\text{ab}$ and every descriptor $\{\hat{d}_k\}$ used in the regression.
 In principle, if conducted with no approximations, the DMD method is rigorously guaranteed to obtain exact results, namely $\epsilon[\Psi] = 0$.
 
-\pagebreak
-peepoo
+\subsection{Fixed-node diffusion Monte Carlo (FN-DMC)}
+When downfolding $\hat{H}_\text{ab}$ we will use FN-DMC to access states in $\mathcal{LE}$ and accurately calculate their \textit{ab-initio} energies and RDM elements.
+Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a Hamiltonian given some initial trial wave function.
+Consider a trial wave function $|\Psi_T\rangle$ and the Hamiltonian $\hat{H}_\text{ab}$ with ground state $|\Phi_0\rangle$.
+We apply the projector $e^{-\tau \hat{H}_\text{ab}}$ as $\tau \rightarrow \infty$ to $|\Psi_T \rangle$
+\begin{equation}
+\lim_{\tau \rightarrow \infty} e^{-\tau \hat{H}_\text{ab}} |\Psi_T\rangle 
+\equiv \lim_{\tau \rightarrow \infty} |\Psi_\text{DMC}(\tau)\rangle \propto \langle \Phi_0|\Psi_T\rangle |\Phi_0\rangle,
+\end{equation}
+projecting out the ground state as long as the trial wave function we choose is not orthogonal to the ground state. 
+The stochastic implementation involves moving samples from the trial function $\Psi_T(R)$ using the Green function $G(R, R^\prime, \tau) = \langle R | e^{-\tau(\hat{H}_\text{ab} - E_T)} | R^\prime \rangle$.
+Since $H_\text{ab} = T + V$, kinetic and potential energy terms, the Green function is approximated by a Trotter expansion $G(R, R^\prime, \tau) = \langle R | e^{-\tau(\hat{H} - E_T)} | R^\prime \rangle \sim \Big[e^{-d\tau(V(R) + V(R^\prime))/2} \langle R| e^{-d\tau(\hat{T} - E_T)}|R^\prime \rangle + O(d\tau^2) \Big]^N $ where $d\tau = \tau/N$.
+This expansion can be interpreted as an interative procedure where samples are moved N times with a small timestep $d\tau$ until convergence.
+The constant $E_T$ is a trial energy used to control the normalization of $\Psi_\text{DMC}(\tau, R)$ and is updated at each move.
+This implementation, however, suffers from a fermion sign problem. 
+We deal with this sign problem through a fixed-node approximation, where the nodal surface of $\Psi_\text{DMC}(\tau, R)$ is forced to match that of the initial trial wave function for all $\tau$.
+This approximation makes FN-DMC variational, and will only return the exact ground state of $H_\text{ab}$ if the nodal surfaces of $|\Psi_T\rangle$ and $|\Phi_0\rangle$ are identical.
+We make use of this variational principle to access low-energy states within $\mathcal{H}$ by choosing trial wave functions with nodes that differ from the nodes of $|\Phi_0 \rangle$.
+To calculate the expectation value of an operator $\hat{A}$ in FN-DMC we will use a mixed estimator $\langle \Psi_{DMC}(\tau) |\hat{A} | \Psi_T \rangle/\langle \Psi_\text{DMC}(\tau) | \Psi_T \rangle$ which allows us to use the importance sampled distribution $f = \Psi_\text{DMC}(\tau)\Psi_T$ for our Monte Carlo estimates.
+Details for calculating reduced density matrix elements in FN-DMC can be found in Wagner.
+
+\subsection{Defining $\mathcal{LE}$ for CuO molecule}
+We construct our $\mathcal{LE}$ based on recent anion photoelectron spectroscopy (APES) measurements of the low-lying excited states of the nuetral CuO molecule. 
+The lowest energy excitations measured, which lie below 2eV, involve primarily the O 2p$_z$, 2p$_\pi$ and Cu 4s orbitals, which are fully-filled, half-filled and empty in the ground state respectively.
+Beginning at 2.2 eV are excitations which remove a single electron from the fully filled Cu 3d shell and add them to either the O 2p$_\pi$ or Cu 4s orbitals.
+Seeing that the lowest energy excitations of the CuO molecule involve removing at most one electron from the Cu 3d shell, we define our low-energy space as
+\begin{equation}
+\mathcal{LE} = \text{Span(}\{ |\Psi \rangle | \langle \Psi | \hat{n}_{3d} | \Psi \rangle \ge 9,\ \hat{H}_\text{ab}|\Psi\rangle = E |\Psi\rangle \}\text{)}.
+\label{eq:LE}
+\end{equation}
+Our particular focus will be on describing most accurately the properties and energies of eigenstates up to $\sim$2eV, as measurements on higher energy states observe a nearly continuous block of states which include vibrational modes.
+
+\subsection{Sampling $\mathcal{LE}$}
+Our sample space was generated by using multi-Slater-Jastrow trial wavefunctions in FN-DMC. 
+In principle we could probe every low-energy excitation in $\mathcal{LE}$ in a statistically independent manner by just sampling the eigenstates within $\mathcal{LE}$ and including various non-eigenstates within $\mathcal{LE}$ as well to ensure robust statistics.
+In practice we do not have access to these eigenstates and approximate methods are required to sample the low-energy space. 
+Consider a trial wavefunction of the form $e^{J_i} |\text{D}_i\rangle$, where $e^{J_i}$ is a three-body Jastrow factor and $|\text{D}_i\rangle$ is a determinant of some single particle orbitals.
+If the nodes of $|\text{D}_i\rangle$ are similar to the nodes of an eigenstate $|\Phi_i\rangle \in \mathcal{LE}$, then the properties and energy calculated from FN-DMC using this trial wavefunction will approximate those of the eigenstate, with the degree of approximation depending on the quality of the trial function nodal structure.
+If we were able to find for each $|\Phi_i \rangle \in \mathcal{LE}$ such a $|\text{D}_i\rangle$ then we can approximate any state in $\mathcal{LE}$ as
+\begin{equation}
+|\Psi\rangle = \sum_i c_i |\Phi_i\rangle \sim \sum_i c_i \lim_{\tau \rightarrow \infty} e^{-\tau \hat{H}_\text{ab}} (e^{J_i} |D_i\rangle) \xrightarrow{J_i = J} \lim_{\tau \rightarrow \infty} e^{-\tau \hat{H}_\text{ab}} (e^{J}\sum_{i} c_i|\text{D}_i\rangle).
+\label{eq:sampling}
+\end{equation}
+The last equality is valid if $\forall i\  J_i = J$, allowing us to map $|\Psi \rangle \in \mathcal{LE}$ to the end result of an FN-DMC calculation using a multi-Slater-Jastrow trial wavefunction.
+We use symmetry-targeted unrestricted Kohn-Sham (UKS) to generate our determinants $|\text{D}_i\rangle$ using a B3LYP functional, which has been shown to accurately reproduce ground state nodal properties of transition-metal oxide molecules, a Trail-Needs pseudopotential, and the VTZ Trail-Needs basis using the package PySCF.
+The symmetry-targeted UKS method allows us to fix the total spin projection S$_z$ and the total number of electrons in a particular irreducible representation (irrep) of the symmetry group under use, $\text{A},\ \text{E}_\text{1x},\ \text{E}_\text{2y}$ etc.
+This method allows us to access almost every excitation in $\mathcal{LE}$, however, there are some cases of two or more low-energy states within $\mathcal{LE}$ which have identical S$_z$ and number of electrons per irrep.
+An example of this dilemma would be the ground state and the state with an excitation from Cu 3d$_{xz} \rightarrow $  O 2p$_x$.
+In these few cases the higher energy excited $|\text{D}_i\rangle$ is inaccessible and the corresponding $|\Phi_i\rangle$ is excluded from the sum in \eqref{eq:sampling}, restricting our sample space to a subspace of $\mathcal{LE}$.
+Methods like constrained DFT also failed to converge the inaccessible $|\text{D}_i\rangle$.
+We will discuss the consequences of this restriction later on.
+A single three-body Jastrow factor $J$ was used for every $|\text{D}_i\rangle$ and was optimized on the lowest energy UKS state using a linear energy optimization method.
+The FN-DMC calculations were conducted with T-moves, to make the calculation variational while using pseudopotentials, with a timestep of $\tau = 0.01$.
+The coefficients $\{c_j\}$ for our sample states were chosen via a shell-sampling method. 
+We begin by fixing the coefficient $c_0 = \sqrt{w}$ where $w \in \{1.0, 0.8, ..., 0.2\}$. 
+For each choice of $w$ we sample n = 5 states by randomly selecting the unassigned coefficients from a uniform distribution such that $\sum_i c_i^2 = 1$. 
+This procedure generates shells of samples at decreasing distance from the eigenstate $|\Phi_0\rangle$. 
+We can then loop over all $i$ to generate shells near each eigenstate.
+This sampling scheme tends to be sparse where the density of states of $\hat{H}_\text{ab}$ is low and therefore extra samples are generated in regions of sparse sample density \textit{post-hoc}.
+
+\subsection{Constructing candidate models}
+Parameterizing our effective model requires constructing a basis on which to calculate our \textit{ab-initio} 1-/2-RDM elements and selecting a set of descriptors from which we would like to build our model.
+As discussed, the lowest energy excitations in the CuO molecule are between the Cu 3d, 4s and O 2p orbitals, meaning that our basis needs to span these orbitals. 
+We constructed two such bases: a localized intrinsic atomic orbital (IAO) basis and a molecular orbital (MO) basis.
+The IAO basis was built on all Cu 3d, 4s and O 2p molecular orbitals from the $|\text{D}_i\rangle$ used to construct our sample states.
+The MO basis consists of the Cu 3d, 4s and O 2p molecular orbitals from the lowest energy restricted open-shell Kohn-Sham (ROKS) solution with $x \leftrightarrow y$ spatial symmetry, a O 2p$_z \rightarrow$ O 2p$_\pi$ excitation.
+As these two bases are used to describe the same space, they are related by an orthogonal transformation which will allow us to map between them if necessary.
+This choice for the MO basis ensures that our basis elements are spin-independent and respect the spatial symmetries of the molecule.
+In order to describe the low-energy degrees of freedom in the CuO molecule our model will require occupation energies and hybridizations between the Cu 3d, 4s and O 2p atomic orbitals.
+A sparser representation can be found using a MO basis, since occupation operators in the MO basis contain information on both occupation and hybridization in an atomic basis. 
+The lack of doubly occupied Cu 4s states in the low-energy spectrum of CuO indicate the necessity of a Hubbard U term on the Cu 4s.
+This is corroborated by the fact that the FN-DMC energy of the lowest-lying sampled state with a doubly occupied Cu 4s orbital is 7 eV above the lowest energy sampled state.
+Further, we include a Hund's coupling between the Cu 4s and Cu 3d orbitals in our model based on the existence of a similar Hund's coupling 
+for the copper atom.
+These two interaction terms are best represented in the IAO basis as they are intuitively interactions between localized orbitals.
+In addition to these important parameters, we will consider models which contain any number of hybridizations between the MOs to account for orbital relaxation between excited states in the CuO molecule.
+In total our space of canditate models is then 
+\begin{equation}
+\begin{split}
+\{\bar{n}_{4s}, \bar{n}_{p_\pi}, \bar{n}_{p_z}, \hat{n}_{4s\uparrow} \hat{n}_{4s\downarrow},\sum_{i \in \{xy, xz, ...\}}\vec{S}_{4s}\cdot \vec{S}_{d_i}\} \ + \\
+\text{P}(\bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi} + h.c.,\ \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z} + h.c.,\ \bar{c}_{4s}^\dagger \bar{c}_{p_z} + h.c.,\ \bar{c}_{d_z^2}^\dagger \bar{c}_{4s} + h.c.)
+\end{split}
+\label{eq:models}
+\end{equation}
+where P denotes the power set and operators are defined on the IAO basis unless denoted by a bar, in which case the operator is built on the MO basis.
+The coefficients for each term above will be denoted $\bar{\epsilon}_{4s},\ \bar{\epsilon}_{p_\pi},\ \bar{\epsilon}_{p_z},\ U_s,\ J_{sd},\ \bar{t}_\pi,\ \bar{t}_{dz},\ \bar{t}_{sz},\ \bar{t}_{ds}$.
+The operator $\bar{n}_{3d}$ is not included in any models as it is linearly dependent on all other occupation energies through the relationship $\bar{n}_{3d} + \bar{n}_{p_z} + \bar{n}_{p_\pi} + \bar{n}_{4s} = N_\text{elec} = \text{15}$.
+The symbol $\pi$ denotes a contraction over $x, y$ for p orbitals and $xz,\ yz$ for d orbitals.
+The symbol $\delta$, introduced later, denotes a contraction over $xy,\ x^2-y^2$ for d orbitals.
 
 \pagebreak
+\subsection{Fitting candidate models}
+After fitting each of the potential models in \eqref{eq:models} using ordinary linear regression (OLS) and solving the resultant models using exact diagonalization, we find a set of models which describe the energy functional on our sample set accurately but whose eigenstates and spectra differ as a consequence of intruder states below an energy of 2eV.
+The sixteen different models all regress with R$^2 >$ 0.95 on our sample data, however some models are more robust than others. 
+Models which have coefficients that are zero within 95\% confidence intervals, computed through bootstrap estimates, are removed from consideration.
+We then take the left over models, rotate every operator and coefficient into the IAO basis through an appropriate orthogonal transformation, and exactly diagonalize the models.
+Any models which have an average errorbar in eigenvalues, also estimated by bootstrapping, greater than 0.25 eV are ignored.
+Each of the remaining six models describe our sample set accurately, have robust non-zero coefficients, and have small error bars in eigenvalues.
+However, the eigenstates below 2eV differ greatly between these models as illustrated in Figure \ref{fig:Intruder}.
 
-Based on anion photoelectron spectroscopy (APES) experiments\textbf{[ref]} on the CuO molecule we define our low-energy space $\mathcal{LE}$ as the space of states with 9 to 10 electrons in the Cu 3d orbitals.
-Mathematically we can express this space as the span of some eigenstates within our Hilbert space
-\begin{equation}
-\mathcal{LE} = \text{Span(}\{ |\Psi \rangle | \langle \Psi | n_{3d} | \Psi \rangle \ge 9,\ H|\Psi\rangle = E |\Psi\rangle \}\text{)}.
-\end{equation}
-The APES measurements indicate that the lowest energy excitations in the CuO molecule are between the O p-orbitals and Cu 4s orbitals, leaving around 10 electrons in the Cu 3d orbitals. 
-Bonding between the O p and Cu 3d orbitals lead to significant variations in the Cu 3d occupation, indicating the importance of including excitations out of the Cu 3d orbitals. 
-This is corroborated by APES measurements indicating that the lowest energy eigenstates with 9 electrons in the Cu 3d orbitals are only $\sim$ 0.2 eV higher in energy than the second excited state of the system with 10 electrons in the Cu 3d orbitals.
-Our particular focus will be on describing most accurately the properties and energies of eigenstates up to 2eV, as higher energy states form a nearly continuous block of states which include vibrational modes.
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/init_ed.pdf}
+\caption{Results of exact diagonalization showing the energies and properties of the first twenty eigenstates for three candidate models.
+The ground state and first excited state are colored and have enlarged markers for clarity.}
+\label{fig:Intruder}
+\end{figure}
+\pagebreak
 
-Our sample space $\mathcal{SS}$ was generated by sampling the span of base states - states which approximately describe true eigenstates within the $\mathcal{LE}$ - using multi-Slater-Jastrow trial wave functions in fixed-node Diffusion Monte Carlo (FN-DMC).
-In principle we could sample $\mathcal{LE}$ by taking linear combinations of the eigenvectors which span it.
-In practice we do not have access to these eigenvectors and approximate methods are required to sample the low-energy space.
-We consider wave functions of the following form:
-\begin{equation}
-\lim_{\tau \rightarrow \infty} e^{-\tau H_\text{ab}} (e^{J}\sum_{i} c_i|\text{D}_i\rangle) = \sum_i c_i \lim_{\tau \rightarrow \infty} e^{-\tau H_\text{ab}} (e^J |D_i\rangle) \equiv \sum_i c_i |\Phi_i\rangle .
-\end{equation}
-where $|D_i\rangle$ is a determinant of single particle orbitals, $e^J$ is a three-body Jastrow function in \textbf{ref}, and $e^{-\tau H_\text{ab}}$ is a projection operator which exponentially suppresses high-energy contributions to the wave function and is realized through an FN-DMC calculation.
-This state is an accurate approximation to a state $|\Psi\rangle \in \mathcal{LE}$ of the form $|\Psi \rangle = \sum_i c_i |\Psi_i\rangle$, where $|\Psi_i\rangle$ is an eigenstate within $\mathcal{LE}$, if $\forall i\ |\Phi_i\rangle \sim |\Psi_i\rangle$.
-While $|\Psi_i\rangle$ are eigenstates of $H_\text{ab}$, $|\Phi_i\rangle$ generally are not, but do form the basis for our sample space and will be called \textit{base states}.
-The fixed-node projection can achieve this similarity if the nodes of $|D_i\rangle$ accurately approximate those of $|\Psi_i\rangle $.
-We use symmetry-targeted unrestricted Kohn-Sham (UKS) to generate our determinants $|D_i\rangle$ using a Trail-Needs pseudopotential, VTZ Trail-Needs basis \textbf{ref}, and a B3LYP functional \textbf{ref}, which has been shown to accurately reproduce nodal properties of transition-metal oxide molecules \textbf{ref}.
-These calculations were carried out in the package PySCF \textbf{ref}.
-The symmetry-targeted UKS method allows us to fix the total spin projection S$_z$ and the total number of electrons in a particular irreducible representation (irrep) of the symmetry group under use, $\text{A},\ \text{E}_\text{1x},\ \text{E}_\text{2y}$ etc.
-There are some cases of two or more base states which have identical S$_z$ and number of electrons per irrep.
-within  $\mathcal{LE}$, for example the ground state and the excited state with excitation $c^\dagger_{p_\pi} c_{d_\pi} |GS\rangle$.
-In this scenario the higher energy excitations are inaccessible and excluded from our sample set.
-We will discuss the consequences of this exclusion later on.
-The three-body Jastrow factor was optimized on the lowest energy UKS state using a linear energy optimization methods \textbf{ref}.
-The FN-DMC was conducted with T-moves \textbf{ref} to make the calculation variational while using pseudopotentials with a timestep of $\tau = 0.01$.
-Necessary 1- and 2-RDM elements were also calculated in FN-DMC using a mixed estimator \textbf{ref}.
-The coefficients $\{c_j\}$ were chosen via a shell-sampling method.
-For each base state $|\Phi_i\rangle$ we fix the coefficient $c_i = \sqrt{w},\ w \in \{0.2, 0.4, ..., 1.0\}$ and for each $w$ sample N = 5 states uniformly such that $\sum_j c_j^2 = 1$.
-Looping over $i$ yields shells of samples centered on each base state.
-This sampling scheme tends to be sparse where the density of states of $H_\text{ab}$ is low and therefore extra samples are generated in regions of sparse sample density \textit{post-hoc}.
-This sampling scheme therefore generates a sample set which can be defined as
-\begin{equation}
-\mathcal{SS} \in \text{Span(}\{ |\Phi \rangle | \langle \Phi | n_{3d} | \Psi \rangle \ge 9,\ H|\Phi\rangle = E |\Phi\rangle \}\text{)} \sim \mathcal{LE}.
-\end{equation}
-where $|\Phi\rangle$ is defined in (5), and which maps exactly onto the true $\mathcal{LE}$ if our base states exactly match the true eigenstates of $H_\text{ab}$.
-
-Parameterizing our effective model requires constructing a basis on which to calculate our \textit{ab-initio} 1-/2-RDM elements and selecting a set of descriptors from which we would like to build our model.
-We constructed two bases for our model Hamiltonian, a localized intrinsic atomic orbital (IAO) basis for evaluating two-body reduced density matrix (2-rdm) elements, and a molecular orbital (MO) basis for one-body reduced density matrix (1-rdm) elements.
-The two-body interactions we are interested in are typically local interactions, for example a Hubbard-U, Hund's-J or superexchange-J, therefore motivating a local basis for the two-body terms.
-In the CuO molecule there is heavy hybridization between the Cu d and O p orbitals, and an MO basis can compactly represent this hybridization, leading us to use MO basis elements for our one-body basis elements.
-Based on experimental measurements and the structure of the data within our $\mathcal{SS}$, the lowest energy excitations of the CuO molecule have excitations between Cu d, O p and Cu 4s orbitals.
-APES measurements do not see any 4s$^2$ states in the low-energy spectra which is corroborated by our FN-DMC energy for the lowest energy base state with a Cu 4s$^2$ occupation is $\sim$ 7 eV above the lowest energy base state.
-Including the $\sim$ 0.5eV Hund's coupling on the copper atom, we believe that a minimal model for our downfolding must contain: $\bar{n}_{4s}, \bar{n}_{p_\pi}, \bar{n}_{p_z}, \sum_{i \in \{xy, xz, ...\}}\vec{S}_{4s}\cdot \vec{S}_{d_i}, n_{4s, \uparrow} n_{4s,\downarrow}$.
-The barred terms are built on the MO basis, and the non-barred ones on the IAO basis.
-The exclusion of $n_{3d}$ from our minimal model is because of the total number of electrons being constrainted by $\bar{n}_{3d} + \bar{n}_{p_\pi} + \bar{n}_{p_z} + \bar{n}_{4s} = 15$, leaving one of these four occupation numbers linearly dependent on the rest.
-Excited states in CuO have heavy orbital relaxation, so including extra hoppings may be useful.
-Therefore we define the following model space $\mathcal{MS}$, from which will we try and select the \textit{best} low-energy model for CuO:
-
-\begin{equation}
-\mathcal{MS} = \{\bar{n}_{4s}, \bar{n}_{p_\pi}, \bar{n}_{p_z}, \sum_{i \in \{xy, xz, ...\}}\vec{S}_{4s}\cdot \vec{S}_{d_i}, n_{4s, \uparrow} n_{4s,\downarrow}\} + \text{P}(\bar{t}_\pi, \bar{t}_{dz}, \bar{t}_{sz}, \bar{t}_{ds})
-\end{equation}
-where P denotes the power set.
-
-After fitting each potential model using ordinary linear regression (OLS) and solving the resultant models using exact diagonalization, we find a set of models which describe the energy functional on our $\mathcal{SS}$ accurately but whose eigenstates and spectra differ as a consequence of intruder states below an energy of 2eV.
-The sixteen different models in $\mathcal{MS}$ all regress with R$^2 >$  0.95.
-We ignore all models which have parameters which are zero within 95\% confidence intervals which we computed through a bootstrap estimate \textbf{ref}.
-Further, any models which have an average errorbar in eigenvalues $>$ 0.25 eV are ignored.
-This leaves us with just six models to further consider: the minimal model (Min), Min + $\bar{t}_\pi$, Min + $\bar{t}_{dz}$, Min + $\bar{t}_\pi, \bar{t}_{ds}$, Min + $\bar{t}_\pi, \bar{t}_{sz}$, Min + $\bar{t}_{ds}, \bar{t}_{dz}$.
+the minimal model (Min), Min + $\bar{t}_\pi$, Min + $\bar{t}_{dz}$, Min + $\bar{t}_\pi, \bar{t}_{ds}$, Min + $\bar{t}_\pi, \bar{t}_{sz}$, Min + $\bar{t}_{ds}, \bar{t}_{dz}$.
 Within the latter five models there are intruder eigenstates, states which lie very far away from our sample set and suffer from large extrapolation errors.

### 2019-06-07 qwalk/old/ub3lyp_s1_/analyzedmc.py

@@ -661,12 +661,15 @@ def comb_plot_ed_small(full_df,av_df,models,fname=None,title=None,cutoff=0):
   rgba_color = plt.cm.Blues(norm(1.75))
   rgba_color2 = plt.cm.Oranges(norm(1.75))
   fig, axes = plt.subplots(nrows=2,ncols=3,sharey=True,figsize=(6,6))
-  xlabels = [r'n$_{d_{z^2}}$',r'n$_{d_{\pi}}$',r'n$_{d_{\delta}}$',
-  r'n$_{z}$',r'n$_{\pi}$',r'n$_{s}$']
+  xlabels = [r'$\langle n_{d_{z^2}} \rangle$',r'$\langle n_{d_{\pi}}\rangle$',
+  r'$\langle n_{d_{\delta}}\rangle$',r'$\langle n_{z}\rangle$',r'$\langle n_{\pi}\rangle$'
+  ,r'$\langle n_{s} \rangle$']
   
-  labels={5:r'Min',9:r'Min$ + \bar{t}_\pi$',
-  12:r'Min$ + \bar{t}_{dz}$',20:r'Min$ + \bar{t}_\pi, \bar{t}_{sz}$',
-  21:r'Min$ + \bar{t}_\pi, \bar{t}_{ds}$',24:r'Min$ + \bar{t}_{ds}, \bar{t}_{dz}$'}
+  labels={5:r'Min',9:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$',
+  12:r'Min$ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$',
+  20:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$',
+  21:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
+  24:r'Min$ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$'}
 
   markers = ['s','o','^']
 
@@ -739,8 +742,9 @@ def plot_ed_outliers(full_df,out_df,av_df,fname=None):
   rgba_color2 = plt.cm.Oranges(norm(1.75))
[…]

### 2019-06-07 qwalk/old/ub3lyp_s1_/analyzeprior.py

@@ -169,17 +169,17 @@ def plot_prior():
   plt.ylabel(r'R$^2$')
 
   #Lambda vs score
-  labels=[r'Min',r'Min$ + \bar{t}_\pi$',
-  r'Min$ + \bar{t}_{dz}$',r'Min$ + \bar{t}_\pi, \bar{t}_{sz}$',
-  r'Min$ + \bar{t}_\pi, \bar{t}_{ds}$',r'Min$ + \bar{t}_{ds}, \bar{t}_{dz}$']
+  labels={5:r'Min',9:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$',
+  12:r'Min$ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$',
+  20:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$',
+  21:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
+  24:r'Min$ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$'}
   plt.subplot(212)
-  z=0
   for group_model in prior_df.groupby(by='model'):        
     score_u = group_model[1]['score_u'] - group_model[1]['score']
     score_d = group_model[1]['score'] - group_model[1]['score_d']
     plt.errorbar(group_model[1]['lam'],group_model[1]['score'],
-    yerr=[score_d,score_u],marker='o',ls='None',label=labels[z])
-    z+=1
+    yerr=[score_d,score_u],marker='o',ls='None',label=labels[group_model[0]])
   plt.legend(loc='best')
   plt.xticks(np.arange(0,24,4))
   plt.ylabel(r'QHL (eV$^2$)')
@@ -354,8 +354,8 @@ def analyze(df=None,save=False):
   #Generate models and plot cost 
   #prior_df = prior_analysis(df,cutoff=cutoff)
   #prior_df.to_pickle('analysis/prior.pickle')
-  #plot_prior()
-  #exit(0)
+  plot_prior()
+  exit(0)
 
   #ED for models
   '''
@@ -369,7 +369,6 @@ def analyze(df=None,save=False):
   exit(0)
   '''
 
-  '''
[…]

### 2019-06-08 paper/draft.tex
finished methods

@@
 We deal with this sign problem through a fixed-node approximation, where the nodal surface of $\Psi_\text{DMC}(\tau, R)$ is forced to match that of the initial trial wave function for all $\tau$.
-This approximation makes FN-DMC variational, and will only return the exact ground state of $H_\text{ab}$ if the nodal surfaces of $|\Psi_T\rangle$ and $|\Phi_0\rangle$ are identical.
+This approximation makes FN-DMC variational, and will only return the exact ground state of $\hat{H}_\text{ab}$ if the nodal surfaces of $|\Psi_T\rangle$ and $|\Phi_0\rangle$ are identical.
 We make use of this variational principle to access low-energy states within $\mathcal{H}$ by choosing trial wave functions with nodes that differ from the nodes of $|\Phi_0 \rangle$.
@@
 Each of the remaining six models describe our sample set accurately, have robust non-zero coefficients, and have small error bars in eigenvalues.
-However, the eigenstates below 2eV differ greatly between these models as illustrated in Figure \ref{fig:Intruder}.
+However, the eigenstates below 2eV differ greatly between these models as illustrated in Figure \ref{fig:InitED}.
 
@@
 The ground state and first excited state are colored and have enlarged markers for clarity.}
+\label{fig:InitED}
+\end{figure}
+
+All three models have a first excited state around 1eV, but only in the minimal model does this state fall near the sample set used for the fitting, and is the only model in which this state corresponds to the correct excitation O 2$p_z \rightarrow $ O 2p$_\pi$ as seen in experiment.
+In contrast, the first excited state for the other two models are visibly distant from our sample set and do not correspond to the experimental first excited state.
+The large distance of these eigenstates from our sample set indicates that their predicted eigenvalues may suffer from large extrapolation errors, and as such we will call them \textit{intruder} states.
+In Figure \ref{fig:Intruder} we present all eigenstates among the six potential models which we classify as intruders.
+While using a Mahalanobis distance is a typical strategy for outlier (intruder) detection, it is only useful for distributions which are approximately normal.
+Our sample space does not resemble a (multivariate) normal distribution in any way, so we instead look at the average distance of the five nearest neighbor samples to an eigenstate.
+If the average distance is larger than 0.9, which in this case happens to divide eigenstates into intruders above and not below cleanly, it is classified as an intruder state.
+In the situation that multiple models share an intruder state, only the intruder state with the farthest average distance is included.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/intruder.pdf}
+\caption{Collection of unique intruder states from our six potential models selected using a k-nearest neighbor approach with k = 5.}
 \label{fig:Intruder}
 \end{figure}
+
+Given that our intruder states correspond to states within $\mathcal{LE}$ but outside our sample set, they must live within the span of the eigenstates which were excluded in our sampling scheme as described before.
+This is evidenced by the fact that two of the intruder states correspond explicitly to excitations we could not access: Cu 3d$_{z^2} \rightarrow $ O 2p$_\pi$ and  Cu 3d$_\pi \rightarrow $ O 2p$_\pi$.
+In fact, these are the only two singly excited states which we could not access with our sampling scheme.
+While inaccessible, we can approximate these states by single rigid MO excitations above the UKS ground state, which results in states with a FN-DMC energy above 4eV.
+Including a generous 2eV reduction in FN-DMC energy due to orbital relaxation, we estimate that these two states should lie at least 2eV in energy. 
+Since all the other inaccessible eigenstates are double or higher order excitations, our very approximate exploration of the inaccessible parts of $\mathcal{LE}$ leaves us with a reasonable prior: intruder states should lie above 2eV in energy in our effective theories.
+We can enforce this prior by adding a term to our ordinary linear regression cost function
+\begin{equation}
+\text{Cost} = \sum_{i} (E_\text{eff}[\Psi_i] - E_\text{ab}[\Psi_i])^2 + \lambda \sum_{p}\text{QHL}(2 - E_\text{eff}[\Psi_p]),\ \text{QHL}(x) = \Theta(x)x^2
+\label{eq:cost}
+\end{equation}
+where $\lambda>0$ is a parameter which can be varied, QHL is a quadratic hinge loss, $\Theta$ is the Heaviside step function, the index $i$ is over our sampled states and $p$ over the selected intruder states.
+Increasing the value of $\lambda$ leads to a stronger penalty for models which do not satisfy our prior.
+
 \pagebreak
-
-the minimal model (Min), Min + $\bar{t}_\pi$, Min + $\bar{t}_{dz}$, Min + $\bar{t}_\pi, \bar{t}_{ds}$, Min + $\bar{t}_\pi, \bar{t}_{sz}$, Min + $\bar{t}_{ds}, \bar{t}_{dz}$.
-Within the latter five models there are intruder eigenstates, states which lie very far away from our sample set and suffer from large extrapolation errors.
-Intruder states were defined as any eigenstates with energy $< $ 2 eV with a Mahalanobis distance greater than the 90th percentile of all distances.
-The Mahalanobis distance is used in data science for outlier detection \textbf{ref} and tells us how far away an eigenstate is from $\mathcal{SS}$.
-Show in \textbf{Figure ?} are the identified intruder states among the six models above which in aggregate we will call the prior space $\mathcal{PS}$.
-These energies of these eigenstates are not constrained by $\mathcal{SS}$ because of our inability to target certain base states like $c^\dagger_{p_\pi} c_{d_\pi} |GS\rangle$ as discussed before.
-This excitation specifically is within our set of intruder states alongside others like $c^\dagger_{p_\pi} c_{d_{z^2}} |GS\rangle$.
-Other methods like constrained DFT and CASSCF were used to converge these states but we were unsuccessful.
-
-In order to ensure that intruder states are not present within our final model, we enforce a prior that pushes intruder states above a chosen $E_{cut}$ = 2eV by altering the cost function for our regression.
-The choice of prior is built on both experimental knowledge and FN-DMC results.
-From experiment we know that any excitation which de-occupies a d-orbital should be $\sim$ 2 eV in energy.
-In fact all of our intruder states are excitations out of a d-orbital except for the higher energy intruder which is already nearly at 2eV and would not be affected too strongly by this choice of $E_{cut}$.
-While we cannot converge these missing base states using UKS, we can consider singles excitations on the UKS ground state which correspond to these excitations in order to get an upper bound for the FN-DMC energies of our missing base states.
-In FN-DMC the corresponding MO excited states are $> $4eV, and we believe even with orbital relaxation that the converged excited state should be $>$ 2eV in energy.
-The altered cost function takes the form:
-
-\begin{equation}
-\text{Cost} = \sum_{i \in \mathcal{SS}} (E_{eff,i} - E_{ab, i})^2 + \lambda \sum_{p \in \mathcal{PS}} \text{QHL}(2 - E_{eff,p})\ \text{QHL}(x) = \Theta(x)x^2
-\end{equation}
-where $E_{eff}$ is the energy of a state on our effective model, $\lambda>0$ is a parameter which can be varied, and QHL is a quadratic hinge loss with $\Theta$ the Heaviside step function. 
 \section{Discussion}

### 2019-06-10 paper/draft.tex
finished results and discussion! just need intro now

@@
 Beginning at 2.2 eV are excitations which remove a single electron from the fully filled Cu 3d shell and add them to either the O 2p$_\pi$ or Cu 4s orbitals.
-Seeing that the lowest energy excitations of the CuO molecule involve removing at most one electron from the Cu 3d shell, we define our low-energy space as
+The neutral copper atom also carries a Hund's coupling between the d and s orbitals of about $\sim$ 0.5 eV, the effects of which would be measurable among the states in $\mathcal{LE}$ as long as states of both doublet and quartet states are included.
+In order to probe all of these low-energy excitations we select a low-energy space
 \begin{equation}
@@
 \includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/init_ed.pdf}
-\caption{Results of exact diagonalization showing the energies and properties of the first twenty eigenstates for three candidate models.
-The ground state and first excited state are colored and have enlarged markers for clarity.}
+\caption{Results of exact diagonalization showing the energies and properties of the first twenty eigenstates for three candidate models fit using ordinary linear regression.
+The ground state and first excited state are colored and have enlarged markers for clarity.
+Error bars are 95\% CI calculated by a bootstrap estimate.}
 \label{fig:InitED}
@@
 
-\pagebreak
-\section{Discussion}
+\section{Results and Discussion}
+\subsection{Regression with a prior}
+Using our new cost function we find a set of models which accurately describe our sample data, have very similar spectra and eigenvectors, and do not contain intruder states below the 2eV prior. 
+Shown in Figure \ref{fig:Prior} show the R$^2$ score and QHL for different models fit at $\lambda \in [0,20]$. 
+The R$^2$ score stays above 0.95 for all models and $\lambda$, and the QHL converges quickly to nearly zero at $\lambda = 20$ for all six models. 
+We conclude that all six models at $\lambda = 20$ should be considered good models as they satisfy our prior and also explain our sample set accurately. 
+Also shown are $E_\text{eff}, E_\text{ab}$ for our samples using the minimal model at $\lambda = 20$ to illustrate the high fit quality even with a large $\lambda$.
 
-\section{Conclusion}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/prior_and_regr.pdf}
+\caption{On the left, scores of the six candidate models at various $\lambda$ when fitting our effective theories using the cost function \eqref{eq:cost}.
+On the right we show predicted versus calculated energies for our low-energy sampled states for the minimal model fit at $\lambda = 20$.}
+\label{fig:Prior}
+\end{figure}
+
+Figure \ref{fig:FinalED} presents the properties and eigenvalues of the lowest 30 eigenstates for three of the six fit models at $\lambda = 20$. 
+In comparison one can view Figure \ref{fig:InitED} as the same figure for fits at $\lambda = 0$. 
+At $\lambda = 20$ there are no outliers below 2eV in any of the three fit models. 
+The ground states are similar for the three models, a feature also seen for the models fit at $\lambda = 0$.
+Unlike at $\lambda = 0$, we see that the excited states of the three models are also very similar.
+This pattern is also shared by the three other candidate models which are not shown. 
+The additional constraint from asserting a prior has seemingly caused a single effective theory to emerge from our set of candidate models.
+The values of the fit parameters for our six models can be seen in Table 1.
+All the models share similar parameter values except the fifth model, Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$, indicating that there are at least two effective theories on $\mathcal{LE}$ which lead to identical low-energy eigenstates and spectra, describe the energies of our sample data accurately and satisfy our prior.
+We believe this arises because our low-energy space has no states which can probe the energy of the excitation Cu 3d $\rightarrow$ O 2p$_z$. 
+No single excitation on the ground state can lead to this excitation and the lowest energy double excitation which can probe this difference would be Cu 3d, O 2p$_z \rightarrow$ O 2p$_\pi$, O 4s which would have fewer than nine electrons in the Cu 3d orbitals since since the O 2p$_z$ molecular orbital is hybridized with the Cu 3d$_{z^2}$ orbital.
+This energy difference can therefore be freely varied without affecting the quality or eigensolutions to the model, meaning there is no unique effective model for this low-energy space.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/final_ed.pdf}
+\caption{Results of exact diagonalization showing the energies and properties of the first thirty eigenstates for three candidate models using linear regression with cost function \ref{eq:cost} and $\lambda = 20$.
+The ground state and first excited state are colored and have enlarged markers for clarity.
+Error bars are 95\% CI calculated by a bootstrap estimate.}
+\label{fig:FinalED}
+\end{figure}	
+\begin{table}[H]
+\begin{center}
+
+\begin{tabular}{l|llllll}
+&Min & Min & Min & Min & Min & Min \\
+& & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$ & $ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$ & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$ & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$ & $ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$ \\ \hline
+$\epsilon_{d_{z^2}}$& 0.31(2)& 0.33(2)& 0.24(2)& 0.34(2)& 0.58(2)& 0.27(2)\\
+$\epsilon_{d_\pi}$& 0.19(1)& 0.10(1)& 0.19(1)& 0.10(2)& 0.08(2)& 0.19(1)\\
+$\epsilon_{d_\delta}$& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)\\
+$\epsilon_{4s}$& 2.16(4)& 2.24(6)& 2.22(3)& 2.23(6)& 1.2(2)& 2.2(6)\\
+$\epsilon_{p_\pi}$& 1.7(4)& 1.84(4)& 1.72(2)& 1.83(4)& 2.13(4)& 1.71(4)\\
+$\epsilon_{p_z}$& 0.93(5)& 0.98(5)& 1.06(3)& 0.96(6)& 1.73(7)& 0.99(7)\\
+$t_\pi$& -0.57(1)& -0.45(2)& -0.58(1)& -0.46(3)& -0.47(2)& -0.57(1)\\
+$t_{dz}$& 0.53(3)& 0.56(3)& 0.52(2)& 0.57(3)& 1.00(4)& 0.53(2)\\
+$t_{sz}$& 0.88(3)& 0.89(1)& 0.84(2)& 0.87(3)& 1.26(6)& 0.8(3)\\
+$t_{ds}$& 0.45(2)& 0.45(1)& 0.48(3)& 0.47(2)& 0.72(4)& 0.55(4)\\
+$J_{sd}$& -0.6(1)& -0.9(1)& -0.7(1)& -0.9(1)& -0.4(1)& -0.7(1)\\
+$U_s$& 4.0(1)& 3.6(3)& 3.9(1)& 3.6(2)& 4.5(2)& 3.9(1)\\
+\end{tabular}
+\\ $\ $
+\\
+Table 1: Parameters in eV for our six potential models when fit using \eqref{eq:cost} at $\lambda = 20$. 
+\end{center}
+\end{table}
+
+\subsection{Comparisons to experiment and theory}
+Our final regressed models accurately reproduce properties and energies of the lowest lying eigenstates as seen in modern APES experiments on the CuO molecule.
+From Figure \ref{fig:FinalED} we see that the ground state of our effective theory has fully filled Cu 3d shell, nearly two electrons in O 2p$_z$ orbital, three in the O 2p$_\pi$ and around a quarter of an electron in the Cu 4s orbital.
+An approximate electronic configuration for the ground state is therefore
+be assigned 1$\sigma^2$1$\pi^4$1$\delta^4$2$\sigma^2$2$\pi^3$3$\sigma^0$ where the orbitals associated with the assignment are Cu 3d$_{z^2}$, Cu 3d$_\pi$, Cu 3d$_\delta$, O 2p$_z$, O 2p$_\pi$, and Cu 4s.
+This state also has a total spin projection S$_z = \frac{1}{2}$.
+This matches the well studied ground state electron configuration for the molecule $^2\Pi$.
+There are two excited states around 1eV in energy, the first of which is a state with the following single excitation O 2p$_z \rightarrow$ O 2p$_\pi$, has the configuration 1$\sigma^2$1$\pi^4$1$\delta^4$2$\sigma^2$2$\pi^4$4$\sigma^0$, and S$_z = \frac{1}{2}$.
+According to experiment there is also such a state at 1eV and is usually denoted as $^2X$.
+A second excited state at 1.2 eV exists which corresponds to an excitation 
+O 2p$_\pi \rightarrow$ Cu 4s, has configuration 1$\sigma^2$1$\pi^4$1$\delta^4$2$\sigma^2$2$\pi^2$4$\sigma^1$, and can either be S$_z = \frac{1}{2}, \frac{3}{2}$. 
+This is also the lowest energy eigenstate which can be a spin quartet.
+\textbf{ref} agree that this excitation should be the lowest spin quartet excitation, but argue that this state should be at an energy of 1.9 eV. 
+Our model has a different spin quartet state with a full Cu d shell at 1.9 eV, corresponding to an excitation O 2p$_z \rightarrow$ Cu 4s, with configuration 1$\sigma^2$1$\pi^4$1$\delta^4$2$\sigma^1$2$\pi^4$4$\sigma^1$.
+There are another host of eigenstates for our models at 2 eV corresponding to singles excitations of the form Cu 3d $\rightarrow$ O 2p$_\pi$. 
+This matches measurements which indicate that the lowest energy eigenstates with a single hole in the Cu 3d shell lie at 2.2 eV above the ground state.
+
+Our model is more accurate than a single-particle model constructed using
+density functional theory orbitals and eigenvalues. 
+We consider a single-particle theory for the CuO molecule using restricted open-shell Kohn Sham (ROKS) eigenvalues and orbitals as single particle energies and states in our theory. 
+This model is very inaccurate in describing the energy of any state with an occupied Cu 4s molecular orbital which it assigns to higher than 4 eV in energy above the ground state.
+We believe this is due to this single particle method neglecting the heavy orbital relaxations between excited states, particularly in the $\sigma$ symmetry sector in which the Cu 4s orbital resides.
+
+\section{Conclusions}
+In this paper we systematically fit a many-body model for the neutral CuO molecule which can accurately reproduce the spectrum and properties of low-lying eigenstates seen in experiment using a \textit{ab-initio} QMC DMD method, and discuss the details of and developments in our model fitting procedure.
+In particular, we study the problem of intruder states in our effective theories --- states which suffer from large extrapolations errors under our model ---  by connecting the existence of these states to our inability to access parts of $\mathcal{LE}$ when generating the low-energy wave function samples used to fit our models.
+The intruder state issue is dealt by using our knowledge of $E_\text{ab}$ on the inaccessible parts of $\mathcal{LE}$ to construct a prior for our regression and enforcing it through an augmented ordinary linear regression cost function.
+The resultant models fit using the augmented cost function do not contain any intruder states.
+The fit models can accurately describe the energies and electron configurations of experimentally measured low-lying excitations with a much higher accuracy than effective single-particle theories generated by ROKS, for example.
+We also discuss the non-uniqueness of effective theories by studying two different effective theories we built which produce almost identical spectra and eigenvectors and fit our sample data accurately.
+
+We believe that the fitting procedure illustrated here can be used to generate effective theories for other strongly correlated systems and can be seen as a stepping stone towards developing a more robust downfolding methodology.
+A particularly interesting avenue may be developing effective theories for all neutral transition-metal oxide molecules (TMO), leading to a sequence of models across the transition metal atoms. 
+From a methodology stand point, the work here indicates the need for a robust sampling method of $\mathcal{LE}$ which allows one to access the full space across different materials.
+The existence of such a method would alleviate the need for the use of a prior to inject information about $E_\text{ab}$ on the inaccessible parts of $\mathcal{LE}$ and lead to a more conceptually and computationally direct model fitting procedure.
 

### 2019-06-10 paper/draft.tex
finished introduction

@@
 \section{Introduction}
+Systematically developing model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electrons systems is a pressing problem in modern condensed matter physics.
+Examples of such materials are high-temperature superconductors and other transition metal oxides.
+Low-energy excitations of these systems typically involve collective spin, lattice, and charge degrees of freedom with intermediate couplings.
+Consequently, many of these systems have competing exotic long range ordering, for example the hypothesized competition between antiferromagnetic order and d-wave superconducting order in the cuprates.
+The main difficulty in describing these materials is that they do not exhibit behavior which can be described by an effective single particle theory nor perturbatively in either weak or strong coupling limits.
+
+The necessity for non-perturbative, many-body models in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing model Hamiltonians for real world systems.
+Fermi liquid theory is the prototypical example of a one-body non-perturbative effective theory for metals.
+The low-energy effective theory has long-lived non-interacting single particle excitations near the Fermi surface and the Coulomb interaction is treated non-perturbatively.
+The anti-ferromagnetic Heisenberg model is a good example of a many-body perturbative effective theory for Mott insulators.
+The low-energy effective theory is built of many-body spin excitations which are derived from perturbing from a strong coupling limit.
+These types of models fail when used to model many strongly correlated electron systems, and consequently various non-perturbative many-body models like the t-J, 3-band Hubbard, and Kanamori models have emerged as candidates.
+While these models are computational tractable to solve, it is unclear whether they can describe the complexity of real systems, or how one would go about developing a more suitable model for a given material.
+
+Common approaches to building suitable model Hamiltonians for strongly correlated materials involve using single particle theories like density functional theory (DFT).
+One-body terms are typically obtained by projecting the solutions from the DFT band structure onto a localized single-particle basis, giving an estimate of hoppings and occupations on a lattice model.
+Two-body terms in the model are developed by assuming a screened Coulomb interaction based on constrained DFT or RPA.
+Aside from this method, Lowdin methods coupled to a stochastic method and canonical transformations have also been used to develop effective theories.
+These methods have the draw back that the constructed effective theory typically does not come with any estimate of the quality of the model, therefore making model validation a phenomenological task which can lead to unclear biases in the model construction.
+
+In this paper we systematically fit a many-body model
+which can accurately describe energies and properties of low-lying eigenstates for the neutral CuO molecule using a generalizable \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method as a stepping stone towards application to bulk strongly correlated materials.
+The neutral CuO molecule has been a subject of intense theoretical and experimental study due to the complex structure of its low-energy space.
+While the low-energy excitations in the doublet sector of the CuO molecule are well understood, singlet selection rules for spectroscopic measurements and the doublet ground state leave the quartet sector of excitations unexplored.
+The CuO molecule is hence a good playground for testing and developing the DMD method as there are some well understood excitations which our model should describe accurately and a set of poorly understood excitations which our model can give some insight into.
+The relative simplicity of the system allows us to rigorously detail each step of the DMD procedure, particularly sampling and regression techniques as well as quantifiable model validation.
 
@@
 The values of the fit parameters for our six models can be seen in Table 1.
-All the models share similar parameter values except the fifth model, Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$, indicating that there are at least two effective theories on $\mathcal{LE}$ which lead to identical low-energy eigenstates and spectra, describe the energies of our sample data accurately and satisfy our prior.
-We believe this arises because our low-energy space has no states which can probe the energy of the excitation Cu 3d $\rightarrow$ O 2p$_z$. 
-No single excitation on the ground state can lead to this excitation and the lowest energy double excitation which can probe this difference would be Cu 3d, O 2p$_z \rightarrow$ O 2p$_\pi$, O 4s which would have fewer than nine electrons in the Cu 3d orbitals since since the O 2p$_z$ molecular orbital is hybridized with the Cu 3d$_{z^2}$ orbital.
-This energy difference can therefore be freely varied without affecting the quality or eigensolutions to the model, meaning there is no unique effective model for this low-energy space.
+All the models share similar parameter values except the fifth model, Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$, indicating that there are at least two different effective theories on $\mathcal{LE}$ which lead to identical low-energy eigenstates and spectra, describe the energies of our sample data accurately and satisfy our prior.
+\textbf{Why does this happen?}
 
@@
 The resultant models fit using the augmented cost function do not contain any intruder states.
-The fit models can accurately describe the energies and electron configurations of experimentally measured low-lying excitations with a much higher accuracy than effective single-particle theories generated by ROKS, for example.
+The fit models can accurately describe the energies and electron configurations of experimentally measured low-lying excitations with a much higher accuracy than effective single-particle theories generated by ROKS, particularly for quartet states.
 We also discuss the non-uniqueness of effective theories by studying two different effective theories we built which produce almost identical spectra and eigenvectors and fit our sample data accurately.

### 2019-06-10 paper/draft.tex
finished abstract, need to do one paragraph of discussion

@@
 \usepackage{wrapfig}
+\begin{document}
+\begin{abstract}
+Constructing model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electron systems is a pressing problem in modern condensed matter physics.
+In this paper we systematically develop a many-body model for the neutral CuO molecule using a generalizable \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method and discuss details of the fitting procedure.
+Exact solutions to our final regressed model accurately reproduce properties and energies of the lowest lying eigenstates of the CuO molecule.
+Our results indicate that the DMD procedure can serve as a systematic method for developing many-body effective theories for strongly correlated electron systems.
+\end{abstract}
 
-\begin{document}
 \section{Introduction}
-Systematically developing model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electrons systems is a pressing problem in modern condensed matter physics.
+Systematically developing model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for strongly correlated electron systems is a pressing problem in modern condensed matter physics.
 Examples of such materials are high-temperature superconductors and other transition metal oxides.
@@
 In this paper we systematically fit a many-body model
-which can accurately describe energies and properties of low-lying eigenstates for the neutral CuO molecule using a generalizable \textit{ab-initio} Quantum Monte Carlo (QMC) density matrix downfolding (DMD) method as a stepping stone towards application to bulk strongly correlated materials.
+which can accurately describe energies and properties of low-lying eigenstates for the neutral CuO molecule using a generalizable \textit{ab-initio} QMC DMD method as a stepping stone towards application to bulk strongly correlated materials.
 The neutral CuO molecule has been a subject of intense theoretical and experimental study due to the complex structure of its low-energy space.

### 2019-06-11 paper/draft.tex
reduced to just 3 models to search over based on energy error on lowest 20 eigenstates. Dont need to worry about big error bars for really high energy states

@@
 We then take the left over models, rotate every operator and coefficient into the IAO basis through an appropriate orthogonal transformation, and exactly diagonalize the models.
-Any models which have an average errorbar in eigenvalues, also estimated by bootstrapping, greater than 0.25 eV are ignored.
-Each of the remaining six models describe our sample set accurately, have robust non-zero coefficients, and have small error bars in eigenvalues.
+Any models which have an average errorbar in the first 20 eigenvalues, also estimated by bootstrapping, greater than 0.20 eV are ignored.
+These eigenvalues correspond to states which lie below $\sim $ 2.5 eV and contain all low-energy Cu 3d$^{10}$ states and the lowest-energy Cu 3d$^{9}$ excitations.
+Each of the remaining three models describe our sample set accurately, have robust non-zero coefficients, and have small error bars in eigenvalues of states which we care about the most.
 However, the eigenstates below 2eV differ greatly between these models as illustrated in Figure \ref{fig:InitED}.
@@
 The large distance of these eigenstates from our sample set indicates that their predicted eigenvalues may suffer from large extrapolation errors, and as such we will call them \textit{intruder} states.
-In Figure \ref{fig:Intruder} we present all eigenstates among the six potential models which we classify as intruders.
+In Figure \ref{fig:Intruder} we present all eigenstates among the three potential models which we classify as intruders.
 While using a Mahalanobis distance is a typical strategy for outlier (intruder) detection, it is only useful for distributions which are approximately normal.
@@
 \includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/intruder.pdf}
-\caption{Collection of unique intruder states from our six potential models selected using a k-nearest neighbor approach with k = 5.}
+\caption{Collection of unique intruder states from our three potential models selected using a k-nearest neighbor approach with k = 5.}
 \label{fig:Intruder}
@@
 Shown in Figure \ref{fig:Prior} show the R$^2$ score and QHL for different models fit at $\lambda \in [0,20]$. 
-The R$^2$ score stays above 0.95 for all models and $\lambda$, and the QHL converges quickly to nearly zero at $\lambda = 20$ for all six models. 
-We conclude that all six models at $\lambda = 20$ should be considered good models as they satisfy our prior and also explain our sample set accurately. 
+The R$^2$ score stays above 0.95 for all models and $\lambda$, and the QHL converges quickly to nearly zero at $\lambda = 20$ for all three models. 
+We conclude that all three models at $\lambda = 20$ should be considered good models as they satisfy our prior and also explain our sample set accurately. 
 Also shown are $E_\text{eff}, E_\text{ab}$ for our samples using the minimal model at $\lambda = 20$ to illustrate the high fit quality even with a large $\lambda$.
@@
 \includegraphics[width=0.7\linewidth]{../qwalk/old/ub3lyp_s1_/analysis/figs/prior_and_regr.pdf}
-\caption{On the left, scores of the six candidate models at various $\lambda$ when fitting our effective theories using the cost function \eqref{eq:cost}.
+\caption{On the left, scores of the three candidate models at various $\lambda$ when fitting our effective theories using the cost function \eqref{eq:cost}.
 On the right we show predicted versus calculated energies for our low-energy sampled states for the minimal model fit at $\lambda = 20$.}
@@
 
-Figure \ref{fig:FinalED} presents the properties and eigenvalues of the lowest 30 eigenstates for three of the six fit models at $\lambda = 20$. 
+Figure \ref{fig:FinalED} presents the properties and eigenvalues of the lowest 30 eigenstates for three of the three fit models at $\lambda = 20$. 
 In comparison one can view Figure \ref{fig:InitED} as the same figure for fits at $\lambda = 0$. 
@@
 Unlike at $\lambda = 0$, we see that the excited states of the three models are also very similar.
-This pattern is also shared by the three other candidate models which are not shown. 
 The additional constraint from asserting a prior has seemingly caused a single effective theory to emerge from our set of candidate models.
-The values of the fit parameters for our six models can be seen in Table 1.
-All the models share similar parameter values except the fifth model, Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$, indicating that there are at least two different effective theories on $\mathcal{LE}$ which lead to identical low-energy eigenstates and spectra, describe the energies of our sample data accurately and satisfy our prior.
-\textbf{Why does this happen?}
+This conclusion is verified by looking at the values of the fit parameters for our three models, presented in Table 1.
+The parameter values for the three different models fit at $\lambda = 20$ are nearly identical within error bars and indicate that asserting our prior ensures that all three candidate models regress to a single low-energy effective theory.
+All occupation energies are relative to $\epsilon_{d_\delta}$.
 
@@
 \begin{tabular}{l|llllll}
-&Min & Min & Min & Min & Min & Min \\
-& & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$ & $ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$ & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$ & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$ & $ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$ \\ \hline
-$\epsilon_{d_{z^2}}$& 0.31(2)& 0.33(2)& 0.24(2)& 0.34(2)& 0.58(2)& 0.27(2)\\
-$\epsilon_{d_\pi}$& 0.19(1)& 0.10(1)& 0.19(1)& 0.10(2)& 0.08(2)& 0.19(1)\\
-$\epsilon_{d_\delta}$& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)& 0.0(0)\\
-$\epsilon_{4s}$& 2.16(4)& 2.24(6)& 2.22(3)& 2.23(6)& 1.2(2)& 2.2(6)\\
-$\epsilon_{p_\pi}$& 1.7(4)& 1.84(4)& 1.72(2)& 1.83(4)& 2.13(4)& 1.71(4)\\
-$\epsilon_{p_z}$& 0.93(5)& 0.98(5)& 1.06(3)& 0.96(6)& 1.73(7)& 0.99(7)\\
-$t_\pi$& -0.57(1)& -0.45(2)& -0.58(1)& -0.46(3)& -0.47(2)& -0.57(1)\\
-$t_{dz}$& 0.53(3)& 0.56(3)& 0.52(2)& 0.57(3)& 1.00(4)& 0.53(2)\\
-$t_{sz}$& 0.88(3)& 0.89(1)& 0.84(2)& 0.87(3)& 1.26(6)& 0.8(3)\\
-$t_{ds}$& 0.45(2)& 0.45(1)& 0.48(3)& 0.47(2)& 0.72(4)& 0.55(4)\\
-$J_{sd}$& -0.6(1)& -0.9(1)& -0.7(1)& -0.9(1)& -0.4(1)& -0.7(1)\\
-$U_s$& 4.0(1)& 3.6(3)& 3.9(1)& 3.6(2)& 4.5(2)& 3.9(1)\\
+&Min & Min & Min \\
+& & $ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$ & $ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$ \\ $\ $ \\ \hline 
+$\epsilon_{d_{z^2}}$& 0.32(2)& 0.32(1)& 0.29(2)\\
+$\epsilon_{d_\pi}$& 0.19(1)& 0.10(2)& 0.19(1)\\
+$\epsilon_{d_\delta}$& 0.0 & 0.0 & 0.0\\
+$\epsilon_{4s}$& 2.2(4)& 2.23(3)& 2.19(5)\\
+$\epsilon_{p_\pi}$& 1.7(3)& 1.8(2)& 1.7(3)\\
+$\epsilon_{p_z}$& 0.96(4)& 0.97(3)& 0.99(5)\\
+$t_\pi$& -0.57(1)& -0.45(2)& -0.57(1)\\
+$t_{dz}$& 0.55(3)& 0.56(2)& 0.54(2)\\
+$t_{sz}$& 0.87(2)& 0.89(2)& 0.85(2)\\
+$t_{ds}$& 0.44(1)& 0.45(1)& 0.45(2)\\
+$J_{sd}$& -0.6(1)& -0.8(1)& -0.6(1)\\
+$U_s$& 3.8(2)& 3.7(2)& 3.9(2))\\
 \end{tabular}
@@
 \\
-Table 1: Parameters in eV for our six potential models when fit using \eqref{eq:cost} at $\lambda = 20$. 
 \end{center}
+Table 1: Parameters in eV for our three potential models when fit using \eqref{eq:cost} at $\lambda = 20$. Error bars are 95\% CI calculated using a bootstrap estimate.
 \end{table}

### 2019-06-11 qwalk/old/ub3lyp_s1_/analyzedmc.py

@@ -671,7 +671,7 @@ def comb_plot_ed_small(full_df,av_df,models,fname=None,title=None,cutoff=0):
   21:r'Min$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
   24:r'Min$ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$'}
 
-  markers = ['s','o','^']
+  markers = ['s','o','^'] + ['o']*15
 
   z=-1
   for parm in ['iao_n_3dz2','iao_n_3dpi','iao_n_3dd','iao_n_2pz','iao_n_2ppi','iao_n_4s']:
@@ -695,7 +695,7 @@ def comb_plot_ed_small(full_df,av_df,models,fname=None,title=None,cutoff=0):
       sub_df = sub_df.sort_values(by=['energy'])
       sub_df['energy'] -= minE
       #sub_df = sub_df[sub_df['energy']<=4.0]
-      sub_df = sub_df.iloc[:20]
+      sub_df = sub_df.iloc[:30]
       x=sub_df[parm].values
       xerr_u=sub_df[parm+'_u'].values
       xerr_d=sub_df[parm+'_l'].values
@@ -835,8 +835,8 @@ def analyze(df=None,save=False):
   avg_eig_df = pd.read_pickle('analysis/avg_eig.pickle')
   noises = []
   for model in unique_models:
-    noise = avg_eig_df[avg_eig_df['model']==model].mean()['energy_u'] +\
-    avg_eig_df[avg_eig_df['model']==model].mean()['energy_l']
+    a = avg_eig_df[avg_eig_df['model']==model].sort_values(by='energy').iloc[:20]
+    noise = a.mean()['energy_u'] + a.mean()['energy_l']
     noises.append(noise)
 
   ind = np.argsort(noises)
@@ -845,23 +845,24 @@ def analyze(df=None,save=False):
   plt.ylabel('Avg E_err, eV')
   plt.xlabel('Model')
   plt.xticks(np.arange(len(ind)),np.array(unique_models)[ind])
-  plt.axhline(0.25,ls='--',c='k')
+  plt.axhline(0.20,ls='--',c='k')
   plt.show() 
   exit(0)
   '''
 
   #Plot ed
[…]

### 2019-06-11 qwalk/old/ub3lyp_s1_/analyzeprior.py

@@ -16,7 +16,7 @@ from find_connect import  *
 import matplotlib as mpl 
 from prior import prior_fit, prior_score #, sigmoid
 import itertools 
-from analyzedmc import sort_ed, desc_ed, avg_ed, plot_ed_small, comb_plot_ed_small
+from analyzedmc import sort_ed, desc_ed, avg_ed, plot_ed_small, comb_plot_ed_small, plot_ed
 ######################################################################################
 #FROZEN METHODS
 #Collect df
@@ -31,30 +31,20 @@ def add_priors(df,cutoff):
   df = df[var]
   df['prior'] = False
   
-  '''
-  prior_df = avg_eig[(avg_eig['model']==12)&(avg_eig['Sz']==0.5)].iloc[2]
-  prior_df = pd.concat((prior_df,avg_eig[(avg_eig['model']==9)&(avg_eig['Sz']==1.5)].iloc[0]),axis=1)
-  prior_df = prior_df.T
-  prior_df = prior_df[var]
-  prior_df['prior'] = True
-  '''
-  
   prior_df = pd.read_pickle('analysis/outlier.pickle')
-  prior_df = prior_df.iloc[[-5,-3,11,29,5]] #Remove any degenerate/near degenerate stuff
+  prior_df = prior_df.iloc[[-5,-3,-1,5]] #Remove any degenerate/near degenerate stuff
   prior_df['prior'] = True 
   prior_df['energy'] = min(df['energy']) + cutoff
 
   return pd.concat((df,prior_df),axis=0)
 
 def get_iao_parms(exp_parms,model):
-  print(exp_parms, model)
   param_names=['mo_n_4s','mo_n_2ppi','mo_n_2pz','mo_t_pi','mo_t_dz',
   'mo_t_sz','mo_t_ds','Jsd','Us']
   params=[]
   for parm in param_names:
     if(parm in model): params.append(exp_parms[model.index(parm)])
     else: params.append(0)
-  print(params)
   
   #params input must be es,epi,epz,tpi,tdz,tsz,tds
   h1_iao = h1_moToIAO(params[:-2])
@@ -74,7 +64,7 @@ def prior_analysis(df,cutoff=2):
   df = add_priors(df,cutoff = 2)
   oneparm_df = pd.read_pickle('analysis/oneparm.pickle').drop(columns=['r2_mu','r2_err'])
   prior_df = None
-  for i in [5, 9, 12, 21, 20, 24]:
[…]

### 2019-06-11 qwalk/old/ub3lyp_s1_/build_tables.py

@@ -1,0 +1,38 @@
+import pandas as pd
+import numpy as np 
+iao_labels=['$\epsilon_{d_{z^2}}$' ,'$\epsilon_{d_\pi}$', '$\epsilon_{d_\delta}$', 
+'$\epsilon_{4s}$', '$\epsilon_{p_\pi}$', '$\epsilon_{p_z}$', '$t_\pi$', 
+'$t_{dz}$', '$t_{sz}$', '$t_{ds}$', '$J_{sd}$', '$U_s$']
+
+model_labels=[r'',
+r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$',
+r'$ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$',
+r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$',
+r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
+r'$ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$']
+
+model_labels = model_labels[:3]
+
+df = pd.read_pickle('analysis/params.pickle')
+data = np.array(list(df['params_iao_mu'].values))
+data_err = np.array(list(df['params_err'].values))
+data = data.T
+data_err = data_err.T
+data = data[:,:3]
+data_err = data_err[:,:3]
+
+#IAO
+my_str='\\begin{tabular}{l|llllll}\n'+\
+  '&'+' & '.join(['Min']*len(model_labels))+' \\\\\n'+\
+  '&'+' & '.join(model_labels)+' \\\\ \hline \n'
+
+for i in range(data.shape[0]):
+  p = np.around(data[i],2)
+  perr = np.around(data_err[i],2)
+
+  add_str = iao_labels[i]
+  for z in range(len(p)):
+    add_str += '& '+str(p[z])+'('+str(perr[z])+')'
+  my_str+=add_str + '\\\\\n'
+my_str+='\\end{tabular} \\\\\n'
+print(my_str)

### 2019-06-11 qwalk/old/ub3lyp_s1_/ed.py

@@ -91,23 +91,39 @@ def ED(parms, nroots, norb, nelec):
   e, ci = fci.direct_uhf.kernel(h1, eri, norb, nelec, nroots=nroots)
   return e, ci
 
-  '''
-  #Generate vector of number occupations 
-  #['del','del','yz','xz','x','y','z2','z','s']
-  dm_u = []
-  dm_d = []
-  sigU = []
-  sigJ = []
-  for i in range(nroots):
-    dm2=cis.make_rdm12s(ci[i],norb,nelec)
-    dm_u.append(dm2[0][0])
-    dm_d.append(dm2[0][1])
-    sigU.append(dm2[1][1][8,8,8,8]) #U4s parameter sum
-    
-    Jsd = 0
-    for i in [0,1,2,3,6]:
-      Jsd += 0.25*(dm2[1][0][8,8,i,i] + dm2[1][2][8,8,i,i] - dm2[1][1][8,8,i,i] - dm2[1][1][i,i,8,8])-\
-             0.5*(dm2[1][1][i,8,8,i] + dm2[1][1][8,i,i,8])
-    sigJ.append(Jsd) #Jsd parameter sum
-  return e, ci, np.array(dm_u), np.array(dm_d), sigU, sigJ
-  '''
+if __name__=='__main__':
+  norb = 9
+  nelec = (8,7)
+  nroots = 30
+  
+  #MINIMAL MODEL
+  #v = [0.31,0.19,0,2.16,1.7,0.93,-0.57,0.53,0.88,0.45,-0.6,4.0]
+  #EXTENDED MODEL
+  v = [0.58,0.08,0,1.2,2.13,1.73,-0.47,1.00,1.26,0.72,-0.4,4.5]
+  edz2, edpi, edd, es, eppi, epz, tpi, tdz, tsz, tds, Jsd, Us = v
+
+  h1 = np.zeros((norb,norb))
+  h1[2,5] = h1[3,4] = tpi
+  h1[6,7] = tdz
+  h1[7,8] = tsz 
+  h1[6,8] = tds
+  h1 += h1.T
+  h1[6,6] = edz2
+  h1[2,2] = h1[3,3] = edpi
+  h1[0,0] = h1[1,1] = edd
+  h1[4,4] = h1[5,5] = eppi
+  h1[7,7] = epz
+  h1[8,8] = es
+
+  h1 = np.array([h1,h1])
+  h2 = h2_IAO(v[-2],v[-1])
+
+  mol = gto.Mole()
[…]

### 2019-06-11 paper/draft.tex
fixed small grammar errors!

@@
 
-The necessity for non-perturbative, many-body models in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing model Hamiltonians for real world systems.
+The necessity for non-perturbative, many-body models in describing the low-lying excited states of strongly correlated electron systems poses a difficult challenge when developing effective theories for real world systems.
 Fermi liquid theory is the prototypical example of a one-body non-perturbative effective theory for metals.
@@
 Using our new cost function we find a set of models which accurately describe our sample data, have very similar spectra and eigenvectors, and do not contain intruder states below the 2eV prior. 
-Shown in Figure \ref{fig:Prior} show the R$^2$ score and QHL for different models fit at $\lambda \in [0,20]$. 
+Shown in Figure \ref{fig:Prior} are the R$^2$ scores and QHL for the three candidate models fit at $\lambda \in [0,20]$. 
 The R$^2$ score stays above 0.95 for all models and $\lambda$, and the QHL converges quickly to nearly zero at $\lambda = 20$ for all three models. 
@@
 
-Figure \ref{fig:FinalED} presents the properties and eigenvalues of the lowest 30 eigenstates for three of the three fit models at $\lambda = 20$. 
+Figure \ref{fig:FinalED} presents the properties and eigenvalues of the lowest 30 eigenstates for the three fit models at $\lambda = 20$. 
 In comparison one can view Figure \ref{fig:InitED} as the same figure for fits at $\lambda = 0$. 
 At $\lambda = 20$ there are no outliers below 2eV in any of the three fit models. 
-The ground states are similar for the three models, a feature also seen for the models fit at $\lambda = 0$.
-Unlike at $\lambda = 0$, we see that the excited states of the three models are also very similar.
+The ground states are similar for the models, a feature also seen for the models fit at $\lambda = 0$.
+Unlike at $\lambda = 0$, we see that the excited states of the models are also very similar.
 The additional constraint from asserting a prior has seemingly caused a single effective theory to emerge from our set of candidate models.
 This conclusion is verified by looking at the values of the fit parameters for our three models, presented in Table 1.
-The parameter values for the three different models fit at $\lambda = 20$ are nearly identical within error bars and indicate that asserting our prior ensures that all three candidate models regress to a single low-energy effective theory.
+The parameter values for the three different models fit at $\lambda = 20$ are nearly identical within error bars and indicate that asserting our prior ensures that all candidate models regress to a single low-energy effective theory.
 All occupation energies are relative to $\epsilon_{d_\delta}$.
@@
 \subsection{Comparisons to experiment and theory}
-Our final regressed models accurately reproduce properties and energies of the lowest lying eigenstates as seen in modern APES experiments on the CuO molecule.
+Our final regressed model accurately reproduces properties and energies of the lowest lying eigenstates as seen in modern APES experiments on the CuO molecule.
 From Figure \ref{fig:FinalED} we see that the ground state of our effective theory has fully filled Cu 3d shell, nearly two electrons in O 2p$_z$ orbital, three in the O 2p$_\pi$ and around a quarter of an electron in the Cu 4s orbital.
@@
 In particular, we study the problem of intruder states in our effective theories --- states which suffer from large extrapolations errors under our model ---  by connecting the existence of these states to our inability to access parts of $\mathcal{LE}$ when generating the low-energy wave function samples used to fit our models.
-The intruder state issue is dealt by using our knowledge of $E_\text{ab}$ on the inaccessible parts of $\mathcal{LE}$ to construct a prior for our regression and enforcing it through an augmented ordinary linear regression cost function.
-The resultant models fit using the augmented cost function do not contain any intruder states.
-The fit models can accurately describe the energies and electron configurations of experimentally measured low-lying excitations with a much higher accuracy than effective single-particle theories generated by ROKS, particularly for quartet states.
-We also discuss the non-uniqueness of effective theories by studying two different effective theories we built which produce almost identical spectra and eigenvectors and fit our sample data accurately.
+The intruder state issue is dealt with by using our knowledge of $E_\text{ab}$ on the inaccessible parts of $\mathcal{LE}$ to construct a prior for our regression and enforcing it through an augmented ordinary linear regression cost function.
+The resultant model fit using the augmented cost function does not contain any intruder states.
+Our model can accurately describe the energies and electron configurations of experimentally measured low-lying excitations with a much higher accuracy than effective single-particle theories generated by ROKS, particularly for quartet states.
 

### 2019-06-14 paper/draft.tex
CuO paper draft done

@@
 The MO basis consists of the Cu 3d, 4s and O 2p molecular orbitals from the lowest energy restricted open-shell Kohn-Sham (ROKS) solution with $x \leftrightarrow y$ spatial symmetry, a O 2p$_z \rightarrow$ O 2p$_\pi$ excitation.
-As these two bases are used to describe the same space, they are related by an orthogonal transformation which will allow us to map between them if necessary.
+We determine whether each basis is valid by looking at how much the trace of 1-RDM in FN-DMC on that basis differs from the expected value of 15 electrons.
+We find that within 95\% confidence the trace is 14.7-14.8 (MO) and 14.6 - 14.7 (IAO), indicating that the major variation between states in $\mathcal{LE}$ can be described by either single particle basis.
+As these two bases are used to describe the same space, they are related by a  transformation which will allow us to map between them if necessary.
 This choice for the MO basis ensures that our basis elements are spin-independent and respect the spatial symmetries of the molecule.

### 2019-06-14 qwalk/old/ub3lyp_s1_/analyzedmc.py

@@ -814,7 +814,6 @@ def analyze(df=None,save=False):
   '''
 
   #Select unique models
-  '''
   unique_models = []
   oneparm_df = pd.read_pickle('analysis/oneparm.pickle').drop(columns=['r2_mu','r2_err'])
   for model in np.arange(32):
@@ -848,7 +847,6 @@ def analyze(df=None,save=False):
   plt.axhline(0.20,ls='--',c='k')
   plt.show() 
   exit(0)
-  '''
 
   #Plot ed
   #from sklearn.neighbors import KDTree, BallTree
@@ -922,4 +920,9 @@ if __name__=='__main__':
   #df.to_pickle('formatted_gosling.pickle')
   
   df = pd.read_pickle('formatted_gosling.pickle')
+  tr_iao = df['iao_n_3d'] + df['iao_n_2pz'] + df['iao_n_2ppi'] + df['iao_n_4s']
+  tr_mo = df['mo_n_3d'] + df['mo_n_2pz'] + df['mo_n_2ppi'] + df['mo_n_4s']
+  print(np.percentile(tr_iao,97.5), np.percentile(tr_iao,2.5))
+  print(np.percentile(tr_mo,97.5), np.percentile(tr_mo,2.5))
+  exit(0)
   analyze(df)

### 2019-06-14 qwalk/old/ub3lyp_s1_/build_tables.py

@@ -5,11 +5,11 @@ iao_labels=['$\epsilon_{d_{z^2}}$' ,'$\epsilon_{d_\pi}$', '$\epsilon_{d_\delta}$
 '$t_{dz}$', '$t_{sz}$', '$t_{ds}$', '$J_{sd}$', '$U_s$']
 
 model_labels=[r'',
-r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$',
-r'$ + \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$',
-r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$',
-r'$ + \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
-r'$ + \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$']
+r'$ +\ \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}$',
+r'$ +\ \bar{c}_{d_{z^2}}^\dagger \bar{c}_{p_z}$',
+r'$ +\ \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{4s}^\dagger \bar{c}_{p_z}$',
+r'$ +\ \bar{c}_{d_\pi}^\dagger \bar{c}_{p_\pi}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$',
+r'$ +\ \bar{c}_{d_z^2}^\dagger \bar{c}_{p_z}, \bar{c}_{d_z^2}^\dagger \bar{c}_{4s}$']
 
 model_labels = model_labels[:3]
 
@@ -20,17 +20,20 @@ data = data.T
 data_err = data_err.T
 data = data[:,:3]
 data_err = data_err[:,:3]
+data = data.T
+data_err = data_err.T
 
 #IAO
-my_str='\\begin{tabular}{l|llllll}\n'+\
-  '&'+' & '.join(['Min']*len(model_labels))+' \\\\\n'+\
-  '&'+' & '.join(model_labels)+' \\\\ \hline \n'
[…]
